### 2019-02-27 paper/ms.tex
Add paper

\documentclass{aastex62}

\usepackage{graphicx}
\usepackage{gensymb}
\usepackage{bm}

\newcommand{\Gus}[1]{\textcolor{red}{#1}}

\newcommand{\Msun}{\ensuremath{\text{M}_\odot}}
\newcommand{\pc}{\text{pc}}
\newcommand{\kpc}{\text{kpc}}
\newcommand{\Myr}{\text{Myr}}
\newcommand{\Gyr}{\text{Gyr}}

\newcommand{\CII}{C~\textsc{ii}}

\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\uth}{\textsuperscript{th}}
\newcommand{\n}{\text{n}}

\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}

\begin{document}

Suppose we have a line $l$ which we are attempting to measure emission from at
some target redshift $z_t$. Then, the interloper problem is that at various other redshifts $z_i$ for $i=1,2,3,...$

\bibliography{references}

\end{document}

### 2019-02-27 paper/ms.tex
Add some preamble commands
Add some introductory text

@@
 \usepackage{bm}
+\usepackage{amsmath}
 
@@
 \newcommand{\Msun}{\ensuremath{\text{M}_\odot}}
-\newcommand{\pc}{\text{pc}}
-\newcommand{\kpc}{\text{kpc}}
-\newcommand{\Myr}{\text{Myr}}
-\newcommand{\Gyr}{\text{Gyr}}
+\newcommand{\pc}{\ensuremath{\text{pc}}}
+\newcommand{\kpc}{\ensuremath{\text{kpc}}}
+\newcommand{\Mpc}{\ensuremath{\text{Mpc}}}
+\newcommand{\Myr}{\ensuremath{\text{Myr}}}
+\newcommand{\Gyr}{\ensuremath{\text{Gyr}}}
 
@@
 
+\newcommand{\mynu}[2]{\ensuremath{\nu_{#1,\text{#2}}}}
+\newcommand{\denps}{\ensuremath{P_{\delta,\delta}}}
+\newcommand{\xps}[2]{\ensuremath{P_{#1,#2}}}
+\newcommand{\pstot}[1]{\ensuremath{P_{#1,\text{tot}}}}
+
+\newcommand{\E}[1]{\mathrm{E}[#1]}
+\newcommand{\Var}[1]{\mathrm{Var}[#1]}
+\newcommand{\Cov}[2]{\mathrm{Cov}[#1,#2]}
+\newcommand{\avg}[1]{\ensuremath{\langle #1 \rangle}}
+
 \begin{document}
+
+The primary data is the observed intensity in a collection of voxels. In
+practice, one will make measurements in sky coordinates and frequency space,
+but to simplify the discussion we consider the observation of a finite
+comoving box with volume $V$. The box is small enough that if one length is
+assumed to lie along frequency space that the corresponding redshift extent of
+that axis is small enough that the observed voxels can be considered
+co-evolving. We are then interested in measuring $I_{l}(\bm{x})$, or the
+collective emission from line $l$ from each voxel. In order to understand the
+statistical properties of $I(\bm{x})$, we can compute the power spectrum which
+is related to the Fourier transform of $I$,
+\beq
+P_{l}(k) = \avg{I(\bm{k}) I^{*}(\bm{k})}\text{.}
+\eeq
+Since the line intensity is a biased tracer of the underlying density field,
+it is useful to parametrize the power spectrum as,
+\beq
+P_l(k) = b_l^2 \avg{I_l}^2 \denps{P_{\delta}}(k)\text{,}
+\eeq
+where $\denps{P_{\delta}}$ is the matter density power spectrum. Measuring
+$b_l$ and $\avg{I_l}$ independently is a useful endeavour, but not the focus
+of our study. Therefore, we will simplify and define $B_l \equiv b_l
+\avg{I_l}$, such that,
+\beq
+P_{l}(k) = B_l^2 \denps(k)
+\eeq
 

### 2019-02-27 paper/ms.tex
Add info about the specifics of interloper problem

@@
 Suppose we have a line $l$ which we are attempting to measure emission from at
-some target redshift $z_t$. Then, the interloper problem is that at various other redshifts $z_i$ for $i=1,2,3,...$
+some target redshift $z_l$ and some observed frequency $\mynu{l}{o} =
+\mynu{l}{e}/(1+z_l)$. Then, the interloper problem is that at various other
+redshifts $z_i$ for $i=1,2,3,...$ there will be emission from lines with
+emitted frequencies at redshift $z_i$ that satisfy the constraint $\mynu{l}{o}
+= \mynu{i}{o}$, or equivalently,
+\beq
+\mynu{i}{e} = \mynu{l}{e}\frac{1+z_i}{1+z_l}\text{.}
+\eeq
 

### 2019-02-27 paper/ms.tex
Put interloper problem into equation form
Start considering triple and setting up three field approach

@@
 
+Assuming perfect foreground removal, if one makes a naive power spectrum
+estimate of the observed intensity at a frequency $\mynu{l}{o}$, then the
+observed power spectrum will be,
+\beq\label{eq:observed_with_int}
+P_{\mynu{l}{o}} = P_{l} + \sum_{i} P_{i}\text{.}
+\eeq
+Since $P_l$ is the object of interest, we must robustly measure and subtract
+each of $P_i$.
+
+Now consider an arbitrary triple of the interloping lines $(i, j, k)$ where
+none of $i$, $j$, or $k$ are equal (and in particular none of $z_i$, $z_j$, or
+$z_k$ are equal). Now consider the case of removing emission from line $i$,
+which is interloping at redshift $z_i$. One can cross-correlate line $i$ with
+line $j$ if the frequency at which line $j$ is emitted at redshift $z_i$ is
+within the observed frequency band. That is, we'd like to observe line $j$ at
+a different frequency $\mynu{j}{o}'$ such that the emitted redshift $z_j'$ is
+equal to $z_i$, so that we can cross-correlate the two. In other words, we
+need $\mynu{j}{o}'$ to satisfy,
+\beq\label{eq:nu_obs}
+\begin{split}
+\mynu{j}{o}' &= \mynu{i}{o} \frac{\mynu{j}{e}}{\mynu{i}{e}} \\
+&= \mynu{i}{o} \frac{1+z_j}{1+z_i}\text{.}
+\end{split}
+\eeq
+If the frequency $\mynu{j}{o}'$ is in the observing band of an instrument
+(though in a different bin than $\mynu{i}{o}$), then a cross-corelation
+between line $i$ and line $j$ can be made. This can be used to measure the
+product $B_iB_j$. However, this does not allow us to remove either line $i$ or
+line $j$ reliably, since the relevant quantity to subtract from
+Equation~\ref{eq:observed_with_int} is $B_i^2 + B_j^2$, for which a direct
+constraint cannot be made. Perhaps measurements of the cross-bispectrum may be
+possible and allow us to measure $B_i$ and $B_j$ independently
+\citep{2018ApJ...867...26B}, but measuring cross-bispectra is difficult in
+practice and a reliable cross-spectrum measurement will probably be possible
+with less survey area.
+
+However, in the case that $\mynu{k}{o}'$ (defined similarly to
+Equation~\ref{eq:nu_obs}) also lies in the observing band, then a three-field
+approach can be employed to directly measure each of $B_i^2$, $B_j^2$, and
+$B_k^2$.
+
 \bibliography{references}

### 2019-02-27 paper/ms.tex
Setup pre-Fisher matrix formalism

@@
 
+One could proceed as we did previously \citep{2018arXiv181110609B}, estimating
+the auto-spectra in each line by forming suitable products and ratios of the
+various cross-spectra. However, we instead take a slightly different approach
+here by performing a joint fit for all of the various auto-spectra. First, we
+assume a measurement of each of $\xps{i}{j}$. Then the relevant variance and
+covariances are \citep[e.g.][]{2015JCAP...03..034V},
+\beq
+\begin{split}
+\Var{\xps{i}{j}} &= \xps{i}{j}^2 + \pstot{i}\pstot{j} \\
+\Cov{\xps{i}{j}}{\xps{i}{k}} &= \pstot{i}\xps{j}{k} + \xps{i}{j}\xps{i}{k}\text{.}
+\end{split}
+\eeq
+We are then making a measurement of each of $\xps{i}{j}$, $\xps{j}{k}$,
+and $\xps{k}{i}$. We further model each of these power spectra as,
+\beq
+\xps{i}{j}(k) = B_i(k) B_j(k) \denps(k)\text{.}
+\eeq
+That is, we are only working in the regime where $r_{i,j}=1$. What this
+translates to is that we may only perform this interloper removal on
+sufficiently large scales, i.e. where $k<k_{\text{max}}$, where
+$k_{\text{max}}$ is set by wherever the lines $i$ and $j$ start to
+decorrelate. The value of $k_{\text{max}}$ is the only aspect of our analysis
+that is model dependent.
+
 \bibliography{references}

### 2019-03-04 paper/ms.tex
Add macros, title material
Add preliminary abstract

@@
 \newcommand{\Gyr}{\ensuremath{\text{Gyr}}}
+\newcommand{\SFR}{\ensuremath{\text{SFR}}}
 
+\newcommand{\CI}{C~\textsc{i}}
 \newcommand{\CII}{C~\textsc{ii}}
+\newcommand{\OIII}{O~\textsc{iii}}
 
@@
 
+\newcommand{\penn}{Department of Physics \& Astronomy, University of
+Pennsylvania, 209 South 33rd St., Philadelphia, PA 19104, USA}
+
 \begin{document}
+
+\title{Removing CO Interlopers from [\CII] Surveys With the Three Field
+Approach}
+
+\email{abeane@sas.upenn.edu}
+
+\author{Angus Beane}
+\affil{\penn}
+
+\author{Adam Lidz}
+\affil{\penn}
+
+\author{others}
+
+\begin{abstract}
+Intensity mapping stands to be a promising probe of the large-scale structure
+of the universe at high redshift ($z>3$). The experiment TIME, currently
+undergoing a preliminary engineering run, will measure [\CII] emission from
+the redshift ranges $5<z<9$ {\bf check}. An important problem to overcome will
+be to remove interloping CO lines. These are lines that are emitted at a
+different frequency than [\CII] but are observed at the same frequency from
+gas residing at a different redshift. The measurement of [\CII] will be
+impacted by emission from three CO transitions
+\end{abstract}
 

### 2019-03-04 paper/ms.tex
Add intro section, separate theory section

@@
 
+\section{Introduction}\label{sec:intro}
+At high redshift ($z>3$) the most promising probe of the large-scale structure
+(LSS) of the universe is line intensity mapping. Rather than attempting to
+resolve individual galaxies, intensity mapping aims to measure the total
+emission from an atomic or molecular line of all galaxies within a rather
+coarse pixel. Commonly proposed lines include H$\alpha$, H$\beta$, Ly$\alpha$,
+[\CII], [\OIII], and 21~cm. During the Epoch of Reionization (EoR;
+$z\gtrsim6$), the hydrogen lines also measure the bulk emission from neutral
+hydrogen residing in the diffuse intergalactic medium (IGM).
+
+\section{Theory}\label{sec:theory}
 The primary data is the observed intensity in a collection of voxels. In

### 2019-03-04 paper/ms.tex
Fix eq bug
Reformat
Add beginning of CO modelling section

@@
 \beq
-P_l(k) = b_l^2 \avg{I_l}^2 \denps{P_{\delta}}(k)\text{,}
+P_l(k) = b_l^2 \avg{I_l}^2 \denps(k)\text{,}
 \eeq
@@
 \Var{\xps{i}{j}} &= \xps{i}{j}^2 + \pstot{i}\pstot{j} \\
-\Cov{\xps{i}{j}}{\xps{i}{k}} &= \pstot{i}\xps{j}{k} + \xps{i}{j}\xps{i}{k}\text{.}
+\Cov{\xps{i}{j}}{\xps{i}{k}} &= \pstot{i}\xps{j}{k} +
+\xps{i}{j}\xps{i}{k}\text{.}
 \end{split}
@@
 
+\section{CO Modelling} \label{sec:co_modelling}
+To model the statistical fluctuation and amplitude of the CO intensity maps we
+follow \citet{2016ApJ...825..143L}, and briefly summarize the procedure here.
+We begin by assuming a Schechter form for the star formation rate function,
+\beq\label{eq:schechter}
+\phi(\SFR)\,\text{d}\SFR = \phi_*
+\left(\frac{\SFR}{\SFR_*}\right)^{\alpha}\exp{\left[-\frac{\SFR}{\SFR_*}\right]}
+\frac{\text{d}\SFR}{\SFR_*}
+\eeq
+where $\alpha$ is the faint-end slope, $\SFR_*$ is the characteristic
+star-formation rate, and $\phi_*$ is the characteristic number density. The
+average specific intensity in a line $l$ can be related to the comoving
+emissivity by \citep{2011ApJ...741...70L, 2013ApJ...768...15P},
+\beq\label{eq:emiss_to_int}
+\avg{I_l} = \frac{\epsilon_l}{4\pi \nu_{\text{rest},l}}\frac{c}{H(z)}\text{,}
+\eeq
+where $\nu_{\text{rest},l}$ is the rest-frame emission frequency and
+$\epsilon_l$ is the comoving emissivity, each of line $l$.
+
 \bibliography{references}

### 2019-03-12 paper/ms.tex
Update line macros
Reorganize section 3

@@
 
-\newcommand{\CI}{C~\textsc{i}}
-\newcommand{\CII}{C~\textsc{ii}}
-\newcommand{\OIII}{O~\textsc{iii}}
+\newcommand{\CI}{\ensuremath{\text{C~\textsc{i}}}}
+\newcommand{\CII}{\ensuremath{\text{C~\textsc{ii}}}}
+\newcommand{\OIII}{\ensuremath{\text{O~\textsc{iii}}}}
+\newcommand{\CO}{\ensuremath{\text{CO}}}
 
@@
 
-\section{CO Modelling} \label{sec:co_modelling}
-To model the statistical fluctuation and amplitude of the CO intensity maps we
-follow \citet{2016ApJ...825..143L}, and briefly summarize the procedure here.
-We begin by assuming a Schechter form for the star formation rate function,
+\section{CO Measurements} \label{sec:co_measurements}
+\subsection{CO Modelling} \label{ssec:co_modelling}
+To model the statistical fluctuation and amplitude of the \CO{} intensity maps
+we follow \citet{2016ApJ...825..143L}, and briefly summarize the procedure
+here. We begin by assuming a Schechter form for the star formation rate
+function,
 \beq\label{eq:schechter}

### 2019-03-12 paper/ms.tex
Finish up CO modelling
Add explicit Fisher matrix calculations

@@
 where $\nu_{\text{rest},l}$ is the rest-frame emission frequency and
-$\epsilon_l$ is the comoving emissivity, each of line $l$.
+$\epsilon_l$ is the comoving emissivity, each of line $l$. Assuming a linear
+luminosity-SFR relation with a constant of proportionality of $L_0^l$, along
+with the Schechter form for the SFR function (Equation~\ref{eq:schechter}), it
+follows that \citep{2013ApJ...768...15P},
+\beq\label{eq:com_emiss}
+\epsilon_l = \phi_* L_0^{l}
+\frac{\SFR_*}{1\,\Msun\text{yr}^{-1}}\Gamma{(2+\alpha)}\text{.}
+\eeq
+We adopt the value of $L_0^{\CO}$ for each line transition from
+\citet{2010JCAP...11..016V}.
+
+\subsection{Something} \label{ssec:co_}
+We now consider the prospects of measuring the \CO{} transition using the
+three-field approach for CONCERTO and CCAT-p. First, let us consider the
+concrete example of jointly measuring the CO(5-4), CO(4-3), and CO(3-2) lines
+in the redshift range $0.6 < z < 0.725$ with CONCERTO. We label each line with
+the upper transitional level, e.g. CO(3-2) is referred to as ``3''. The
+relevant Fisher matrix is then,
+\beq\label{eq:co_fisher}
+F_{i,j} = 
+\int \frac{\text{d}k\,k^2}{2\pi^2} 
+V_{\text{surv}} \sum_{l} \sum_{m} 
+\frac{\partial \hat{P}_l(k)}{\partial B_i}
+\frac{1}{\Cov{\hat{P}_i(k)}{\hat{P}_j(k)}} 
+\frac{\partial \hat{P}_m(k)}{\partial B_j}\text{,}
+\eeq
+where $l$ and $m$ sum over all three cross-spectra. In our specific case where
+the partial derivatives are quite simple, we can simplify this expression for
+the off-diagonal elements as,
+\beq\label{eq:fisher_simple}
+F_{i,j} =
+\int \frac{\text{d}k\,k^2}{2\pi^2} 
+V_{\text{surv}}
+\left[
+\frac{B_i B_j}{(B_i B_j)^2 + B_{i,\text{tot}}^2B_{j,\text{tot}}^2}
++\sum_{i', j', k'\,\text{perm.}}
+\frac{B_{i'} B_k}{B_{i', \text{tot}}^2 B_{j'} B_{k'} + B_{i'} B_i B_j B_k}
+\right]\text{,}
+\eeq
+where the sum on $i', j', k'$ is over all permutations, i.e. over the three
+combinations $(i', j', k') = (1, 2, 3), (2, 3, 1), (3, 1, 2)$. Strikingly the
+integrand is independent of $k$, and as a result we can further simplify,
+resulting in,
+\beq\label{eq:fisher_super_simple}
+F_{i,j} = 
+\tilde{V_k}
+\left(
+\frac{B_i B_j}{(B_i B_j)^2 + B_{i,\text{tot}}^2B_{j,\text{tot}}^2}
++\sum_{i', j', k'\,\text{perm.}}
+\frac{B_{i'} B_k}{B_{i', \text{tot}}^2 B_{j'} B_{k'} + B_{i'} B_i B_j B_k}
+\right)\text{,}
+\eeq
+where,
+\beq\label{eq:Vk}
+\tilde{V_k} = \frac{k_{\text{max}}^3}{6\pi^2} V_{\text{surv}}\text{.}
+\eeq
+
+We can write down the diagonal elements similarly as,
+\beq\label{eq:fisher_offdiagonal}
+F_{i,i} = \tilde{V_k}
+\left(
+\frac{B_j^2}{(B_iB_j)^2+B_{i,\text{tot}}^2B_{j,\text{tot}}^2}
++\frac{B_k^2}{(B_iB_k)^2+B_{i,\text{tot}}^2B_{k,\text{tot}}^2}
++\frac{2B_j B_k}{B_{i,\text{tot}}^2B_jB_k + B_i^2B_jB_k}
+\right)\text{.}
+\eeq
 

### 2019-03-12 fisher_plots/CO_data.py
Create CO_data.py

@@ -1,0 +1,20 @@
+import numpy as np 
+import astropy.units as u
+from astropy.constants import c
+
+# CO line wavelengths in microns
+CO_lines_wave = {'1-0': 2610, '2-1': 1300, '3-2': 866, '4-3': 651,
+                 '5-4': 521, '6-5': 434, '7-6': 372, '8-7': 325,
+                 '9-8': 289, '10-9': 260, '11-10': 237,
+                 '12-11': 217, '13-12': 200}
+
+# Convert CO wavelengths to GHz
+speed_of_light = c.to_value(u.micron*u.GHz)
+
+CO_lines = { key: speed_of_light/wave for key, wave in CO_lines_wave }
+
+# CO luminosity constant in Lsolar
+CO_L0 = {'1-0': 3.7E3, '2-1': 2.8E4, '3-2': 7E4, '4-3': 9.7E4,
+         '5-4': 9.6E4, '6-5': 9.5E4, '7-6': 8.9E4, '8-7': 7.7E4,
+         '9-8': 6.9E4, '10-9': 5.3E4, '11-10': 3.8E4,
+         '12-11': 2.6E4, '13-12': 1.4E4}

### 2019-03-12 fisher_plots/threefield.py
Create threefield.py, generates Fisher matrices

@@ -1,0 +1,48 @@
+import numpy as np
+
+def gen_Vk(kmax, Vsurv):
+    ans = kmax**3/(6.*np.pi**2)
+    return Vsurv*ans
+
+def diagonal_component(B1, B2, B3, N1, N2, N3, Vk):
+    B1tot = np.sqrt(B1**2 + N1**2)
+    B2tot = np.sqrt(B2**2 + N2**2)
+    B3tot = np.sqrt(B3**2 + N3**2)
+
+    ans = B2**2/( (B1*B2)**2 + B1tot**2 * B2tot**2 )
+    ans += B3**2/( (B1*B3)**2 + B1tot**2 * B3tot**2 )
+    ans += 2*B2*B3/( B1tot**2*B2*B3 + B1**2*B2*B3 )
+
+    return Vk*ans
+
+def offdiagonal_component(B1, B2, B3, N1, N2, N3, Vk):
+    B1tot = np.sqrt(B1**2 + N1**2)
+    B2tot = np.sqrt(B2**2 + N2**2)
+    B3tot = np.sqrt(B3**2 + N3**2)
+
+    ans = B1*B2/( (B1*B2)**2 + B1tot**2*B2tot**2 )
+    ans += B1*B3/( B1tot**2*B2*B3 + B1*(B1*B2*B3) )
+    ans += B2*B3/( B2tot**2*B3*B1 + B2*(B1*B2*B3) )
+    ans += B3*B3/( B3tot**2*B1*B2 + B3*(B1*B2*B3) )
+
+    return Vk*ans
+
+def gen_fisher_matrix(B1, B2, B3, N1, N2, N3, kmax, Vsurv):
+    Vk = gen_Vk(kmax, Vsurv)
+
+    F11 = diagonal_component(B1, B2, B3, N1, N2, N3, Vk)
+    F22 = diagonal_component(B2, B3, B1, N2, N3, N1, Vk)
+    F33 = diagonal_component(B3, B1, B2, N3, N1, N2, Vk)
+
+    F12 = offdiagonal_component(B1, B2, B3, N1, N2, N3, Vk)
+    F23 = offdiagonal_component(B2, B3, B1, N2, N3, N1, Vk)
+    F31 = offdiagonal_component(B3, B1, B2, N3, N1, N2, Vk)
+
+    F21 = F12
+    F32 = F23
+    F13 = F31
+
+    mat = Vk * np.array([[F11, F12, F13], [F21, F22, F23], [F31, F32, F33]])
+
+    return mat
+

### 2019-03-12 fisher_plots/threefield.py
Add chisq function

@@ -1,4 +1,5 @@
 import numpy as np
+from scipy.stats import chi2
 
 def gen_Vk(kmax, Vsurv):
     ans = kmax**3/(6.*np.pi**2)
@@ -45,4 +46,34 @@ def gen_fisher_matrix(B1, B2, B3, N1, N2, N3, kmax, Vsurv):
     mat = Vk * np.array([[F11, F12, F13], [F21, F22, F23], [F31, F32, F33]])
 
     return mat
+
+class chisq(object):
+    def __init__(self, B1, B2, B3, cov_mat):
+        self.B1 = B1
+        self.B2 = B2
+        self.B3 = B3
+
+        self.cov_mat = cov_mat
+
+        # self.sigma1 = np.sqrt(cov_mat[0][0])
+        # self.sigma2 = np.sqrt(cov_mat[1][1])
+        # self.sigma3 = np.sqrt(cov_mat[2][2])
+
+        # self.sigma12 = cov_mat[0][1]
+        # self.sigma23 = cov_mat[1][2]
+        # self.sigma31 = cov_mat[2][0]
+
+        # self.rho12 = self.sigma12/(self.sigma1*self.sigma2)
+        # self.rho23 = self.sigma23/(self.sigma2*self.sigma3)
+        # self.rho31 = self.sigma31/(self.sigma3*self.sigma1)
+
+    def __call__(self, b1, b2, b3, chisq):
+        d1 = b1 - self.B1
+        d2 = b2 - self.B2
+        d3 = b3 - self.B3
+        d = np.array([d1, d2, d3])
+
+        chisq = np.matmul(np.matmul(np.transpose(d), np.linalg.inv(self.cov_mat)), d)
+        
+        return chisq
 

### 2019-03-12 fisher_plots/threefield.py
Add beginnings of corner plot

@@ -77,3 +77,36 @@ class chisq(object):
         
         return chisq
 
+def corner_plot(B1, B2, B3, N1, N2, N3, kmax, Vsurv):
+    fisher_mat = gen_fisher(B1, B2, B3, N1, N2, N3, kmax, Vsurv)
+
+    cov_mat = np.inverse(fisher_mat)
+
+    b1list = np.linspace(0.7*B1, 1.3*B1, 100)
+    b2list = np.linspace(0.7*B2, 1.3*B2, 100)
+    b3list = np.linspace(0.7*B3, 1.3*B3, 100)
+
+    b12_1, b12_2 = np.meshgrid(b1list, b2list)
+    b23_2, b23_3 = np.meshgrid(b2list, b3list)
+    b31_3, b31_1 = np.meshgrid(b3list, b1list)
+
+    chisq_b12 = chisq()
+
+    p1sigma = 0.68269   # probability inside 1 sigma
+    p2sigma = 0.95449   # probability inside 2 sigma
+    df = 3
+
+    delta1chisq = chi2.isf(1.-p1sigma, df=df)
+    delta2chisq = chi2.isf(1.-p2sigma, df=df)
+    contour_list = [delta1chisq, delta2chisq]
+
+    fig = plt.figure()
+    ax1 = plt.subplot(3, 3, 1)
+    ax2 = plt.subplot(3, 3, 5)
+    ax3 = plt.subplot(3, 3, 9)
+
+    ax12 = plt.subplot(3, 3, 4, sharex=ax1)
+    ax23 = plt.subplot(3, 3, 8, sharex=ax2)
+    ax13 = plt.subplot(3, 3, 7, sharex=ax1, sharey=ax23)
+
+    ax12.contour()

### 2019-03-12 fisher_plots/CO_predictions_threefield.py
Create CO_predictions_threefield.py

@@ -1,0 +1,5 @@
+import numpy as np 
+
+from threefield import gen_fisher_matrix
+
+

### 2019-03-14 fisher_plots/CO_data.py
Fix CO_lines line

@@ -11,7 +11,7 @@ CO_lines_wave = {'1-0': 2610, '2-1': 1300, '3-2': 866, '4-3': 651,
 # Convert CO wavelengths to GHz
 speed_of_light = c.to_value(u.micron*u.GHz)
 
-CO_lines = { key: speed_of_light/wave for key, wave in CO_lines_wave }
+CO_lines = { key: speed_of_light/wave for key, wave in CO_lines_wave.items() }
 
 # CO luminosity constant in Lsolar
 CO_L0 = {'1-0': 3.7E3, '2-1': 2.8E4, '3-2': 7E4, '4-3': 9.7E4,

### 2019-03-14 paper/ms.tex
Add \GHz command
Resection theory
Minor fixes

@@
 \newcommand{\SFR}{\ensuremath{\text{SFR}}}
+
+\newcommand{\GHz}{\ensuremath{\text{GHz}}}
 
@@
 
-\section{Theory}\label{sec:theory}
+\section{Motivation}\label{sec:theory}
+\subsection{Interloper Problem}\label{ssec:interloper}
 The primary data is the observed intensity in a collection of voxels. In
@@
 \beq
-P_{l}(k) = \avg{I(\bm{k}) I^{*}(\bm{k})}\text{.}
+P_{l,l}(k) = \avg{I_l(\bm{k}) I_l^{*}(\bm{k})}\text{.}
 \eeq
@@
 \beq
-P_l(k) = b_l^2 \avg{I_l}^2 \denps(k)\text{,}
+P_{l,l}(k) = b_l^2 \avg{I_l}^2 \denps(k)\text{,}
 \eeq
-where $\denps{P_{\delta}}$ is the matter density power spectrum. Measuring
+where $\denps(k)$ is the matter density power spectrum. Measuring
 $b_l$ and $\avg{I_l}$ independently is a useful endeavour, but not the focus
@@
 \beq
-P_{l}(k) = B_l^2 \denps(k)
+P_{l,l}(k) = B_l^2 \denps(k)
 \eeq

### 2019-03-14 paper/ms.tex
Some random text

@@
 each of $P_i$.
+
+\subsection{Three-Field Approach}\label{ssec:three_field}
+
+Consider one of the interloping lines, and assume that there exists two other
+lines emitted at the same redshift but by virtue of having a different
+emission frequency have a different observed frequency. For example, CO(6-5)
+emitted at $z=1$ will be observed at $345\,\GHz$, while CO(5-4) would be
+observed at $288\,\GHz$ and CO(4-3) at $230\,\GHz$. As long as these
+frequencies are in the observing band of some instrument, then we have enough
+freedom to directly constrain the auto-spectrum of each line. We could proceed
+as we did previously, forming suitable products and ratios to measure the
+relevant cross-spectra \citep{2018arXiv181110609B},
+\beq\label{eq:old_way}
+P_{\text{CO(6-5),CO(6-5)}} = 
+\frac{ \xps{\text{CO(6-5)}}{\text{CO(5-4)}} 
+       \xps{\text{CO(4-3)}}{\text{CO(6-5)}} }
+     { \xps{\text{CO(5-4)}}{\text{CO(4-3)}}}\text{.}
+\eeq
+However, this is a bit unconventional and extending to more than three lines
+is cumbersome.
 

### 2019-03-14 fisher_plots/CO_data.py
Add freq, res, area, spixtpix to CO_data

@@ -18,3 +18,33 @@ CO_L0 = {'1-0': 3.7E3, '2-1': 2.8E4, '3-2': 7E4, '4-3': 9.7E4,
          '5-4': 9.6E4, '6-5': 9.5E4, '7-6': 8.9E4, '8-7': 7.7E4,
          '9-8': 6.9E4, '10-9': 5.3E4, '11-10': 3.8E4,
          '12-11': 2.6E4, '13-12': 1.4E4}
+
+survey_freq_range = { 'TIME': np.array([183, 326]),
+                      'CONCERTO': np.array([200, 360]),
+                      'CCAT-p': np.array([210, 420]) }
+
+def TIME_res(nu):
+    if nu < 230:
+        return 1.5
+    else:
+        return 1.9
+
+def CONCERTO_res(nu):
+    return 1.5
+
+def CCATp_res(nu):
+    return nu/100
+
+survey_res_func = { 'TIME': TIME_res,
+                    'CONCERTO': CONCERTO_res,
+                    'CCAT-p': CCATp_res }
+
+survey_area = { 'TIME': 1.3*0.0083,
+                'CONCERTO': 1.4,
+                'CCAT-p': 2 }
+
+survey_z_spixtpix = { 'TIME': np.array([[6.0, 1.6E4], [7.4, 5.7E3]]),
+                      'CONCERTO': np.array([[4.5, 4.7E4], [6.0, 1.8E4], [7.4, 8.0E3]]),
+                      'CCAT-p': np.array([[3.7, 2.2E4], [4.5, 1.2E4], [6.0, 6.2E3]]) }
+
+

### 2019-03-20 fisher_plots/CO_data.py
Add gen_Blist_Nlist function

@@ -180,3 +180,30 @@ def calc_Vsurv(nu_obs, nu_emit, bandwidth, survey_area, cosmo):
     dlow = comoving_distance_at_freq(nu_obs + bandwidth/2, nu_emit, cosmo)
     Vsurv = (survey_area/totaldeg) * (4.*np.pi/3.) * (dup**3 - dlow**3)
     return Vsurv
+
+def gen_Blist_Nlist(b, bandwidth, kmax, zobs, lines, survey, cosmo):
+
+    nuemit = np.array([CO_lines[l] for l in lines])
+    nuobs = nuemit / (1.+zobs)
+
+    resolution = np.array([survey_res_func[survey](n) for n in nuobs])
+
+    avg_int_list = []
+    for l,n in zip(lines, nuemit):
+        L0 = CO_L0[l]
+        stable = smit_unlog_table
+
+        I = avg_int(L0, zobs, stable, n, cosmo)
+        avg_int_list.append(I)
+    avg_int_list = np.array(avg_int_list)
+
+    Blist = avg_int_list * b
+
+    Nlist = []
+    for r,no,ne in zip(resolution,nuobs,nuemit):
+        Vpix = calc_Vpix(no, ne, r, survey, cosmo)
+        N = spixtpix(no, survey)**2 * Vpix
+        Nlist.append(N)
+    Nlist = np.array(Nlist)
+
+    return Blist, Nlist

### 2019-03-20 fisher_plots/threefield.py
Add a threefield class that attempts to calculation fisher matrix

@@ -1,6 +1,57 @@
 import numpy as np
 from scipy.stats import chi2
 
+class threefield(object):
+    def __init__(self, z, Blist, Nlist, kmax, cosmo, kmin=1E-3, nint=1000):
+        
+        # construct linear matter power spectrum
+        self.klist = np.logspace(np.log10(kmin), np.log10(kmax), nint)
+        self.Pklist = cosmo.matterPowerSpectrum(self.klist*cosmo.h, z)
+        self.Pklist /= cosmo.h**3
+
+        # check Blist, Nlist, make sure lengths match
+        self.Blist = np.asarray(Blist)
+        self.Nlist = np.asarray(Nlist)
+        assert len(self.Blist) == len(self.Nlist), "Bias and noise lists \
+                                                    are different length!"
+        self.nparam = len(Blist)
+
+        # generate dPdB matrix
+        self.dPdB = np.zeros((self.nparam, self.nparam))
+        for i in range(self.nparam):
+            self.dPdB[i][i] = Blist[np.mod(i+1,self.nparam)]
+            self.dPdB[i][np.mod(i+1,self.nparam)] = Blist[i]
+        self.dPdB = np.transpose(self.dPdB)
+        self.dPdB = np.tensordot(self.dPdB, self.Pklist, axes=0)
+
+        # generate covariance matrix
+        self.cov = np.zeros((self.nparam, self.nparam, nint))
+        for i in range(self.nparam):
+            inext = np.mod(i+1, self.nparam)
+            self.cov[i][i] = (self.Blist[i]*self.Blist[inext]*self.Pklist)**2
+            self.cov[i][i] += (self.Blist[i]**2*self.Pklist + self.Nlist[i])*\
+                              (self.Blist[inext]**2*self.Pklist + self.Nlist[inext])
+            
+            inext2 = np.mod(i+2, self.nparam)
+            self.cov[i][inext] = (self.Blist[inext]**2*self.Pklist + self.Nlist[inext])*\
+                                 (self.Blist[i]*self.Blist[inext2]*self.Pklist)
+            self.cov[i][inext] += self.Blist[i]*self.Blist[inext]**2*self.Blist[inext2]*\
+                                  self.Pklist**2
+            self.cov[inext][i] = self.cov[i][inext].copy()
+
+        self.fmat_int = np.zeros((self.nparam, self.nparam, nint))
[…]

### 2019-03-20 fisher_plots/threefield.py
Add convenient testing bit

@@ -161,3 +161,21 @@ def corner_plot(B1, B2, B3, N1, N2, N3, kmax, Vsurv):
     ax13 = plt.subplot(3, 3, 7, sharex=ax1, sharey=ax23)
 
     ax12.contour()
+
+if __name__ == '__main__':
+    from colossus.cosmology import cosmology
+    from CO_data import gen_Blist_Nlist
+
+    params = {'flat': True, 'H0': 70, 'Om0': 0.27, 'Ob0': 0.046, 'sigma8': 0.8, 'ns': 1.0}
+    cosmo = cosmology.setCosmology('myCosmo', params)
+
+    survey = 'CCAT-p'
+    lines = ['6-5', '5-4', '4-3']
+    z = 0.88
+    kmax = 1
+    bandwidth = 28
+    b = 3
+
+    Blist, Nlist = gen_Blist_Nlist(3, 28, kmax, z, lines, survey, cosmo)
+
+    tf = threefield(z, Blist, Nlist, kmax, cosmo)

### 2019-03-20 paper/ms.tex
Change title
Delete a lot of stuff - its about to get real

@@
 
-\title{Removing CO Interlopers from [\CII] Surveys With the Three Field
-Approach}
+\title{CO Interlopers Eloping from [C~\textsc{ii}] Surveys}
 
@@
 \subsection{Something} \label{ssec:co_}
-We now consider the prospects of measuring the \CO{} transition using the
-three-field approach for CONCERTO and CCAT-p. First, let us consider the
-concrete example of jointly measuring the CO(5-4), CO(4-3), and CO(3-2) lines
-in the redshift range $0.6 < z < 0.725$ with CONCERTO. We label each line with
-the upper transitional level, e.g. CO(3-2) is referred to as ``3''. The
-relevant Fisher matrix is then,
 \beq\label{eq:co_fisher}
@@
 \eeq
-where $l$ and $m$ sum over all three cross-spectra. In our specific case where
-the partial derivatives are quite simple, we can simplify this expression for
-the off-diagonal elements as,
-\beq\label{eq:fisher_simple}
-F_{i,j} =
-\int \frac{\text{d}k\,k^2}{2\pi^2} 
-V_{\text{surv}}
-\left[
-\frac{B_i B_j}{(B_i B_j)^2 + B_{i,\text{tot}}^2B_{j,\text{tot}}^2}
-+\sum_{i', j', k'\,\text{perm.}}
-\frac{B_{i'} B_k}{B_{i', \text{tot}}^2 B_{j'} B_{k'} + B_{i'} B_i B_j B_k}
-\right]\text{,}
 \eeq
-where the sum on $i', j', k'$ is over all permutations, i.e. over the three
-combinations $(i', j', k') = (1, 2, 3), (2, 3, 1), (3, 1, 2)$. Strikingly the
-integrand is independent of $k$, and as a result we can further simplify,
-resulting in,
-\beq\label{eq:fisher_super_simple}
-F_{i,j} = 
-\tilde{V_k}
-\left(
-\frac{B_i B_j}{(B_i B_j)^2 + B_{i,\text{tot}}^2B_{j,\text{tot}}^2}
-+\sum_{i', j', k'\,\text{perm.}}
-\frac{B_{i'} B_k}{B_{i', \text{tot}}^2 B_{j'} B_{k'} + B_{i'} B_i B_j B_k}
-\right)\text{,}
 \eeq
-where,
-\beq\label{eq:Vk}
-\tilde{V_k} = \frac{k_{\text{max}}^3}{6\pi^2} V_{\text{surv}}\text{.}
-\eeq
-
-We can write down the diagonal elements similarly as,
-\beq\label{eq:fisher_offdiagonal}
-F_{i,i} = \tilde{V_k}
-\left(
-\frac{B_j^2}{(B_iB_j)^2+B_{i,\text{tot}}^2B_{j,\text{tot}}^2}
-+\frac{B_k^2}{(B_iB_k)^2+B_{i,\text{tot}}^2B_{k,\text{tot}}^2}
-+\frac{2B_j B_k}{B_{i,\text{tot}}^2B_jB_k + B_i^2B_jB_k}
-\right)\text{.}
 \eeq

### 2019-03-20 paper/ms.tex
Add correct Fisher matrix simplification

@@
 \newcommand{\pstot}[1]{\ensuremath{P_{#1,\text{tot}}}}
+\newcommand{\Bsum}{\ensuremath{\tilde{B}}}
 
@@
 \subsection{Something} \label{ssec:co_}
+We now consider the prospects of measuring the \CO{} transition using a
+multi-field approach. First, we choose to label each line with the upper
+transitional level, e.g. CO(3-2) is referred to as ``3.'' The relevant Fisher
+matrix is then,
 \beq\label{eq:co_fisher}
@@
 \eeq
+where $i$ and $j$ each refer to a line by its upper transitional level and the
+$l$ and $m$ sum over all \textit{combinations} of $i$ (or $j$).
+
+However, we can greatly simplify this expression by noticing that in the sum
+over $l$ all terms not involving $i$ will vanish in the derivative. Therefore,
+if we define the total sum of all bias factors as
+\beq\label{eq:sum_bias}
+\Bsum = \sum_k B_k\text{,}
 \eeq
+then we can write the sum portion of Equation~\ref{eq:co_fisher} as,
+\beq\label{eq:sum_part_of_fisher}
+\sum_l \frac{\partial \hat{P}_l(k)}{\partial B_i}
+= (\Bsum - B_i) \denps(k)\text{.}
 \eeq
+Therefore, we can simplify Equation~\ref{eq:co_fisher} and simply write,
+\beq\label{eq:co_fisher_simple}
+F_{i,j} = 
+\int \frac{\text{d}k\,k^2}{2\pi^2} 
+V_{\text{surv}}
+\frac{(\Bsum - B_i)(\Bsum - B_j)}
+{\Cov{\hat{P}_i(k)}{\hat{P}_j(k)}} \denps(k)^2
+\text{.}
 \eeq
+Interestingly, if one wishes to modify this approach and include the
+auto-power spectra in the analysis, the only modification is to make the
+substitution $(\Bsum - B_i) \rightarrow (\Bsum + B_i)$, and similarly for $j$.
 

### 2019-03-20 fisher_plots/threefield.py
Store parameters upon init in threefield

@@ -4,6 +4,11 @@ from scipy.stats import chi2
 class threefield(object):
     def __init__(self, z, Blist, Nlist, kmax, cosmo, kmin=1E-3, nint=1000):
         
+        # store some parameters
+        self.kmin, self.kmax = kmin, kmax
+        self.z, self.nint = z, nint
+        self.cosmo = cosmo
+
         # construct linear matter power spectrum
         self.klist = np.logspace(np.log10(kmin), np.log10(kmax), nint)
         self.Pklist = cosmo.matterPowerSpectrum(self.klist*cosmo.h, z)

### 2019-03-20 fisher_plots/threefield.py
Move lin ps to auxiliary function

@@ -10,9 +10,8 @@ class threefield(object):
         self.cosmo = cosmo
 
         # construct linear matter power spectrum
-        self.klist = np.logspace(np.log10(kmin), np.log10(kmax), nint)
-        self.Pklist = cosmo.matterPowerSpectrum(self.klist*cosmo.h, z)
-        self.Pklist /= cosmo.h**3
+        self.klist, self.Pklist = self._gen_lin_ps_(self.kmin, self.kmax, 
+                                                    self.nint, self.cosmo)
 
         # check Blist, Nlist, make sure lengths match
         self.Blist = np.asarray(Blist)
@@ -55,6 +54,13 @@ class threefield(object):
         self.fmat_int = np.multiply(self.fmat_int, int_factor)
 
         self.fmat = np.trapz(self.fmat_int, self.klist, axis=2)
+
+    def _gen_lin_ps_(self, kmin, kmax, nint, cosmo):
+        klist = np.logspace(np.log10(kmin), np.log10(kmax), nint)
+        Pklist = cosmo.matterPowerSpectrum(klist*cosmo.h, z)
+        Pklist /= cosmo.h**3
+
+        return klist, Pklist
 
 
 def gen_Vk(kmax, Vsurv):

### 2019-03-20 fisher_plots/threefield.py
Move Blist, Nlist checking to aux function

@@ -14,12 +14,6 @@ class threefield(object):
                                                     self.nint, self.cosmo)
 
         # check Blist, Nlist, make sure lengths match
-        self.Blist = np.asarray(Blist)
-        self.Nlist = np.asarray(Nlist)
-        assert len(self.Blist) == len(self.Nlist), "Bias and noise lists \
-                                                    are different length!"
-        self.nparam = len(Blist)
-
         # generate dPdB matrix
         self.dPdB = np.zeros((self.nparam, self.nparam))
         for i in range(self.nparam):
@@ -27,6 +21,8 @@ class threefield(object):
             self.dPdB[i][np.mod(i+1,self.nparam)] = Blist[i]
         self.dPdB = np.transpose(self.dPdB)
         self.dPdB = np.tensordot(self.dPdB, self.Pklist, axes=0)
+        self.Blist, self.Nlist, self.nparam = self._check_BN_param_(Blist, Nlist)
+
 
         # generate covariance matrix
         self.cov = np.zeros((self.nparam, self.nparam, nint))
@@ -61,6 +57,15 @@ class threefield(object):
         Pklist /= cosmo.h**3
 
         return klist, Pklist
+
+    def _check_BN_param_(self, Blist, Nlist):
+        # check Blist, Nlist, make sure lengths match
+        Blist = np.asarray(Blist)
+        Nlist = np.asarray(Nlist)
+        assert len(Blist) == len(Nlist), "Bias and noise lists are different length!"
+                                                    
+        nparam = len(Blist)
+        return Blist, Nlist, nparam
 
 
 def gen_Vk(kmax, Vsurv):

### 2019-03-20 fisher_plots/threefield.py
Move dPdB matrix gen to aux function

@@ -14,15 +14,10 @@ class threefield(object):
                                                     self.nint, self.cosmo)
 
         # check Blist, Nlist, make sure lengths match
-        # generate dPdB matrix
-        self.dPdB = np.zeros((self.nparam, self.nparam))
-        for i in range(self.nparam):
-            self.dPdB[i][i] = Blist[np.mod(i+1,self.nparam)]
-            self.dPdB[i][np.mod(i+1,self.nparam)] = Blist[i]
-        self.dPdB = np.transpose(self.dPdB)
-        self.dPdB = np.tensordot(self.dPdB, self.Pklist, axes=0)
         self.Blist, self.Nlist, self.nparam = self._check_BN_param_(Blist, Nlist)
 
+        # generate Bsum - Bi list
+        self.dPdB = self._gen_dPdB_(self.Blist, self.nparam)
 
         # generate covariance matrix
         self.cov = np.zeros((self.nparam, self.nparam, nint))
@@ -66,6 +61,13 @@ class threefield(object):
                                                     
         nparam = len(Blist)
         return Blist, Nlist, nparam
+
+    def _gen_dPdB_(self, Blist, nparam):
+        Btot = np.sum(Blist)
+        dPdB = np.full(nparam, Btot)
+        dPdB = np.subtract(dPdB, Blist)
+
+        return dPdB
 
 
 def gen_Vk(kmax, Vsurv):

### 2019-03-20 fisher_plots/threefield.py
Move cov calculation to aux function

@@ -20,19 +20,8 @@ class threefield(object):
         self.dPdB = self._gen_dPdB_(self.Blist, self.nparam)
 
         # generate covariance matrix
-        self.cov = np.zeros((self.nparam, self.nparam, nint))
-        for i in range(self.nparam):
-            inext = np.mod(i+1, self.nparam)
-            self.cov[i][i] = (self.Blist[i]*self.Blist[inext]*self.Pklist)**2
-            self.cov[i][i] += (self.Blist[i]**2*self.Pklist + self.Nlist[i])*\
-                              (self.Blist[inext]**2*self.Pklist + self.Nlist[inext])
-            
-            inext2 = np.mod(i+2, self.nparam)
-            self.cov[i][inext] = (self.Blist[inext]**2*self.Pklist + self.Nlist[inext])*\
-                                 (self.Blist[i]*self.Blist[inext2]*self.Pklist)
-            self.cov[i][inext] += self.Blist[i]*self.Blist[inext]**2*self.Blist[inext2]*\
-                                  self.Pklist**2
-            self.cov[inext][i] = self.cov[i][inext].copy()
+        self.cov = self._gen_cov_(self.Blist, self.Nlist, self.Pklist, 
+                                  self.nparam, self.nint)
 
         self.fmat_int = np.zeros((self.nparam, self.nparam, nint))
         self.sum_dPdB = np.sum(self.dPdB, axis=0)
@@ -69,6 +58,24 @@ class threefield(object):
 
         return dPdB
 
+    def _gen_cov_(Blist, Nlist, Pklist, nparam, nint):
+        cov = np.zeros((nparam, nparam, nint))
+        for i in range(nparam):
+            # diagonal elements
+            inext = np.mod(i+1, nparam)
+            cov[i][i] = (Blist[i]*Blist[inext]*Pklist)**2
+            cov[i][i] += (Blist[i]**2*Pklist + Nlist[i])*\
+                         (Blist[inext]**2*Pklist + Nlist[inext])
+            
+            # off-diagonal elements
+            inext2 = np.mod(i+2, nparam)
+            cov[i][inext] = (Blist[inext]**2*Pklist + Nlist[inext])*\
+                            (Blist[i]*Blist[inext2]*Pklist)
+            cov[i][inext] += Blist[i]*Blist[inext]**2*Blist[inext2]*\
+                             Pklist**2
[…]

### 2019-03-20 fisher_plots/threefield.py
Fix typo in threefield

@@ -58,7 +58,7 @@ class threefield(object):
 
         return dPdB
 
-    def _gen_cov_(Blist, Nlist, Pklist, nparam, nint):
+    def _gen_cov_(self, Blist, Nlist, Pklist, nparam, nint):
         cov = np.zeros((nparam, nparam, nint))
         for i in range(nparam):
             # diagonal elements

### 2019-03-23 paper/ms.tex
Fix Fisher matrix calc

--- 2019-03-20 paper/ms.tex
@@
 \subsection{Something} \label{ssec:co_}
+We now consider the prospects of measuring the \CO{} transition using a
+multi-field approach. First, we choose to label each line with the upper
+transitional level, e.g. CO(3-2) is referred to as ``3.'' The relevant Fisher
+matrix is then,
 \beq\label{eq:co_fisher}
 F_{i,j} = 
-\int \frac{\text{d}k\,k^2}{2\pi^2} 
-V_{\text{surv}} \sum_{l} \sum_{m} 
-\frac{\partial \hat{P}_l(k)}{\partial B_i}
-\frac{1}{\Cov{\hat{P}_i(k)}{\hat{P}_j(k)}} 
-\frac{\partial \hat{P}_m(k)}{\partial B_j}\text{,}
+\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
+\sum_{\substack{l,l'\\l > l'}} \sum_{\substack{m,m'\\m > m'}}
+\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
+\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
+\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
 \eeq
-\eeq
-\eeq
+where $i$ and $j$ each refer to a line by its upper transitional level and the
+$l$, $l'$, $m$ and $m'$ sum over all lines considered.
+
+Ignoring interlopers and foreground contamination for a moment, we can
+simplify this expression as
+\beq\label{eq:fisher_nocontam}
+\begin{split}
+F_{i,j} =&
+\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} \denps^2(k) \\
+\times & \left[ 
+\sum_{l\neq i,j} \frac{B_l^2}{\pstot{l}\xps{i}{j} + \xps{i}{l}\xps{l}{j}}
++ \delta_{ij} \left( 
+\sum_{l\neq i} \frac{B_l^2}{\xps{i}{l}^2 + \pstot{i}\pstot{l}}
++ \frac{1}{\pstot{i}\xps{\delta}{\delta} + \xps{i}{\delta}^2}
+\right) \right. \\
+& + (1-\delta_{ij}) \left(
+\frac{B_i}{\pstot{i}\xps{j}{\delta} + \xps{i}{\delta}\xps{i}{j}}
++ \frac{B_j}{\pstot{j}\xps{i}{\delta} + \xps{j}{\delta}\xps{i}{j}}
++ \frac{B_iB_j}{\xps{i}{j}^2 + \pstot{i}\pstot{j}}
+\right)
+\Bigg]
+\end{split}
 \eeq

### 2019-03-23 paper/ms.tex
Fix fisher matrix
Add derivation of Fisher matrix

@@
 Ignoring interlopers and foreground contamination for a moment, we can
-simplify this expression as
+simplify this expression as (see Appendix~\ref{app:fisher_deriv} for a
+derivation):
 \beq\label{eq:fisher_nocontam}
@@
 \times & \left[ 
-\sum_{l\neq i,j} \frac{B_l^2}{\pstot{l}\xps{i}{j} + \xps{i}{l}\xps{l}{j}}
-+ \delta_{ij} \left( 
+\delta_{ij} \left( 
 \sum_{l\neq i} \frac{B_l^2}{\xps{i}{l}^2 + \pstot{i}\pstot{l}}
@@
 \right) \right. \\
-& + (1-\delta_{ij}) \left(
-\frac{B_i}{\pstot{i}\xps{j}{\delta} + \xps{i}{\delta}\xps{i}{j}}
+&\left. + (1-\delta_{ij}) \left( 
+\sum_{l\neq i,j} \frac{B_l^2}{\pstot{l}\xps{i}{j} + \xps{i}{l}\xps{l}{j}}
++\frac{B_i}{\pstot{i}\xps{j}{\delta} + \xps{i}{\delta}\xps{i}{j}}
 + \frac{B_j}{\pstot{j}\xps{i}{\delta} + \xps{j}{\delta}\xps{i}{j}}
@@
 \right)
-\Bigg]
+\right]\text{.}
 \end{split}
 \eeq
+Including the auto-spectra in this analysis simply requires summing over all
+$l$ values, replacing $\xps{i}{i}$ with $\pstot{i}$ \Gus{I think this is
+correct?}.
+
+\appendix
+
+\section{Fisher Matrix Derivation}\label{app:fisher_deriv}
+We show a derivation of Equation~\ref{eq:fisher_nocontam}. First, consider the
+Fisher matrix from Equation~\ref{eq:co_fisher}.
+\beq\label{eq:co_fisher_2}
+F_{i,j} = 
+\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
+\sum_{\substack{l,l'\\l > l'}} \sum_{\substack{m,m'\\m > m'}}
+\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
+\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
+\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
+\eeq
+where $i$ and $j$ each refer to a line by its upper transitional level and the
+$l$, $l'$, $m$ and $m'$ sum over all lines considered. We exploit the fact
+that the Fisher matrix is unchanged under the substitution,
+\begin{equation*}
+\sum_{\substack{l,l'\\l > l'}} \rightarrow 
+\frac{1}{2} \sum_{\substack{l,l'\\l \neq l'}}\text{.}
+\end{equation*}
+Next, we can write down the derivatives of the power spectra as,
+\beq\label{eq:psderiv}
+\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
+= \left( B_{l'} \delta_{il} + B_l\delta_{il'} \right) \denps(k)\text{.}
+\eeq
+Now we can also write down the covariance formula as,
+\beq\label{eq:cov}
+\begin{aligned}
+\left(\Cov{\hat{P}_{l,l'}}{\hat{P}_{m,m'}}\right)^{-1} = 
+&(\pstot{l}\xps{l'}{m'} + \xps{l}{l'}\xps{l}{m'})^{-1} &&\times \delta_{lm} (1-\delta_{l'm'}) \\
+&+ (\pstot{l}\xps{l'}{m} + \xps{l'}{l}\xps{l}{m})^{-1} &&\times \delta_{lm'} (1-\delta_{l'm}) \\
+&+ (\pstot{l'}\xps{l}{m'} + \xps{l'}{l}\xps{l'}{m'})^{-1} &&\times \delta_{l'm} (1-\delta_{lm'}) \\
+&+ (\pstot{l'}\xps{l}{m} + \xps{l'}{l}\xps{l'}{m})^{-1} &&\times \delta_{l'm'} (1-\delta_{lm}) \\
+&+ (\xps{l}{l'}^2 + \pstot{l}\pstot{l'})^{-1} &&\times \delta_{lm} \delta_{l'm'} \\
+&+ (\xps{l}{l'}^2 + \pstot{l}\pstot{l'})^{-1} &&\times \delta_{lm'} \delta_{l'm}\text{.}
+\end{aligned}
+\eeq
+We are at liberty to distribute the inverse to all terms since upon inspection
+of the Kronecker delta's one and only one term will contribute to the sum. In
+the case that the covariance vanishes (e.g.
+$\Cov{\hat{P}_{1,2}}{\hat{P}_{3,4}}=0$) we exclude this term from the sum in
+Equation~\ref{eq:co_fisher_2}. Since the product,
+\begin{equation*}
+\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
+% \frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
+\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}
+\end{equation*}
+is symmetric under $(l,l',m,m') \rightarrow (l',l,m',m)$\footnote{and the
+summation is as well}, we can equivalently use the following formula for the
+covariance:
+\beq\label{eq:cov_simple}
+\begin{aligned}
+\left(\Cov{\hat{P}_{l,l'}}{\hat{P}_{m,m'}}\right)^{-1} = 
+&4 (\pstot{l}\xps{l'}{m'} + \xps{l}{l'}\xps{l}{m'})^{-1} &&\times \delta_{lm} (1-\delta_{l'm'}) \\
+&+ 2(\xps{l}{l'}^2 + \pstot{l}\pstot{l'})^{-1} &&\times \delta_{lm} \delta_{l'm'}\text{.}
+\end{aligned}
+\eeq
+Combining these facts we can arrive at the following formula for the Fisher matrix:
+\beq\label{eq:co_fisher_explicity}
+\begin{split}
+F_{i,j} = 
+\frac{1}{4} \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
+\denps(k)^2
+\sum_{\substack{l,l'\\l \neq l'}} \sum_{\substack{m,m'\\m \neq m'}}
+&\left( B_{l'} \delta_{il} + B_l\delta_{il'} \right)
+\left( B_{m'} \delta_{jm} + B_m\delta_{jm'} \right) \\
+\times&\left( \frac{4}{\pstot{l}\xps{l'}{m'} + \xps{l}{l'}\xps{l}{m'}} \delta_{lm} (1-\delta_{l'm'})
++ \frac{2}{\xps{l}{l'}^2 + \pstot{l}\pstot{l'}} \delta_{lm} \delta_{l'm'}\right)
+\text{.}
+\end{split}
+\eeq
+This formula can be expanded and simplified to give Equation~\ref{eq:fisher_nocontam}.
 

### 2019-03-24 paper/ms.tex
Rewrite fisher matrix calc

@@
 \section{Motivation}\label{sec:theory}
-\subsection{Interloper Problem}\label{ssec:interloper}
-The primary data is the observed intensity in a collection of voxels. In
-practice, one will make measurements in sky coordinates and frequency space,
-but to simplify the discussion we consider the observation of a finite
-comoving box with volume $V$. The box is small enough that if one length is
-assumed to lie along frequency space that the corresponding redshift extent of
-that axis is small enough that the observed voxels can be considered
-co-evolving. We are then interested in measuring $I_{l}(\bm{x})$, or the
-collective emission from line $l$ from each voxel. In order to understand the
-statistical properties of $I(\bm{x})$, we can compute the power spectrum which
-is related to the Fourier transform of $I$,
-\beq
-P_{l,l}(k) = \avg{I_l(\bm{k}) I_l^{*}(\bm{k})}\text{.}
-\eeq
-Since the line intensity is a biased tracer of the underlying density field,
-it is useful to parametrize the power spectrum as,
-\beq
-P_{l,l}(k) = b_l^2 \avg{I_l}^2 \denps(k)\text{,}
-\eeq
-where $\denps(k)$ is the matter density power spectrum. Measuring
-$b_l$ and $\avg{I_l}$ independently is a useful endeavour, but not the focus
-of our study. Therefore, we will simplify and define $B_l \equiv b_l
-\avg{I_l}$, such that,
-\beq
-P_{l,l}(k) = B_l^2 \denps(k)
-\eeq
-
-Suppose we have a line $l$ which we are attempting to measure emission from at
-some target redshift $z_l$ and some observed frequency $\mynu{l}{o} =
-\mynu{l}{e}/(1+z_l)$. Then, the interloper problem is that at various other
-redshifts $z_i$ for $i=1,2,3,...$ there will be emission from lines with
-emitted frequencies at redshift $z_i$ that satisfy the constraint $\mynu{l}{o}
-= \mynu{i}{o}$, or equivalently,
-\beq
-\mynu{i}{e} = \mynu{l}{e}\frac{1+z_i}{1+z_l}\text{.}
-\eeq
-
-Assuming perfect foreground removal, if one makes a naive power spectrum
-estimate of the observed intensity at a frequency $\mynu{l}{o}$, then the
-observed power spectrum will be,
-\beq\label{eq:observed_with_int}
-P_{\mynu{l}{o}} = P_{l} + \sum_{i} P_{i}\text{.}
-\eeq
-Since $P_l$ is the object of interest, we must robustly measure and subtract
-each of $P_i$.
 
 \subsection{Three-Field Approach}\label{ssec:three_field}
+We describe the multi-field approach in full generality and state some
+results.
 
-Consider one of the interloping lines, and assume that there exists two other
-lines emitted at the same redshift but by virtue of having a different
-emission frequency have a different observed frequency. For example, CO(6-5)
-emitted at $z=1$ will be observed at $345\,\GHz$, while CO(5-4) would be
-observed at $288\,\GHz$ and CO(4-3) at $230\,\GHz$. As long as these
-frequencies are in the observing band of some instrument, then we have enough
-freedom to directly constrain the auto-spectrum of each line. We could proceed
-as we did previously, forming suitable products and ratios to measure the
-relevant cross-spectra \citep{2018arXiv181110609B},
-\beq\label{eq:old_way}
-P_{\text{CO(6-5),CO(6-5)}} = 
-\frac{ \xps{\text{CO(6-5)}}{\text{CO(5-4)}} 
-       \xps{\text{CO(4-3)}}{\text{CO(6-5)}} }
-     { \xps{\text{CO(5-4)}}{\text{CO(4-3)}}}\text{.}
-\eeq
-However, this is a bit unconventional and extending to more than three lines
-is cumbersome.
-
-Now consider an arbitrary triple of the interloping lines $(i, j, k)$ where
-none of $i$, $j$, or $k$ are equal (and in particular none of $z_i$, $z_j$, or
-$z_k$ are equal). Now consider the case of removing emission from line $i$,
-which is interloping at redshift $z_i$. One can cross-correlate line $i$ with
-line $j$ if the frequency at which line $j$ is emitted at redshift $z_i$ is
-within the observed frequency band. That is, we'd like to observe line $j$ at
-a different frequency $\mynu{j}{o}'$ such that the emitted redshift $z_j'$ is
-equal to $z_i$, so that we can cross-correlate the two. In other words, we
-need $\mynu{j}{o}'$ to satisfy,
-\beq\label{eq:nu_obs}
-\begin{split}
-\mynu{j}{o}' &= \mynu{i}{o} \frac{\mynu{j}{e}}{\mynu{i}{e}} \\
-&= \mynu{i}{o} \frac{1+z_j}{1+z_i}\text{.}
-\end{split}
-\eeq
-If the frequency $\mynu{j}{o}'$ is in the observing band of an instrument
-(though in a different bin than $\mynu{i}{o}$), then a cross-corelation
-between line $i$ and line $j$ can be made. This can be used to measure the
-product $B_iB_j$. However, this does not allow us to remove either line $i$ or
-line $j$ reliably, since the relevant quantity to subtract from
-Equation~\ref{eq:observed_with_int} is $B_i^2 + B_j^2$, for which a direct
-constraint cannot be made. Perhaps measurements of the cross-bispectrum may be
-possible and allow us to measure $B_i$ and $B_j$ independently
-\citep{2018ApJ...867...26B}, but measuring cross-bispectra is difficult in
-practice and a reliable cross-spectrum measurement will probably be possible
-with less survey area.
-
-However, in the case that $\mynu{k}{o}'$ (defined similarly to
-Equation~\ref{eq:nu_obs}) also lies in the observing band, then a three-field
-approach can be employed to directly measure each of $B_i^2$, $B_j^2$, and
-$B_k^2$.
-
-One could proceed as we did previously \citep{2018arXiv181110609B}, estimating
-the auto-spectra in each line by forming suitable products and ratios of the
-various cross-spectra. However, we instead take a slightly different approach
-here by performing a joint fit for all of the various auto-spectra. First, we
-assume a measurement of each of $\xps{i}{j}$. Then the relevant variance and
-covariances are \citep[e.g.][]{2015JCAP...03..034V},
+First, we assume a measurement of each of $\xps{i}{j}$. The relevant variance
+and covariances are \citep[e.g.][]{2015JCAP...03..034V}
 \beq
@@
 We are then making a measurement of each of $\xps{i}{j}$, $\xps{j}{k}$,
-and $\xps{k}{i}$. We further model each of these power spectra as,
+and $\xps{k}{i}$. We model each of these power spectra as
 \beq
@@
 decorrelate. The value of $k_{\text{max}}$ is the only aspect of our analysis
-that is model dependent.
+that is model dependent. Only considering modes up to a $k_{\text{max}}$ is
+analogous to a similar procedure in galaxy surveys where only large-scale
+information up to a $k_{\text{max}}$.
 

### 2019-03-24 fisher_plots/threefield.py

@@ -16,23 +16,9 @@ class threefield(object):
         # check Blist, Nlist, make sure lengths match
         self.Blist, self.Nlist, self.nparam = self._check_BN_param_(Blist, Nlist)
 
-        # generate Bsum - Bi list
-        self.dPdB = self._gen_dPdB_(self.Blist, self.nparam)
+        self.fmat = self._gen_fmat_(self.Blist, self.Nlist, self.klist, self.Pklist, 
+                                    self.nparam, self.nint)
 
-        # generate covariance matrix
-        self.cov = self._gen_cov_(self.Blist, self.Nlist, self.Pklist, 
-                                  self.nparam, self.nint)
-
-        self.fmat_int = np.zeros((self.nparam, self.nparam, nint))
-        self.sum_dPdB = np.sum(self.dPdB, axis=0)
-        for i in range(self.nparam):
-            for j in range(self.nparam):
-                print('lol')
-
-        int_factor = np.divide(np.square(self.klist), 2.*np.pi**2)
-        self.fmat_int = np.multiply(self.fmat_int, int_factor)
-
-        self.fmat = np.trapz(self.fmat_int, self.klist, axis=2)
 
     def _gen_lin_ps_(self, kmin, kmax, nint, cosmo):
         klist = np.logspace(np.log10(kmin), np.log10(kmax), nint)
@@ -50,12 +36,69 @@ class threefield(object):
         nparam = len(Blist)
         return Blist, Nlist, nparam
 
-    def _gen_dPdB_(self, Blist, nparam):
-        Btot = np.sum(Blist)
-        dPdB = np.full(nparam, Btot)
-        dPdB = np.subtract(dPdB, Blist)
+    def _gen_fmat_(self, Blist, Nlist, klist, Pklist, nparam, nint):
+        fmat = np.zeros((nparam, nparam, nint))
+        for i in range(nparam):
+            for j in range(nparam):
+                fmat[i][j] = self._gen_fmat_int_(i, j, Blist, Nlist, klist, Pklist)
+        
+        fmat = np.trapz(fmat, klist, axis=2)
 
-        return dPdB
+        return fmat
+
+    def _gen_fmat_int_(self, i, j, Blist, Nlist, klist, Pklist):
[…]

### 2019-03-24 fisher_plots/threefield.py
Add explicit fish mat calc

@@ -19,6 +19,8 @@ class threefield(object):
         self.fmat = self._gen_fmat_(self.Blist, self.Nlist, self.klist, self.Pklist, 
                                     self.nparam, self.nint)
 
+        self.explicit_fmat = self._explicit_fmat_(self.Blist, self.Nlist, self.klist, 
+                                                  self.Pklist, self.nparam, self.nint)
 
     def _gen_lin_ps_(self, kmin, kmax, nint, cosmo):
         klist = np.logspace(np.log10(kmin), np.log10(kmax), nint)
@@ -100,14 +102,63 @@ class threefield(object):
 
         return np.add(np.add(np.add(t1, t2), t3), t4)
 
-    def _gen_cov_(self, Blist, Nlist, Pklist, nparam, nint):
-        cov = np.zeros((nparam, nparam, nint))
+    def _explicit_fmat_(self, Blist, Nlist, klist, Pklist, nparam, nint):
+        fmat = np.zeros((nparam, nparam))
         for i in range(nparam):
-            # diagonal elements
-            inext = np.mod(i+1, nparam)
-            cov[i][i] = (Blist[i]*Blist[inext]*Pklist)**2
-            cov[i][i] += (Blist[i]**2 + Nlist[i])*\
-                         (Blist[inext]**2 + Nlist[inext])*np.square(Pklist)
+            for j in range(nparam):
+                fmat[i][j] = self._explicit_fmat_term_(i, j, Blist, Nlist, klist, Pklist, nparam, nint)
+        return fmat
+
+    def _explicit_fmat_term_(self, i, j, Blist, Nlist, klist, Pklist, nparam, nint):
+        Pbiilist = np.outer(np.square(Blist), Pklist)
+        Ptot = np.add(Pbiilist, Nlist[:,np.newaxis])
+
+        tot = 0
+        for l in range(nparam):
+            for lp in range(nparam):
+                if l <= lp:
+                    continue
+                if l==i:
+                    dPl = Blist[lp]*Pklist
+                elif lp==i:
+                    dPl = Blist[l]*Pklist
+                else:
+                    dPl = 0
+
+                for m in range(nparam):
+                    for mp in range(nparam):
+                        if m <= mp:
+                            continue
+                        if m==j:
+                            dPm = Blist[mp]*Pklist
+                        elif mp==j:
+                            dPm = Blist[m]*Pklist
[…]

### 2019-03-24 fisher_plots/threefield.py
Update threefield.py

@@ -159,16 +159,31 @@ class threefield(object):
 
 
 
-            
-            # off-diagonal elements
-            inext2 = np.mod(i+2, nparam)
-            cov[i][inext] = (Blist[inext]**2*Pklist + Nlist[inext])*\
-                            (Blist[i]*Blist[inext2]*Pklist)
-            cov[i][inext] += Blist[i]*Blist[inext]**2*Blist[inext2]*\
-                             Pklist**2
-            cov[inext][i] = cov[i][inext].copy()
+    # def _gen_dPdB_(self, Blist, nparam):
+    #     Btot = np.sum(Blist)
+    #     dPdB = np.full(nparam, Btot)
+    #     dPdB = np.subtract(dPdB, Blist)
 
-        return cov
+    #     return dPdB
+
+    # def _gen_cov_(self, Blist, Nlist, Pklist, nparam, nint):
+    #     cov = np.zeros((nparam, nparam, nint))
+    #     for i in range(nparam):
+    #         # diagonal elements
+    #         inext = np.mod(i+1, nparam)
+    #         cov[i][i] = (Blist[i]*Blist[inext]*Pklist)**2
+    #         cov[i][i] += (Blist[i]**2 + Nlist[i])*\
+    #                      (Blist[inext]**2 + Nlist[inext])*np.square(Pklist)
+            
+    #         # off-diagonal elements
+    #         inext2 = np.mod(i+2, nparam)
+    #         cov[i][inext] = (Blist[inext]**2*Pklist + Nlist[inext])*\
+    #                         (Blist[i]*Blist[inext2]*Pklist)
+    #         cov[i][inext] += Blist[i]*Blist[inext]**2*Blist[inext2]*\
+    #                          Pklist**2
+    #         cov[inext][i] = cov[i][inext].copy()
+
+    #     return cov
 
 def gen_Vk(kmax, Vsurv):
     ans = kmax**3/(6.*np.pi**2)

### 2019-03-24 paper/ms.tex
Reorganize section 2

@@
 
-\section{Motivation}\label{sec:theory}
-
-\subsection{Three-Field Approach}\label{ssec:three_field}
+\section{Multi-field Approach}\label{sec:theory}
 We describe the multi-field approach in full generality and state some
-results.
-
-First, we assume a measurement of each of $\xps{i}{j}$. The relevant variance
-and covariances are \citep[e.g.][]{2015JCAP...03..034V}
+results. First, we assume a measurement of each of $\xps{i}{j}$. The relevant
+variance and covariances are \citep[e.g.][]{2015JCAP...03..034V}
 \beq
@@
 analogous to a similar procedure in galaxy surveys where only large-scale
-information up to a $k_{\text{max}}$.
+information up to a $k_{\text{max}}$ where linear theory is applicable is used.
 

### 2019-03-24 paper/ms.tex
Add Fisher matrix intro
Add high precision regime

@@
 information up to a $k_{\text{max}}$ where linear theory is applicable is used.
+
+The Fisher matrix for our measurement is
+\beq\label{eq:fisher}
+F_{i,j} = 
+\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
+\sum_{\substack{l,l'\\l > l'}} \sum_{\substack{m,m'\\m > m'}}
+\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
+\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
+\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
+\eeq
+where $l$, $l'$, $m$, and $m'$ sum over all lines being considered. Note that
+we can make the substitution
+\begin{equation*}
+\sum_{\substack{l,l'\\l > l'}} \rightarrow 
+\frac{1}{2} \sum_{\substack{l,l'\\l \neq l'}}\text{,}
+\end{equation*}
+without changing the value of the Fisher matrix. Thus it will be easier to compute
+\beq\label{eq:fisher4}
+F_{i,j} = 
+\frac{1}{4} \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
+\sum_{\substack{l,l'\\l \neq l'}} \sum_{\substack{m,m'\\m \neq m'}}
+\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
+\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
+\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
+\eeq
+
+\subsection{High Precision Regime}\label{ssec:high_precision}
+To build some intuition, we consider the idealized case with no interloper,
+foreground, or detector noise. This is achievable in principle, though
+certainly not with current techniques and instruments. In this case, we have
+that $\pstot{i} = \xps{i}{i}$. Therefore, we can modify the variance and
+covariance formulas from before as
+\beq
+\begin{split}
+\Var{\xps{i}{j}} &= 2(B_iB_j)^2 \denps(k)^2 \\
+\Cov{\xps{i}{j}}{\xps{i}{k}} &= 2B_i^2B_jB_k\denps(k)^2\text{.}
+\end{split}
+\eeq
+We are now in a position to write down a general formula for the covariance
+between two cross-spectra,
+\beq\label{eq:cov_kron}
+\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} =
+\frac{1}{2B_l B_{l'} B_m B_{m'}}
+\left(\delta_{lm} + \delta_{lm'} + \delta_{l'm} + \delta_{l'm'} -
+\delta_{lm}\delta_{l'm'} - \delta_{lm'}\delta_{l'm}\right)
+\frac{1}{\denps(k)^2}\text{,}
+\eeq
+where the $\delta_{lm}$ is the Kronecker delta, and same for $\delta_{l'm}$,
+etc. We can also similarly write down a formula for the power spectrum
+derivative as
+\beq\label{eq:ps_deriv}
+\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
+= \left( B_l \delta_{il'} + B_{l'}\delta_{il} \right) \denps(k)\text{.}
+\eeq
+Combining the two results gives
+\beq\label{eq:cov_and_deriv}
+\begin{split}
+\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}&
+\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
+\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\\ 
+&= 
+\frac{(B_l \delta_{il'} + B_{l'} \delta_{il})(B_m \delta_{jm'} + B_{m'} \delta_{jm})}
+{2 B_l B_{l'} B_m B_{m'}}
+\left(\delta_{lm} + \delta_{lm'} + \delta_{l'm} + \delta_{l'm'}
+-\delta_{lm}\delta_{l'm'} - \delta_{lm'}\delta_{l'm}\right)\text{.}
+\end{split}
+\eeq
+Note that this product is independent of $k$. As a result, we can pull it out of the integral in Equation~\ref{eq:fisher4}. We can then perform that integral. If we then define
+\begin{equation*}
+\tilde{V}_k \equiv \frac{k_{\text{max}}^3}{6\pi^2} V_{\text{surv}}\text{,}
+\end{equation*}
+then we can write the Fisher matrix as
+\beq
+F_{i,j} = \frac{\tilde{V}_k}{4}
+\sum_{\substack{l,l'\\l \neq l'}} \sum_{\substack{m,m'\\m \neq m'}}
+\frac{(B_l \delta_{il'} + B_{l'} \delta_{il})(B_m \delta_{jm'} + B_{m'} \delta_{jm})}
+{2 B_l B_{l'} B_m B_{m'}}
+\left(\delta_{lm} + \delta_{lm'} + \delta_{l'm} + \delta_{l'm'}
+-\delta_{lm}\delta_{l'm'} - \delta_{lm'}\delta_{l'm}\right)\text{.}
+\eeq
+
+Since the factor that comes before the $(\delta_{lm} + \delta_{lm'} +
+\delta_{l'm} + \delta_{l'm'})$ term is symmetric under $l\rightarrow l'$ and
+$m\rightarrow m'$, we can replace it by $4\delta_{lm}$. One can show by direct
+computation that the $\delta_{lm}\delta_{l'm'}$ and $\delta_{lm'}\delta_{l'm}$
+terms vanish, and so we can write
+\beq
+F_{i,j} = \tilde{V}_k
+\sum_{\substack{l,l'\\l \neq l'}} \sum_{\substack{m,m'\\m \neq m'}}
+\frac{(B_l \delta_{il'} + B_{l'} \delta_{il})(B_m \delta_{jm'} + B_{m'} \delta_{jm})}
+{2 B_l B_{l'} B_m B_{m'}}
+\delta_{lm}\text{.}
+\eeq
+It is then possible to show that
+\beq\label{eq:fisher_perfect}
+    F_{i,j}=\frac{\tilde{V}_k}{2B_iB_j} \times
+    \begin{cases}
+         N(N-1) & \text{if $i=j$} \\
+         3N-4 &\text{if $i\neq j$} \\
+    \end{cases}
+\eeq
+where $N$ is the number of lines being considered. This can be inverted by
+guessing a functional form after working out a few test cases to give
+\beq\label{eq:cov_perfect}
+    C_{i,j} = (F^{-1})_{i,j}=\frac{B_iB_j}{2\tilde{V}_k\left[(N-2)(N-1)\right]^2} \times
+    \begin{cases}
+         4N^2 - 11N + 8 & \text{if $i=j$} \\
+         4-3N &\text{if $i\neq j$} \\
+    \end{cases}
+\eeq
+Note that the diagonal elements scale like $1/N^2$ while the off-diagonal
+elements scale like $1/N^3$. What this means is that in the large $N$ limit,
+the covariance matrix approaches diagonality. In particular, we can write that
+\beq\label{eq:cov_perfect_largeN}
+C_{i,j} \rightarrow \frac{2B_i^2}{N^2 \tilde{V}_k} \delta_{ij}\text{.}
+\eeq
+Note that this is equivalent to a perfect auto-spectrum measurement of volume
+$N^2 V_{\text{surv}}$. Therefore, with $N$ measurements of a volume
+$V_{\text{surv}}$, one can have the constraining power of a volume $N^2
+V_{\text{surv}}$!
 

### 2019-03-26 paper/ms.tex
Update ms.tex
Remove Fisher matrix section
Add noise limited regime

--- 2019-03-24 paper/ms.tex
@@
 variance and covariances are \citep[e.g.][]{2015JCAP...03..034V}
-\beq
+\beq\label{eq:var_cov}
 \begin{split}
@@
 information up to a $k_{\text{max}}$ where linear theory is applicable is used.
+
+The Fisher matrix for our measurement is
+\beq\label{eq:fisher}
+F_{i,j} = 
+\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
+\sum_{\substack{l,l'\\l > l'}} \sum_{\substack{m,m'\\m > m'}}
+\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
+\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
+\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
+\eeq
+where $l$, $l'$, $m$, and $m'$ sum over all lines being considered. Note that
+we can make the substitution
+\begin{equation*}
+\sum_{\substack{l,l'\\l > l'}} \rightarrow 
+\frac{1}{2} \sum_{\substack{l,l'\\l \neq l'}}\text{,}
+\end{equation*}
+without changing the value of the Fisher matrix. Thus it will sometimes be
+easier to compute
+\beq\label{eq:fisher4}
+F_{i,j} = 
+\frac{1}{4} \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
+\sum_{\substack{l,l'\\l \neq l'}} \sum_{\substack{m,m'\\m \neq m'}}
+\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
+\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
+\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
+\eeq
+
+\subsection{Noise-limited Regime} \label{ssec:noise_limited}
+We consider the noise-limited regime. In this case, we assume that $N_i \gg
+P_i$, so that Equation~\ref{eq:var_cov} reduces to
+\beq \label{eq:var_cov_noise}
+\begin{split}
+\Var{\xps{i}{j}} &= N_iN_j \\
+\Cov{\xps{i}{j}}{\xps{i}{k}} &= 0 \text{.}
+\end{split}
+\eeq
+We will also assume a white noise spectrum, so that each $N_i$ is a constant
+value. In this case, the computation of the Fisher matrix is quite simple. In
+fact, we can rewrite it as
+\beq\label{eq:fisher_noisedom}
+F_{i,j} = 
+\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
+\sum_{\substack{l,l'\\l > l'}}
+\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
+\frac{1}{\Var{\hat{P}_{l,l'}(k)}}
+\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_j}\text{.}
+\eeq
+For a diagonal element, we can see that we will only get terms when $l=i$ or $l'=i$. Therefore
+\beq\label{eq:fisher_noisedom2}
+F_{i,i} = 
+\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
+\sum_{\substack{l\neq i}}
+\frac{B_l^2}{N_iN_l}\denps(k)^2\text{.}
+\eeq
+Since we are assuming a white noise power spectrum, if we define
+\begin{equation*}
+V_k = \int \frac{\text{d}k\,k^2}{2\pi^2} \denps(k)^2 V_{\text{surv}}\text{,}
+\end{equation*}
+then we can simplify Equation~\ref{eq:fisher_noisedom2} to
+\beq\label{eq:fisher_noisedom_diag}
+F_{i,i} = 
+V_k
+\sum_{\substack{l\neq i}}
+\frac{B_l^2}{N_iN_l}\text{.}
+\eeq
+For the off-diagonal case, we can see that the only term that will contribute
+is when $l=i$ and $l'=j$, or vice-versa. Therefore, we have that
+\beq\label{eq:fisher_noisedom_offdiag}
+F_{i,j} = V_k
+\frac{B_iB_j}{N_iN_j}\text{.}
+\eeq
+Note that as the number of fields increases, the diagonal elements become much
+larger than the off-diagonal elements, assuming the magnitudes of all the
+$B_i$'s and $N_i$'s are roughly similar. Therefore, the Fisher matrix becomes
+approximately diagonal, as does the covariance matrix, and the errors on the
+$B_i$'s become uncorrelated. This matches our naive expectation that
+considering additional fields should reduce the degeneracies between each
+$B_i$.
+
+\Gus{Inverting}
+
+In the case of three fields labeled $1$, $2$, and $3$, we can explicitly write
+down the Fisher matrix as
+\beq
+F = V_k
+\begin{pmatrix}
+\frac{B_2^2}{N_1N_2}+\frac{B_3^2}{N_1N_3} & \frac{B_1B_2}{N_1N_2} & \frac{B_1B_3}{N_1N_3} \\
+\frac{B_2B_1}{N_2N_1} & \frac{B_3^2}{N_2N_3}+\frac{B_1^2}{N_2N_1} & \frac{B_2B_3}{N_2N_3} \\
+\frac{B_3B_1}{N_3N_1} & \frac{B_3B_2}{N_3N_2} & \frac{B_1^2}{N_3N_1}+\frac{B_2^2}{N_3N_2}\text{.}
+\end{pmatrix}
+\eeq
 

### 2019-03-26 fisher_plots/threefield.py
Oh Lord cleanse me

@@ -17,10 +17,6 @@ class threefield(object):
         self.Blist, self.Nlist, self.nparam = self._check_BN_param_(Blist, Nlist)
 
         self.fmat = self._gen_fmat_(self.Blist, self.Nlist, self.klist, self.Pklist, 
-                                    self.nparam, self.nint)
-
-        self.explicit_fmat = self._explicit_fmat_(self.Blist, self.Nlist, self.klist, 
-                                                  self.Pklist, self.nparam, self.nint)
 
     def _gen_lin_ps_(self, kmin, kmax, nint, cosmo):
         klist = np.logspace(np.log10(kmin), np.log10(kmax), nint)
@@ -38,198 +34,6 @@ class threefield(object):
         nparam = len(Blist)
         return Blist, Nlist, nparam
 
-    def _gen_fmat_(self, Blist, Nlist, klist, Pklist, nparam, nint):
-        fmat = np.zeros((nparam, nparam, nint))
-        for i in range(nparam):
-            for j in range(nparam):
-                fmat[i][j] = self._gen_fmat_int_(i, j, Blist, Nlist, klist, Pklist)
-        
-        fmat = np.trapz(fmat, klist, axis=2)
-
-        return fmat
-
-    def _gen_fmat_int_(self, i, j, Blist, Nlist, klist, Pklist):
-        Pbiilist = np.outer(np.square(Blist), Pklist)
-        Ptotlist = np.add(Pbiilist, Nlist[:,np.newaxis])
-
-        Pbijlist = np.multiply.outer(np.outer(Blist, Blist), Pklist)
-
-        Pbideltalist = np.outer(Blist, Pklist)
-
-        if i==j:
-            term = self._gen_fmat_diag_term_(i, Blist, Ptotlist, Pbijlist, Pbideltalist, Pklist)
-        else:
-            term = self._gen_fmat_offdiag_term_(i, j, Blist, Ptotlist, Pbijlist, Pbideltalist)
-
-        factor = np.divide(np.square(klist), 2.*np.pi**2)
-        factor = np.multiply(factor, np.square(Pklist))
-        term = np.multiply(term, factor)
-
-        return term
-
-    def _gen_fmat_diag_term_(self, i, Blist, Ptot, Pbij, Pbidelta, Pklist):
[…]

### 2019-03-26 fisher_plots/threefield.py
Add threefield Fisher matrix (actually works for N fields)

@@ -2,12 +2,17 @@ import numpy as np
 from scipy.stats import chi2
 
 class threefield(object):
-    def __init__(self, z, Blist, Nlist, kmax, cosmo, kmin=1E-3, nint=1000):
+    def __init__(self, z, Blist, Nlist, kmax, Vsurv, cosmo, kmin=1E-3, nint=1000,
+                 noisedominated=True, whitenoise=True):
         
+        if not noisedominated or not whitenoise:
+            raise NotImplementedError()
+
         # store some parameters
         self.kmin, self.kmax = kmin, kmax
         self.z, self.nint = z, nint
-        self.cosmo = cosmo
+        self.Vsurv, self.cosmo = Vsurv, cosmo
+        self.noisedominated, self.whitenoise = noisedominated, whitenoise
 
         # construct linear matter power spectrum
         self.klist, self.Pklist = self._gen_lin_ps_(self.kmin, self.kmax, 
@@ -17,6 +22,8 @@ class threefield(object):
         self.Blist, self.Nlist, self.nparam = self._check_BN_param_(Blist, Nlist)
 
         self.fmat = self._gen_fmat_(self.Blist, self.Nlist, self.klist, self.Pklist, 
+                                    self.Vsurv, self.nparam, self.nint,
+                                    self.noisedominated, self.whitenoise)
 
     def _gen_lin_ps_(self, kmin, kmax, nint, cosmo):
         klist = np.logspace(np.log10(kmin), np.log10(kmax), nint)
@@ -34,6 +41,31 @@ class threefield(object):
         nparam = len(Blist)
         return Blist, Nlist, nparam
 
+    def _compute_Vk_noisedom_whitenoise_(self, klist, Pklist, Vsurv):
+        integrand = np.divide(np.square(klist*Pklist), 2.*np.pi**2)
+        Vk = np.trapz(integrand, klist)
+        return Vsurv*Vk
+
+    def _fmat_offdiag_noisedom_whitenoise_(self, i, j, Blist, Nlist):
+        return (Blist[i]*Blist[j])/(Nlist[i]*Nlist[j])
+
+    def _fmat_diag_noisedom_whitenoise_(self, i, Blist, Nlist):
+        tosum = np.square(Blist)/(Nlist[i]*Nlist)
+        tosum[i] = 0
+        return np.sum(tosum)
+
+    def _gen_fmat_(self, Blist, Nlist, klist, Pklist, Vsurv, nparam, nint,
[…]

### 2019-03-26 paper/ms.tex
Add trivial case where all B, N equal

@@
 \begin{equation*}
-V_k = \int \frac{\text{d}k\,k^2}{2\pi^2} \denps(k)^2 V_{\text{surv}}\text{,}
+V_k \equiv \int \frac{\text{d}k\,k^2}{2\pi^2} \denps(k)^2 V_{\text{surv}}\text{,}
 \end{equation*}
@@
 $B_i$.
+
+Consider the extremely trivial case such that $B_i = B$ and $N_i = N$ for all
+lines $i$. In this case, if we have $n_l$ lines, the Fisher matrix reduces to
+\beq\label{eq:fisher_supertrivial}
+        F_{i,j} = V_k \frac{B^2}{N^2} \times
+        \begin{cases}
+             n_l-1 & \text{if $i=j$} \\
+             1 &\text{if $i\neq j$} \\
+        \end{cases}\text{.}
+\eeq
+In the large $n_l$ limit, the Fisher matrix becomes diagonal, and we can
+therefore write the covariance matrix as
+\beq\label{eq:cov_supertrivial_largen}
+C_{i,j} = \frac{N^2}{V_k B^2} \frac{1}{n_l-1} \delta_{ij}\text{,}
+\eeq
+where $\delta_{ij}$ is the Kronecker delta. This leads us to the conclusion
+that in the noise-dominated regime where each line has comparable
+$\text{S}/\text{N}$, the constraining power on each line $i$ scales as
+$1/n_l$. In other words, one can improve the constraint on $B_i$ without
+executing additional observations of line $i$.
 

### 2019-03-27 fisher_plots/CO_data.py
Add CII line to CO_data

@@ -9,7 +9,7 @@ from scipy.special import gamma
 CO_lines_wave = {'1-0': 2610, '2-1': 1300, '3-2': 866, '4-3': 651,
                  '5-4': 521, '6-5': 434, '7-6': 372, '8-7': 325,
                  '9-8': 289, '10-9': 260, '11-10': 237,
-                 '12-11': 217, '13-12': 200}
+                 '12-11': 217, '13-12': 200, 'CII': 157.7}
 
 # Convert CO wavelengths to GHz
 speed_of_light = c.to_value(u.micron*u.GHz)
@@ -26,7 +26,7 @@ CO_lines = { key: speed_of_light/wave for key, wave in CO_lines_wave.items() }
 CO_L0 = {'1-0': 3.7E3, '2-1': 2.8E4, '3-2': 7E4, '4-3': 9.7E4,
          '5-4': 9.6E4, '6-5': 9.5E4, '7-6': 8.9E4, '8-7': 7.7E4,
          '9-8': 6.9E4, '10-9': 5.3E4, '11-10': 3.8E4,
-         '12-11': 2.6E4, '13-12': 1.4E4}
+         '12-11': 2.6E4, '13-12': 1.4E4, 'CII': 6E6}
 
 def _find_nearest_(array, value):
     array = np.asarray(array)

### 2019-03-27 fisher_plots/CO_predictions_threefield.py
Fix tf import, call

@@ -1,6 +1,6 @@
 import numpy as np 
 
-from threefield import gen_fisher_matrix, gen_Vk
+from threefield import threefield
 import CO_data
 from colossus.cosmology import cosmology
 
@@ -40,5 +40,4 @@ Nlist = np.array(Nlist)
 
 Vsurv = CO_data.calc_Vsurv(nuobs[0], nuemit[0], bandwidth, CO_data.survey_area[survey], cosmo)
 
-fish = gen_fisher_matrix(Blist[0], Blist[1], Blist[2],
-                         Nlist[0], Nlist[1], Nlist[2], kmax, Vsurv)
+tf = threefield(zobs, Blist, Nlist, kmax, Vsurv, cosmo)

### 2019-03-27 fisher_plots/threefield.py
Fix ps generator

@@ -15,7 +15,7 @@ class threefield(object):
         self.noisedominated, self.whitenoise = noisedominated, whitenoise
 
         # construct linear matter power spectrum
-        self.klist, self.Pklist = self._gen_lin_ps_(self.kmin, self.kmax, 
+        self.klist, self.Pklist = self._gen_lin_ps_(self.z, self.kmin, self.kmax, 
                                                     self.nint, self.cosmo)
 
         # check Blist, Nlist, make sure lengths match
@@ -25,9 +25,9 @@ class threefield(object):
                                     self.Vsurv, self.nparam, self.nint,
                                     self.noisedominated, self.whitenoise)
 
-    def _gen_lin_ps_(self, kmin, kmax, nint, cosmo):
+    def _gen_lin_ps_(self, z, kmin, kmax, nint, cosmo):
         klist = np.logspace(np.log10(kmin), np.log10(kmax), nint)
-        Pklist = cosmo.matterPowerSpectrum(klist*cosmo.h, z)
+        Pklist = cosmo.matterPowerSpectrum(klist/cosmo.h, z)
         Pklist /= cosmo.h**3
 
         return klist, Pklist

### 2019-03-27 fisher_plots/threefield.py
Fix threefield.py

@@ -67,6 +67,9 @@ class threefield(object):
                         fisher[i][j] = self._fmat_offdiag_noisedom_whitenoise_(i, j, Blist, Nlist)
             return Vk*fisher
 
+# class naive_snr(object):
+#     def __init__(self, z, B, N, kmax, )
+
 class chisq(object):
     def __init__(self, B1, B2, B3, cov_mat):
         self.B1 = B1

### 2019-03-27 paper/ms.tex
Add SN macro
Add perfect auto-ps SNR
Add some more general formulae

@@
 \newcommand{\avg}[1]{\ensuremath{\langle #1 \rangle}}
+\newcommand{\SN}{\ensuremath{\text{S}/\text{N}}}
 
@@
 \frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
-\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
+\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{.}
 \eeq
+We also note that a perfect auto-spectrum measurement will have a limit to the
+precision of a $B_i$ as
+\beq\label{eq:Bi_auto_snr}
+\text{S}/\text{N}(B_i) = \frac{B_i^2}{\sqrt{N_i}}\sqrt{V_k}\text{.}
+\eeq
+This will be useful to compare to the $\text{S}/\text{N}$ we will compute for
+the multi-field approach.
 
@@
 \eeq
-For a diagonal element, we can see that we will only get terms when $l=i$ or $l'=i$. Therefore
+For a diagonal element, we can see that we will only get terms when $l=i$ or
+$l'=i$. Therefore
 \beq\label{eq:fisher_noisedom2}
@@
 that in the noise-dominated regime where each line has comparable
-$\text{S}/\text{N}$, the constraining power on each line $i$ scales as
-$1/n_l$. In other words, one can improve the constraint on $B_i$ without
-executing additional observations of line $i$.
+\SN{}, then the \SN{} on the bias factor of each
+line can be written as
+\beq
+\SN(B) =
+\frac{B^2}{N} \sqrt{V_k(n_l-1)}
+\eeq
+
+Now let us consider a slightly more general case where $n_l \gg 1$ but we
+allow each $B_i$ and $N_i$ to be any value, each of which has $B_i^2/N_i$ to
+be of comparable value. In this case, we can approximate the Fisher matrix as
+diagonal and write
+\beq\label{eq:fisher_BiNi_samemag}
+F_{i,j} = \frac{V_k}{N_i}\delta_{ij}
+\sum_{\substack{l\neq i}}
+\frac{B_l^2}{N_l}\text{.}
+\eeq
+Inversion of this matrix is trivial, and we can therefore write down the
+$\text{S}/\text{N}$ on each bias factor as
+\beq\label{eq:snr_nlgg1}
+\text{S}/\text{N}(B_i) = \frac{B_i}{\sqrt{N_i}}
+\sqrt{V_k} \left( \sum_{l\neq i} \frac{B_l^2}{N_l}\right)^{1/2}
+\text{.}
+\eeq
+Now, suppose that of the lines $l\neq i$ one of them --- say, line $j$ --- is
+measured to much higher precision than the other lines. Then the sum is
+approximated by just the term with $l=j$, and we can approximate the \SN{}
+{$\text{S}/\text{N}$} on $B_i$ as
+\beq
+\SN(B_i) \approx \frac{B_iB_j}{\sqrt{N_iN_j}}\sqrt{V_k}\text{.}
+\eeq
+Now, compare this to the \SN{} one would expect from the auto-spectrum:
+\beq
+\frac{\SN(B_i,\text{multi-field})}{\SN(B_i,\text{auto-spectrum})} =
+\frac{B_j/\sqrt{N_j}}{B_i/\sqrt{N_i}}
+\eeq
 

### 2019-03-27 paper/ms.tex
Add SN info and comparisons for three field

@@
 \frac{B_2B_1}{N_2N_1} & \frac{B_3^2}{N_2N_3}+\frac{B_1^2}{N_2N_1} & \frac{B_2B_3}{N_2N_3} \\
-\frac{B_3B_1}{N_3N_1} & \frac{B_3B_2}{N_3N_2} & \frac{B_1^2}{N_3N_1}+\frac{B_2^2}{N_3N_2}\text{.}
+\frac{B_3B_1}{N_3N_1} & \frac{B_3B_2}{N_3N_2} & \frac{B_1^2}{N_3N_1}+\frac{B_2^2}{N_3N_2}
 \end{pmatrix}
+\text{.}
 \eeq
+We can also write down the covariance matrix on the bias factors as
+\beq
+C = F^{-1} = \frac{1}{4V_k}
+\begin{pmatrix}
+\frac{B_1^2N_2N_3 + B_2^2N_3N_1 + B_3^2N_1N_2}{B_2^2B_3^2} & \frac{-B_1^2N_2N_3 - B_2^2N_3N_1 + B_3^2N_1N_2}{B_1B_2B_3^2} & \frac{-B_1^2N_2N_3 + B_2^2N_3N_1 - B_3^2N_1N_2}{B_1B_2^2B_3} \\
+\frac{-B_1^2N_2N_3 - B_2^2N_3N_1 + B_3^2N_1N_2}{B_1B_2B_3^2} & \frac{B_1^2N_2N_3 + B_2^2N_3N_1 + B_3^2N_1N_2}{B_3^2B_1^2} & \frac{B_1^2N_2N_3 - B_2^2N_3N_1 - B_3^2N_1N_2}{B_1^2B_2B_3} \\
+\frac{B_1^2N_2N_3 - B_2^2N_3N_1 - B_3^2N_1N_2}{B_1^2B_2B_3} & \frac{B_1^2N_2N_3 - B_2^2N_3N_1 - B_3^2N_1N_2}{B_1^2B_2B_3} & \frac{B_1^2N_2N_3 + B_2^2N_3N_1 + B_3^2N_1N_2}{B_1^2B_2^2}
+\end{pmatrix}
+\text{.}
+\eeq
+The diagonal elements show that
+\beq
+\begin{split}
+C_{1,1} = \sigma_{B_1}^2 &= \frac{1}{4V_k} \left( B_1^2 \frac{N_2N_3}{B_2^2B_3^2} + N_1(\frac{N_2}{B_2^2} + \frac{N_3}{B_3^2}) \right) \\
+\implies \frac{\sigma_{B_1}^2}{B_1^2} &= \frac{1}{4V_k} \left( \frac{N_1N_2}{B_1^2B_2^2} + \frac{N_2N_3}{B_2^2B_3^2} + \frac{N_3N_1}{B_3^2B_1^2} \right)
+\end{split}
+\eeq
+Note that this equation disagrees with Equation~\ref{eq:snr_nlgg1} because in
+that case we assumed $n_l \gg 1$ and therefore ignored the off-diagonal
+elements of the Fisher matrix, whereas here $n_l=3$. The symmetry of this
+equation also leads us to the conclusion that
+\beq
+\frac{\sigma_{B_1}^2}{B_1^2} = \frac{\sigma_{B_2}^2}{B_2^2} = 
+\frac{\sigma_{B_3}^2}{B_3^2}\text{.}
+\eeq
+Unfortunately this convenient result only holds in the case $n_l=3$.
+
+In the three-field case, let us also consider the \SN{} here compared to the
+auto-spectrum case. This will be simpler to write if we introduce $\tilde{B}_i
+\equiv B_i^2/N_i$. Then
+\beq
+\frac{\SN(B_1, \text{three-field})}{\SN(B_1, \text{auto-spectrum})} =
+\frac{2}{\tilde{B}_1}
+\sqrt{\frac{\tilde{B}_1\tilde{B}_2\tilde{B}_3}{\tilde{B}_1 + \tilde{B}_2 + \tilde{B}_3}}
+\text{.}
+\eeq
+There are several interesting cases to consider with this formula.
+For starters, let us assume that each field is measured to the same precision, i.e.
+$\tilde{B}_1 = \tilde{B}_2 = \tilde{B}_3 = \tilde{B}$.
+In this case, we have that
+\beq
+\frac{\SN(B_1, \text{three-field})}{\SN(B_1, \text{auto-spectrum})} =
+\frac{2}{\sqrt{3}} \approx 1.15
+\text{.}
+\eeq
+So, the three-field approach gives a marginally better \SN{} than the
+auto-spectrum approach. Next, let us assume that the field $1$ has a much
+stronger signal strength than $2$ or $3$ --- i.e. $\tilde{B}_1 \gg
+\tilde{B}_2,\tilde{B}_3$. In this case we have that
+\beq
+\frac{\SN(B_1, \text{three-field})}{\SN(B_1, \text{auto-spectrum})} =
+2\frac{\sqrt{\tilde{B}_2\tilde{B}_3}}{\tilde{B}_1}\text{.}
+\eeq
+In this case we see that it is unlikely for the $\text{S}/\text{N}$ on $B_1$
+to be higher in the three-field case than in the auto-spectrum case. On the
+other hand, let us consider the case where one of the other lines is measured
+to much higher precision, e.g. $\tilde{B}_2 \gg \tilde{B}_1,\tilde{B}_3$. In
+this case, we have that
+\beq
+\frac{\SN(B_1, \text{three-field})}{\SN(B_1, \text{auto-spectrum})} =
+2\sqrt{\frac{\tilde{B}_3}{\tilde{B}_1}}\text{.}
+\eeq
+As long as field $1$ and $3$ are measured to comparable precision, a gain in
+the \SN{} of $\sim2$ is possible with the three-field approach. Finally, let
+us consider the most interesting case in which fields $2$ and $3$ are measured
+to much higher precision than field $1$ --- i.e. $\tilde{B}_2, \tilde{B}_3 \gg
+\tilde{B}_1$. For simplicity let us also assume that $\tilde{B}_2 \approx
+\tilde{B}_3 = \tilde{B}$. In this case, we have that
+\beq
+\frac{\SN(B_1, \text{three-field})}{\SN(B_1, \text{auto-spectrum})} =
+\sqrt{2}\sqrt{\frac{\tilde{B}}{\tilde{B}_1}}
+\text{.}
+\eeq
+As a result, we can see that if two lines are measured with strong precision,
+then we can strongly boost the \SN{} of a third, weakly measured line with the
+three-field approach.
 

### 2019-03-29 fisher_plots/CO_data.py
Add line names to CO_data

@@ -5,6 +5,9 @@ from scipy.special import gamma
 
 # basic info about the lines
 
+CO_lines_names = ['1-0', '2-1', '3-2', '4-3', '5-4', '6-5', '7-6', '8-7', '9-8',
+                  '10-9', '11-10', '12-11', '13-12', 'CII']
+
 # CO line wavelengths in microns
 CO_lines_wave = {'1-0': 2610, '2-1': 1300, '3-2': 866, '4-3': 651,
                  '5-4': 521, '6-5': 434, '7-6': 372, '8-7': 325,

### 2019-03-29 plots/freq_redshift_coverage/plot_freq_redshift_coverage.py
Add freq_redshift_coverage plot

@@ -1,0 +1,64 @@
+import sys
+sys.path.append('../../fisher_plots')
+
+import CO_data
+import numpy as np 
+import matplotlib.pyplot as plt
+
+from labellines import labelLine, labelLines
+
+import matplotlib as mpl
+from matplotlib import rc
+rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
+rc('text', usetex=True)
+mpl.rcParams['text.latex.preamble'] = [r'\usepackage{amsmath}']
+
+tb_c = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f',
+        '#edc948', '#b07aa1', '#ff9da7', '#9c755f', '#bab0ac']
+
+surveys = ['TIME', 'CONCERTO', 'CCAT-p']
+surveys_tex = [r'\textbf{TIME}', r'\textbf{CONCERTO}', r'\textbf{CCAT-p}']
+
+xrnge = [150, 525]
+yrnge = [0, 10]
+
+nuobs_list = np.linspace(xrnge[0], xrnge[1], 1000)
+
+fig, ax = plt.subplots(1, 1, figsize=(4, 6))
+
+for l in CO_data.CO_lines_names:
+    nuemit = CO_data.CO_lines[l]
+    zlist = (nuemit - nuobs_list)/nuobs_list
+    if l=='CII':
+        ax.plot(nuobs_list, zlist, label=r'$\text{C \textsc{ii}}$', c='k', lw=0.5)
+    else:
+        ax.plot(nuobs_list, zlist, label=l, c='k', lw=0.5)
+
+xlist = np.linspace(450, 460, len(CO_data.CO_lines_names))
+xlist[-1] = 490
+xlist[1] = 170
+xlist[2] = 260
+xlist[3] = 390
+labelLines(ax.get_lines(), zorder=2.5, bbox={'pad': 0.2, 'facecolor': 'white', 'edgecolor': 'white'}, 
+                           xvals=xlist, fontsize=7)
+
+for s,st,c in zip(surveys, surveys_tex, tb_c):
+    freq_range = CO_data.survey_freq_range[s]
+    ax.axvline(freq_range[0], color=c, zorder=4)
+    ax.axvline(freq_range[1], color=c, zorder=4)
+    ax.axvspan(freq_range[0], freq_range[1], color=c, alpha=0.25, zorder=4)
[…]

### 2019-04-07 fisher_plots/threefield.py
Update corner plot calc

@@ -1,5 +1,16 @@
 import numpy as np
 from scipy.stats import chi2
+import matplotlib.pyplot as plt
+from matplotlib import gridspec
+
+import matplotlib as mpl
+from matplotlib import rc
+rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
+rc('text', usetex=True)
+mpl.rcParams['text.latex.preamble'] = [r'\usepackage{amsmath}']
+
+tb_c = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f',
+        '#edc948', '#b07aa1', '#ff9da7', '#9c755f', '#bab0ac']
 
 class threefield(object):
     def __init__(self, z, Blist, Nlist, kmax, Vsurv, cosmo, kmin=1E-3, nint=1000,
@@ -100,39 +111,97 @@ class chisq(object):
         
         return chisq
 
-def corner_plot(B1, B2, B3, N1, N2, N3, kmax, Vsurv):
-    fisher_mat = gen_fisher(B1, B2, B3, N1, N2, N3, kmax, Vsurv)
+def _gaussian_(x, mu, sig):
+    return np.exp(-np.power(x - mu, 2.) / (2 * np.power(sig, 2.)))/(np.sqrt(2.*np.pi*np.square(sig)))
 
-    cov_mat = np.inverse(fisher_mat)
+def corner_plot(z, B1sq, B2sq, B3sq, N1, N2, N3, kmax, Vk, cosmo):
+    B1 = np.sqrt(B1sq)
+    B2 = np.sqrt(B2sq)
+    B3 = np.sqrt(B3sq)
 
-    b1list = np.linspace(0.7*B1, 1.3*B1, 100)
-    b2list = np.linspace(0.7*B2, 1.3*B2, 100)
-    b3list = np.linspace(0.7*B3, 1.3*B3, 100)
+    Blist = np.array([B1, B2, B3])
+    Nlist = np.array([N1, N2, N3])
+    tf = threefield(z, Blist, Nlist, kmax, 1, cosmo, Vk=Vk)
+
+    cov_mat = np.linalg.inv(tf.fmat)
+
+    b1list = np.linspace(B1-0.7, B1+0.7, 1000)
+    b2list = np.linspace(B2-0.7, B2+0.7, 1000)
[…]

### 2019-04-07 fisher_plots/threefield.py
Let user input Vk

@@ -14,14 +14,14 @@ tb_c = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f',
 
 class threefield(object):
     def __init__(self, z, Blist, Nlist, kmax, Vsurv, cosmo, kmin=1E-3, nint=1000,
-                 noisedominated=True, whitenoise=True):
+                 noisedominated=True, whitenoise=True, Vk=None):
         
         if not noisedominated or not whitenoise:
             raise NotImplementedError()
 
         # store some parameters
         self.kmin, self.kmax = kmin, kmax
-        self.z, self.nint = z, nint
+        self.z, self.nint, self.Vk = z, nint, Vk
         self.Vsurv, self.cosmo = Vsurv, cosmo
         self.noisedominated, self.whitenoise = noisedominated, whitenoise
 
@@ -34,7 +34,7 @@ class threefield(object):
 
         self.fmat = self._gen_fmat_(self.Blist, self.Nlist, self.klist, self.Pklist, 
                                     self.Vsurv, self.nparam, self.nint,
-                                    self.noisedominated, self.whitenoise)
+                                    self.noisedominated, self.whitenoise, self.Vk)
 
     def _gen_lin_ps_(self, z, kmin, kmax, nint, cosmo):
         klist = np.logspace(np.log10(kmin), np.log10(kmax), nint)
@@ -66,10 +66,11 @@ class threefield(object):
         return np.sum(tosum)
 
     def _gen_fmat_(self, Blist, Nlist, klist, Pklist, Vsurv, nparam, nint,
-                   noisedominated, whitenoise):
+                   noisedominated, whitenoise, Vk=None):
         if noisedominated and whitenoise:
             fisher = np.zeros((nparam, nparam))
-            Vk = self._compute_Vk_noisedom_whitenoise_(klist, Pklist, Vsurv)
+            if Vk is None:
+                Vk = self._compute_Vk_noisedom_whitenoise_(klist, Pklist, Vsurv)
             for i in range(nparam):
                 for j in range(nparam):
                     if i==j:

### 2019-04-07 plots/freq_redshift_coverage/plot_freq_redshift_coverage.py
Update freq redshift coverage plot

@@ -9,7 +9,7 @@ from labellines import labelLine, labelLines
 
 import matplotlib as mpl
 from matplotlib import rc
-rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
+rc('font', **{'family': 'serif', 'serif': [r'\ttdefault']})
 rc('text', usetex=True)
 mpl.rcParams['text.latex.preamble'] = [r'\usepackage{amsmath}']
 
@@ -52,8 +52,10 @@ for s,st,c in zip(surveys, surveys_tex, tb_c):
 ax.set_xlim(xrnge)
 ax.set_ylim(yrnge)
 
-ax.set_xlabel(r'$\text{\texttt{observed frequency [GHz]}}$')
-ax.set_ylabel(r'$\text{\texttt{emitted redshift}}$')
+# ax.set_xlabel(r'$\text{\texttt{observed frequency [GHz]}}$')
+# ax.set_ylabel(r'$\text{\texttt{emitted redshift}}$')
+ax.set_xlabel(r'$\text{observed frequency}\,[\,\text{GHz}\,]$')
+ax.set_ylabel(r'$\text{emitted redshift}$')
 
 fig.tight_layout()
 fig.savefig('freq_redshift_coverage.pdf')

### 2019-04-07 fisher_plots/CO_predictions_threefield.py
Add corner plot run

@@ -1,6 +1,6 @@
 import numpy as np 
 
-from threefield import threefield
+from threefield import threefield, corner_plot
 import CO_data
 from colossus.cosmology import cosmology
 
@@ -11,7 +11,7 @@ survey = 'CCAT-p'
 lines = ['6-5', '5-4', '4-3']
 
 b = 3
-bandwidth = 28
+bandwidth = 40
 kmax = 1
 
 zobs = 0.88
@@ -41,3 +41,11 @@ Nlist = np.array(Nlist)
 Vsurv = CO_data.calc_Vsurv(nuobs[0], nuemit[0], bandwidth, CO_data.survey_area[survey], cosmo)
 
 tf = threefield(zobs, Blist, Nlist, kmax, Vsurv, cosmo)
+
+fig, ax, tf = corner_plot(1, 1, 2, 3, 1, 1, 1, 1, 20, cosmo)
+fig.tight_layout()
+fig.savefig('corner_Nconstant.pdf')
+
+fig, ax, tf = corner_plot(1, 2, 2, 2, 1, 2, 3, 1, 20, cosmo)
+fig.tight_layout()
+fig.savefig('corner_Bconstant.pdf')

### 2019-04-07 paper/ms.tex
Fix S/N for auto-spectrum
Separate multi-field section

@@
 \beq\label{eq:Bi_auto_snr}
-\text{S}/\text{N}(B_i) = \frac{B_i^2}{\sqrt{N_i}}\sqrt{V_k}\text{.}
+\text{S}/\text{N}(B_i) = \frac{B_i^2}{N_i}\sqrt{V_k}\text{.}
 \eeq
@@
 the multi-field approach.
+
+\section{Three Field Case} \label{sec:three_field}
+We begin by considering the three field case. While numerically evaluating the
+Fisher matrix is straightforward for any number of lines, it is tractable to
+evaluate analytically in the three field case. Since the behavior of the
+Fisher matrix in the multi-field case is driven largely by the best measured
+line, we can understand the behavior of the general case by studying first the
+three field case.
 

### 2019-04-10 paper/ms.tex
Clear paper

--- 2019-03-27 paper/ms.tex
@@
 \begin{abstract}
-Intensity mapping stands to be a promising probe of the large-scale structure
-of the universe at high redshift ($z>3$). The experiment TIME, currently
-undergoing a preliminary engineering run, will measure [\CII] emission from
-the redshift ranges $5<z<9$ {\bf check}. An important problem to overcome will
-be to remove interloping CO lines. These are lines that are emitted at a
-different frequency than [\CII] but are observed at the same frequency from
-gas residing at a different redshift. The measurement of [\CII] will be
-impacted by emission from three CO transitions
+Abstract.
 \end{abstract}
@@
 \section{Introduction}\label{sec:intro}
-At high redshift ($z>3$) the most promising probe of the large-scale structure
-(LSS) of the universe is line intensity mapping. Rather than attempting to
-resolve individual galaxies, intensity mapping aims to measure the total
-emission from an atomic or molecular line of all galaxies within a rather
-coarse pixel. Commonly proposed lines include H$\alpha$, H$\beta$, Ly$\alpha$,
-[\CII], [\OIII], and 21~cm. During the Epoch of Reionization (EoR;
-$z\gtrsim6$), the hydrogen lines also measure the bulk emission from neutral
-hydrogen residing in the diffuse intergalactic medium (IGM).
-
-\section{Multi-field Approach}\label{sec:theory}
-We describe the multi-field approach in full generality and state some
-results. First, we assume a measurement of each of $\xps{i}{j}$. The relevant
-variance and covariances are \citep[e.g.][]{2015JCAP...03..034V}
-\beq\label{eq:var_cov}
-\begin{split}
-\Var{\xps{i}{j}} &= \xps{i}{j}^2 + \pstot{i}\pstot{j} \\
-\Cov{\xps{i}{j}}{\xps{i}{k}} &= \pstot{i}\xps{j}{k} +
-\xps{i}{j}\xps{i}{k}\text{.}
-\end{split}
-\eeq
-We are then making a measurement of each of $\xps{i}{j}$, $\xps{j}{k}$,
-and $\xps{k}{i}$. We model each of these power spectra as
-\beq
-\xps{i}{j}(k) = B_i(k) B_j(k) \denps(k)\text{.}
-\eeq
-That is, we are only working in the regime where $r_{i,j}=1$. What this
-translates to is that we may only perform this interloper removal on
-sufficiently large scales, i.e. where $k<k_{\text{max}}$, where
-$k_{\text{max}}$ is set by wherever the lines $i$ and $j$ start to
-decorrelate. The value of $k_{\text{max}}$ is the only aspect of our analysis
-that is model dependent. Only considering modes up to a $k_{\text{max}}$ is
-analogous to a similar procedure in galaxy surveys where only large-scale
-information up to a $k_{\text{max}}$ where linear theory is applicable is used.
-
-The Fisher matrix for our measurement is
-\beq\label{eq:fisher}
-F_{i,j} = 
-\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
-\sum_{\substack{l,l'\\l > l'}} \sum_{\substack{m,m'\\m > m'}}
-\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
-\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
-\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
-\eeq
-where $l$, $l'$, $m$, and $m'$ sum over all lines being considered. Note that
-we can make the substitution
-\begin{equation*}
-\sum_{\substack{l,l'\\l > l'}} \rightarrow 
-\frac{1}{2} \sum_{\substack{l,l'\\l \neq l'}}\text{,}
-\end{equation*}
-without changing the value of the Fisher matrix. Thus it will sometimes be
-easier to compute
-\beq\label{eq:fisher4}
-F_{i,j} = 
-\frac{1}{4} \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
-\sum_{\substack{l,l'\\l \neq l'}} \sum_{\substack{m,m'\\m \neq m'}}
-\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
-\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
-\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{.}
-\eeq
-We also note that a perfect auto-spectrum measurement will have a limit to the
-precision of a $B_i$ as
-\beq\label{eq:Bi_auto_snr}
-\text{S}/\text{N}(B_i) = \frac{B_i^2}{\sqrt{N_i}}\sqrt{V_k}\text{.}
-\eeq
-This will be useful to compare to the $\text{S}/\text{N}$ we will compute for
-the multi-field approach.
-
-\subsection{Noise-limited Regime} \label{ssec:noise_limited}
-We consider the noise-limited regime. In this case, we assume that $N_i \gg
-P_i$, so that Equation~\ref{eq:var_cov} reduces to
-\beq \label{eq:var_cov_noise}
-\begin{split}
-\Var{\xps{i}{j}} &= N_iN_j \\
-\Cov{\xps{i}{j}}{\xps{i}{k}} &= 0 \text{.}
-\end{split}
-\eeq
-We will also assume a white noise spectrum, so that each $N_i$ is a constant
-value. In this case, the computation of the Fisher matrix is quite simple. In
-fact, we can rewrite it as
-\beq\label{eq:fisher_noisedom}
-F_{i,j} = 
-\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
-\sum_{\substack{l,l'\\l > l'}}
-\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
-\frac{1}{\Var{\hat{P}_{l,l'}(k)}}
-\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_j}\text{.}
-\eeq
-For a diagonal element, we can see that we will only get terms when $l=i$ or
-$l'=i$. Therefore
-\beq\label{eq:fisher_noisedom2}
-F_{i,i} = 
-\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
-\sum_{\substack{l\neq i}}
-\frac{B_l^2}{N_iN_l}\denps(k)^2\text{.}
-\eeq
-Since we are assuming a white noise power spectrum, if we define
-\begin{equation*}
-V_k \equiv \int \frac{\text{d}k\,k^2}{2\pi^2} \denps(k)^2 V_{\text{surv}}\text{,}
-\end{equation*}
-then we can simplify Equation~\ref{eq:fisher_noisedom2} to
-\beq\label{eq:fisher_noisedom_diag}
-F_{i,i} = 
-V_k
-\sum_{\substack{l\neq i}}
-\frac{B_l^2}{N_iN_l}\text{.}
-\eeq
-For the off-diagonal case, we can see that the only term that will contribute
-is when $l=i$ and $l'=j$, or vice-versa. Therefore, we have that
-\beq\label{eq:fisher_noisedom_offdiag}
-F_{i,j} = V_k
-\frac{B_iB_j}{N_iN_j}\text{.}
-\eeq
-Note that as the number of fields increases, the diagonal elements become much
-larger than the off-diagonal elements, assuming the magnitudes of all the
-$B_i$'s and $N_i$'s are roughly similar. Therefore, the Fisher matrix becomes
-approximately diagonal, as does the covariance matrix, and the errors on the
-$B_i$'s become uncorrelated. This matches our naive expectation that
-considering additional fields should reduce the degeneracies between each
-$B_i$.
-
-Consider the extremely trivial case such that $B_i = B$ and $N_i = N$ for all
-lines $i$. In this case, if we have $n_l$ lines, the Fisher matrix reduces to
-\beq\label{eq:fisher_supertrivial}
-        F_{i,j} = V_k \frac{B^2}{N^2} \times
-        \begin{cases}
-             n_l-1 & \text{if $i=j$} \\
-             1 &\text{if $i\neq j$} \\
-        \end{cases}\text{.}
-\eeq
-In the large $n_l$ limit, the Fisher matrix becomes diagonal, and we can
-therefore write the covariance matrix as
-\beq\label{eq:cov_supertrivial_largen}
-C_{i,j} = \frac{N^2}{V_k B^2} \frac{1}{n_l-1} \delta_{ij}\text{,}
-\eeq
-where $\delta_{ij}$ is the Kronecker delta. This leads us to the conclusion
-that in the noise-dominated regime where each line has comparable
-\SN{}, then the \SN{} on the bias factor of each
-line can be written as
-\beq
-\SN(B) =
-\frac{B^2}{N} \sqrt{V_k(n_l-1)}
-\eeq
-
-Now let us consider a slightly more general case where $n_l \gg 1$ but we
-allow each $B_i$ and $N_i$ to be any value, each of which has $B_i^2/N_i$ to
-be of comparable value. In this case, we can approximate the Fisher matrix as
-diagonal and write
-\beq\label{eq:fisher_BiNi_samemag}
-F_{i,j} = \frac{V_k}{N_i}\delta_{ij}
-\sum_{\substack{l\neq i}}
-\frac{B_l^2}{N_l}\text{.}
-\eeq
-Inversion of this matrix is trivial, and we can therefore write down the
-$\text{S}/\text{N}$ on each bias factor as
-\beq\label{eq:snr_nlgg1}
-\text{S}/\text{N}(B_i) = \frac{B_i}{\sqrt{N_i}}
-\sqrt{V_k} \left( \sum_{l\neq i} \frac{B_l^2}{N_l}\right)^{1/2}
-\text{.}
-\eeq
-Now, suppose that of the lines $l\neq i$ one of them --- say, line $j$ --- is
-measured to much higher precision than the other lines. Then the sum is
-approximated by just the term with $l=j$, and we can approximate the \SN{}
-{$\text{S}/\text{N}$} on $B_i$ as
-\beq
-\SN(B_i) \approx \frac{B_iB_j}{\sqrt{N_iN_j}}\sqrt{V_k}\text{.}
-\eeq
-Now, compare this to the \SN{} one would expect from the auto-spectrum:
-\beq
-\frac{\SN(B_i,\text{multi-field})}{\SN(B_i,\text{auto-spectrum})} =
-\frac{B_j/\sqrt{N_j}}{B_i/\sqrt{N_i}}
-\eeq
-
-\Gus{Inverting}
-
-In the case of three fields labeled $1$, $2$, and $3$, we can explicitly write
-down the Fisher matrix as
-\beq
-F = V_k
-\begin{pmatrix}
-\frac{B_2^2}{N_1N_2}+\frac{B_3^2}{N_1N_3} & \frac{B_1B_2}{N_1N_2} & \frac{B_1B_3}{N_1N_3} \\
-\frac{B_2B_1}{N_2N_1} & \frac{B_3^2}{N_2N_3}+\frac{B_1^2}{N_2N_1} & \frac{B_2B_3}{N_2N_3} \\
-\frac{B_3B_1}{N_3N_1} & \frac{B_3B_2}{N_3N_2} & \frac{B_1^2}{N_3N_1}+\frac{B_2^2}{N_3N_2}\text{.}
-\end{pmatrix}
-\eeq
-
-\section{CO Measurements} \label{sec:co_measurements}
-\subsection{CO Modelling} \label{ssec:co_modelling}
-To model the statistical fluctuation and amplitude of the \CO{} intensity maps
-we follow \citet{2016ApJ...825..143L}, and briefly summarize the procedure
-here. We begin by assuming a Schechter form for the star formation rate
-function,
-\beq\label{eq:schechter}
-\phi(\SFR)\,\text{d}\SFR = \phi_*
-\left(\frac{\SFR}{\SFR_*}\right)^{\alpha}\exp{\left[-\frac{\SFR}{\SFR_*}\right]}
-\frac{\text{d}\SFR}{\SFR_*}
-\eeq
-where $\alpha$ is the faint-end slope, $\SFR_*$ is the characteristic
-star-formation rate, and $\phi_*$ is the characteristic number density. The
-average specific intensity in a line $l$ can be related to the comoving
-emissivity by \citep{2011ApJ...741...70L, 2013ApJ...768...15P},
-\beq\label{eq:emiss_to_int}
-\avg{I_l} = \frac{\epsilon_l}{4\pi \nu_{\text{rest},l}}\frac{c}{H(z)}\text{,}
-\eeq
-where $\nu_{\text{rest},l}$ is the rest-frame emission frequency and
-$\epsilon_l$ is the comoving emissivity, each of line $l$. Assuming a linear
-luminosity-SFR relation with a constant of proportionality of $L_0^l$, along
-with the Schechter form for the SFR function (Equation~\ref{eq:schechter}), it
-follows that \citep{2013ApJ...768...15P},
-\beq\label{eq:com_emiss}
-\epsilon_l = \phi_* L_0^{l}
-\frac{\SFR_*}{1\,\Msun\text{yr}^{-1}}\Gamma{(2+\alpha)}\text{.}
-\eeq
-We adopt the value of $L_0^{\CO}$ for each line transition from
-\citet{2010JCAP...11..016V}.
-
-\subsection{Something} \label{ssec:co_}
-We now consider the prospects of measuring the \CO{} transition using a
-multi-field approach. First, we choose to label each line with the upper
-transitional level, e.g. CO(3-2) is referred to as ``3.'' The relevant Fisher
-matrix is then,
-\beq\label{eq:co_fisher}
-F_{i,j} = 
-\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
-\sum_{\substack{l,l'\\l > l'}} \sum_{\substack{m,m'\\m > m'}}
-\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
-\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
-\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
-\eeq
-where $i$ and $j$ each refer to a line by its upper transitional level and the
-$l$, $l'$, $m$ and $m'$ sum over all lines considered.
-
-Ignoring interlopers and foreground contamination for a moment, we can
-simplify this expression as (see Appendix~\ref{app:fisher_deriv} for a
-derivation):
-\beq\label{eq:fisher_nocontam}
-\begin{split}
-F_{i,j} =&
-\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} \denps^2(k) \\
-\times & \left[ 
-\delta_{ij} \left( 
-\sum_{l\neq i} \frac{B_l^2}{\xps{i}{l}^2 + \pstot{i}\pstot{l}}
-+ \frac{1}{\pstot{i}\xps{\delta}{\delta} + \xps{i}{\delta}^2}
-\right) \right. \\
-&\left. + (1-\delta_{ij}) \left( 
-\sum_{l\neq i,j} \frac{B_l^2}{\pstot{l}\xps{i}{j} + \xps{i}{l}\xps{l}{j}}
-+\frac{B_i}{\pstot{i}\xps{j}{\delta} + \xps{i}{\delta}\xps{i}{j}}
-+ \frac{B_j}{\pstot{j}\xps{i}{\delta} + \xps{j}{\delta}\xps{i}{j}}
-+ \frac{B_iB_j}{\xps{i}{j}^2 + \pstot{i}\pstot{j}}
-\right)
-\right]\text{.}
-\end{split}
-\eeq
-Including the auto-spectra in this analysis simply requires summing over all
-$l$ values, replacing $\xps{i}{i}$ with $\pstot{i}$ \Gus{I think this is
-correct?}.
-
-\appendix
-
-\section{Fisher Matrix Derivation}\label{app:fisher_deriv}
-We show a derivation of Equation~\ref{eq:fisher_nocontam}. First, consider the
-Fisher matrix from Equation~\ref{eq:co_fisher}.
-\beq\label{eq:co_fisher_2}
-F_{i,j} = 
-\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
-\sum_{\substack{l,l'\\l > l'}} \sum_{\substack{m,m'\\m > m'}}
-\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
-\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
-\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
-\eeq
-where $i$ and $j$ each refer to a line by its upper transitional level and the
-$l$, $l'$, $m$ and $m'$ sum over all lines considered. We exploit the fact
-that the Fisher matrix is unchanged under the substitution,
-\begin{equation*}
-\sum_{\substack{l,l'\\l > l'}} \rightarrow 
-\frac{1}{2} \sum_{\substack{l,l'\\l \neq l'}}\text{.}
-\end{equation*}
-Next, we can write down the derivatives of the power spectra as,
-\beq\label{eq:psderiv}
-\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
-= \left( B_{l'} \delta_{il} + B_l\delta_{il'} \right) \denps(k)\text{.}
-\eeq
-Now we can also write down the covariance formula as,
-\beq\label{eq:cov}
-\begin{aligned}
-\left(\Cov{\hat{P}_{l,l'}}{\hat{P}_{m,m'}}\right)^{-1} = 
-&(\pstot{l}\xps{l'}{m'} + \xps{l}{l'}\xps{l}{m'})^{-1} &&\times \delta_{lm} (1-\delta_{l'm'}) \\
-&+ (\pstot{l}\xps{l'}{m} + \xps{l'}{l}\xps{l}{m})^{-1} &&\times \delta_{lm'} (1-\delta_{l'm}) \\
-&+ (\pstot{l'}\xps{l}{m'} + \xps{l'}{l}\xps{l'}{m'})^{-1} &&\times \delta_{l'm} (1-\delta_{lm'}) \\
-&+ (\pstot{l'}\xps{l}{m} + \xps{l'}{l}\xps{l'}{m})^{-1} &&\times \delta_{l'm'} (1-\delta_{lm}) \\
-&+ (\xps{l}{l'}^2 + \pstot{l}\pstot{l'})^{-1} &&\times \delta_{lm} \delta_{l'm'} \\
-&+ (\xps{l}{l'}^2 + \pstot{l}\pstot{l'})^{-1} &&\times \delta_{lm'} \delta_{l'm}\text{.}
-\end{aligned}
-\eeq
-We are at liberty to distribute the inverse to all terms since upon inspection
-of the Kronecker delta's one and only one term will contribute to the sum. In
-the case that the covariance vanishes (e.g.
-$\Cov{\hat{P}_{1,2}}{\hat{P}_{3,4}}=0$) we exclude this term from the sum in
-Equation~\ref{eq:co_fisher_2}. Since the product,
-\begin{equation*}
-\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
-% \frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
-\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}
-\end{equation*}
-is symmetric under $(l,l',m,m') \rightarrow (l',l,m',m)$\footnote{and the
-summation is as well}, we can equivalently use the following formula for the
-covariance:
-\beq\label{eq:cov_simple}
-\begin{aligned}
-\left(\Cov{\hat{P}_{l,l'}}{\hat{P}_{m,m'}}\right)^{-1} = 
-&4 (\pstot{l}\xps{l'}{m'} + \xps{l}{l'}\xps{l}{m'})^{-1} &&\times \delta_{lm} (1-\delta_{l'm'}) \\
-&+ 2(\xps{l}{l'}^2 + \pstot{l}\pstot{l'})^{-1} &&\times \delta_{lm} \delta_{l'm'}\text{.}
-\end{aligned}
-\eeq
-Combining these facts we can arrive at the following formula for the Fisher matrix:
-\beq\label{eq:co_fisher_explicity}
-\begin{split}
-F_{i,j} = 
-\frac{1}{4} \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
-\denps(k)^2
-\sum_{\substack{l,l'\\l \neq l'}} \sum_{\substack{m,m'\\m \neq m'}}
-&\left( B_{l'} \delta_{il} + B_l\delta_{il'} \right)
-\left( B_{m'} \delta_{jm} + B_m\delta_{jm'} \right) \\
-\times&\left( \frac{4}{\pstot{l}\xps{l'}{m'} + \xps{l}{l'}\xps{l}{m'}} \delta_{lm} (1-\delta_{l'm'})
-+ \frac{2}{\xps{l}{l'}^2 + \pstot{l}\pstot{l'}} \delta_{lm} \delta_{l'm'}\right)
-\text{.}
-\end{split}
-\eeq
-This formula can be expanded and simplified to give Equation~\ref{eq:fisher_nocontam}.
 

### 2019-04-11 paper/ms.tex
Update front matter
Add three field section

@@
 
+\newcommand{\ps}[1]{\ensuremath{P_{#1,#1}}}
+\newcommand{\xps}[2]{\ensuremath{P_{#1,#2}}}
+
+\newcommand{\kmax}{\ensuremath{k_{\text{max}}}}
+
 \newcommand{\mynu}[2]{\ensuremath{\nu_{#1,\text{#2}}}}
 \newcommand{\denps}{\ensuremath{P_{\delta,\delta}}}
-\newcommand{\xps}[2]{\ensuremath{P_{#1,#2}}}
 \newcommand{\pstot}[1]{\ensuremath{P_{#1,\text{tot}}}}
@@
 
-\title{CO Interlopers Eloping from [C~\textsc{ii}] Surveys}
+\title{Multi-line Intensity Mapping}
 
@@
 
+\shorttitle{Multi-line Intensity Mapping}
+\shortauthors{Beane et al.}
+
 \begin{abstract}
@@
 
+\section{Three Field Approach}\label{sec:tf}
+We begin by considering the three field approach. We first start with this
+relatively simple case to gain some intuition for the \SN{} behavior when the
+cross-spectra of multiple lines are combined.
+
+We are concerned with the problem of estimating the power spectrum of each
+line only from the three cross-spectra. To be more concrete, we model each
+auto-spectrum and cross-spectrum as,
+\beq\label{eq:auto_xps}
+\begin{split}
+\ps{i}(k,z) &= B_i(z)^2 \denps(k,z) \\
+\xps{i}{j}(k,z) &= B_i(z) B_j(z) \denps(k,z)\text{,}
+\end{split}
+\eeq
+where $B_i(z) \equiv b_i(z) \avg{I_i}(z)$. We will generally suppress the
+redshift and $k$ arguments for brevity. We can model the auto-spectra and
+cross-spectra in this way only on sufficiently large scales, i.e. only when
+$k<\kmax$ for some value of $k_{\text{max}}$. The value of \kmax{} is set by
+two conditions. First, we must have that linear biasing is a good description
+for each field $i$. This way $B_i$ for each line will be independent of $k$.
+Second, for each pair of lines $(i,j)$ we must have that $\abs{r_{i,j}(k)} =
+1$ when $k<\kmax$.
+
+Eventually it will be desirable to place constraints on $\denps(k)$. For now,
+however, we simply wish to understand how well future experiments will be able
+to determine each of $B_i$ as a function of $z$. We can proceed simply by
+computing the relevant Fisher matrix:
+\beq\label{eq:fisher_tf}
+F_{i,j} = 
+\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
+\sum_{\substack{l,l'\\l > l'}} \sum_{\substack{m,m'\\m > m'}}
+\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
+\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
+\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
+\eeq
+where the sum of $l$, $l'$, $m$, and $m'$ is over each of the three lines.
+Equation~\ref{eq:fisher_tf} can be readily modified to accomodate the case of
+more than three lines (by extending the summations to include these lines) and
+to accomodate the auto-spectra (by allowing $l=l'$ and $m=m'$ in the relevant
+summations). We will consider these cases in Sections~\Gus{x}~and~\Gus{y},
+respectively.
+
+For the variance and covariance of the power spectra, it can be shown that,
+\beq\label{eq:var_cov}
+\begin{split}
+\Var{\xps{i}{j}} &= \xps{i}{j}^2 + \pstot{i}\pstot{j} \\
+\Cov{\xps{i}{j}}{\xps{i}{k}} &= \pstot{i}\xps{j}{k} +
+\xps{i}{j}\xps{i}{k}\text{,}
+\end{split}
+\eeq
+where $\pstot{i} \equiv \ps{i} + N_i$. Note that $N_i$ contains contributions
+from instrument noise, residual foreground contamination, and
+interloping/extraloping lines. While computing the Fisher matrix numerically
+is trivial, we will first work out the noise-dominated case which has a
+somewhat tractable analytic solution.
+
 \bibliography{references}

### 2019-04-11 paper/ms.tex
Add white noise dom subsection

@@
 
+\subsection{White Noise-dominated Regime} \label{ssec:tf_noisedom}
+In the white noise-dominated regime, we have that each $N_i \gg \ps{i}$ and
+$N_i(k) = N_i$. The relevant variance and covariance formulae then reduce to,
+\beq\label{eq:var_cov}
+\begin{split}
+\Var{\xps{i}{j}} &= N_iN_j \\
+\Cov{\xps{i}{j}}{\xps{i}{k}} &= N_i\xps{j}{k}\text{.}
+\end{split}
+\eeq
+Since the covariance formula is only first order in $N_i$, we will ignore
+contributions from terms like it and only consider terms involving
+$\Var{\xps{i}{j}}$. In such a case, the formula for the Fisher matrix
+simplifies greatly and we can write it down as:
+\beq \label{eq:fmat_tf_exp}
+F = V_k^2
+\begin{pmatrix}
+\frac{B_2^2}{N_1N_2}+\frac{B_3^2}{N_1N_3} & \frac{B_1B_2}{N_1N_2} & \frac{B_1B_3}{N_1N_3} \\
+\frac{B_2B_1}{N_2N_1} & \frac{B_3^2}{N_2N_3}+\frac{B_1^2}{N_2N_1} & \frac{B_2B_3}{N_2N_3} \\
+\frac{B_3B_1}{N_3N_1} & \frac{B_3B_2}{N_3N_2} & \frac{B_1^2}{N_3N_1}+\frac{B_2^2}{N_3N_2}
+\end{pmatrix}
+\text{,}
+\eeq
+where,
+\beq \label{eq:Vk}
+V_k^2 \equiv V_{\text{surv}} \int \frac{\text{d}k\,k^2}{2\pi^2} \denps(k)^2\text{.}
+\eeq
+
+Inverting this matrix we find that the covariance matrix of the bias factors is,
+\beq \label{eq:covmat_tf_wn}
+C = F^{-1} = \frac{1}{4V_k^2}
+\begin{pmatrix}
+\frac{B_1^2N_2N_3 + B_2^2N_3N_1 + B_3^2N_1N_2}{B_2^2B_3^2} & \frac{-B_1^2N_2N_3 - B_2^2N_3N_1 + B_3^2N_1N_2}{B_1B_2B_3^2} & \frac{-B_1^2N_2N_3 + B_2^2N_3N_1 - B_3^2N_1N_2}{B_1B_2^2B_3} \\
+\frac{-B_1^2N_2N_3 - B_2^2N_3N_1 + B_3^2N_1N_2}{B_1B_2B_3^2} & \frac{B_1^2N_2N_3 + B_2^2N_3N_1 + B_3^2N_1N_2}{B_3^2B_1^2} & \frac{B_1^2N_2N_3 - B_2^2N_3N_1 - B_3^2N_1N_2}{B_1^2B_2B_3} \\
+\frac{B_1^2N_2N_3 - B_2^2N_3N_1 - B_3^2N_1N_2}{B_1^2B_2B_3} & \frac{B_1^2N_2N_3 - B_2^2N_3N_1 - B_3^2N_1N_2}{B_1^2B_2B_3} & \frac{B_1^2N_2N_3 + B_2^2N_3N_1 + B_3^2N_1N_2}{B_1^2B_2^2}
+\end{pmatrix}
+\text{.}
+\eeq
+Examining the diagonal components we have that:
+\beq \label{eq:var_bias_tf_wn}
+\begin{split}
+C_{1,1} = \sigma_{B_1}^2 &= \frac{1}{4V_k^2} \left( B_1^2 \frac{N_2N_3}{B_2^2B_3^2} + N_1(\frac{N_2}{B_2^2} + \frac{N_3}{B_3^2}) \right) \\
+\implies \frac{\sigma_{B_1}^2}{B_1^2} &= \frac{1}{4V_k^2} \left( \frac{N_1N_2}{B_1^2B_2^2} + \frac{N_2N_3}{B_2^2B_3^2} + \frac{N_3N_1}{B_3^2B_1^2} \right)\text{.}
+\end{split}
+\eeq
+The symmetry of this result implies that,
+\beq \label{eq:frac_error_same}
+\frac{\sigma_{B_1}^2}{B_1^2} = \frac{\sigma_{B_2}^2}{B_2^2} = 
+\frac{\sigma_{B_3}^2}{B_3^2}\text{.}
+\eeq
+Unfortunately the surprising result that the fractional error on each line is
+the same only holds in the three field case.
+
+Now we wish to consider how the \SN{} on each $B_i$ from the various
+cross-spectra is related to the \SN{} in the auto-spectrum case. We first
+write down the \SN{} from the auto-spectrum in the white-noise dominated
+regime:
+\beq \label{eq:autops_sn_wn}
+\SN(B_1, \text{auto-spectrum}) = \frac{B_1^2}{N_1} V_k
+\eeq
+
+Now, let us compare the \SN{} of the two approaches in various cases. This
+will be simpler to write if we introduce $\tilde{B}_i \equiv B_i^2/N_i$. Then,
+\beq
+\frac{\SN(B_1, \text{three-field})}{\SN(B_1, \text{auto-spectrum})} =
+\frac{2}{\tilde{B}_1}
+\sqrt{\frac{\tilde{B}_1\tilde{B}_2\tilde{B}_3}{\tilde{B}_1 + \tilde{B}_2 + \tilde{B}_3}}
+\text{.}
+\eeq
+There are several interesting cases to consider with this formula. For
+starters, let us assume that each field is measured to the same precision,
+i.e. $\tilde{B}_1 = \tilde{B}_2 = \tilde{B}_3 = \tilde{B}$. In this case, we
+have that
+\beq
+\frac{\SN(B_1, \text{three-field})}{\SN(B_1, \text{auto-spectrum})} =
+\frac{2}{\sqrt{3}} \approx 1.15
+\text{.}
+\eeq
+So, the three-field approach gives a marginally better \SN{} than the
+auto-spectrum approach. This is encouraging, because it means that a tentative
+auto-spectrum measurement could be checked against the value derived from the
+three-field approach. Next, let us assume that the field $1$ has a much
+stronger signal strength than $2$ or $3$ --- i.e. $\tilde{B}_1 \gg
+\tilde{B}_2,\tilde{B}_3$. In this case we have that
+\beq
+\frac{\SN(B_1, \text{three-field})}{\SN(B_1, \text{auto-spectrum})} =
+2\frac{\sqrt{\tilde{B}_2\tilde{B}_3}}{\tilde{B}_1}\text{.}
+\eeq
+In this case we see that it is unlikely for the $\text{S}/\text{N}$ on $B_1$
+to be higher in the three-field case than in the auto-spectrum case. On the
+other hand, let us consider the case where one of the other lines is measured
+to much higher precision, e.g. $\tilde{B}_2 \gg \tilde{B}_1,\tilde{B}_3$. In
+this case, we have that
+\beq
+\frac{\SN(B_1, \text{three-field})}{\SN(B_1, \text{auto-spectrum})} =
+2\sqrt{\frac{\tilde{B}_3}{\tilde{B}_1}}\text{.}
+\eeq
+As long as field $1$ and $3$ are measured to comparable precision, a gain in
+the \SN{} of $\sim2$ is possible with the three-field approach. Finally, let
+us consider the most interesting case in which fields $2$ and $3$ are measured
+to much higher precision than field $1$ --- i.e. $\tilde{B}_2, \tilde{B}_3 \gg
+\tilde{B}_1$. For simplicity let us also assume that $\tilde{B}_2 \approx
+\tilde{B}_3 = \tilde{B}$. In this case, we have that
+\beq
+\frac{\SN(B_1, \text{three-field})}{\SN(B_1, \text{auto-spectrum})} =
+\sqrt{2}\sqrt{\frac{\tilde{B}}{\tilde{B}_1}}
+\text{.}
+\eeq
+As a result, if two lines are measured with strong precision, then we can
+strongly boost the \SN{} of a third, weakly measured line with the three-field
+approach.
+
 \bibliography{references}

### 2019-04-11 paper/ms.tex
Add CO subsection and appendix

@@
 
+\subsection{\CO{} Forecasts for CCAT-p and CONCERTO} \label{ssec:forecasts_tf}
+Armed with some intuition from the simple white noise-dominated case, we now
+turn to forecasting constraints that can be placed on the CO bias factors. Our
+modelling of the \CO{} intensity as a function of redshift follows
+\citet{2016ApJ...825..143L} and is outlined in Appendix~\ref{app:co_int}. We
+assume that $b_i=3$ for each CO line.
+
+\appendix
+\section{CO Intensity Modelling} \label{app:co_int}
+To model the statistical fluctuation and amplitude of the \CO{} intensity maps
+we follow \citet{2016ApJ...825..143L}, and briefly summarize the procedure
+here. We begin by assuming a Schechter form for the star formation rate
+function,
+\beq\label{eq:schechter}
+\phi(\SFR)\,\text{d}\SFR = \phi_*
+\left(\frac{\SFR}{\SFR_*}\right)^{\alpha}\exp{\left[-\frac{\SFR}{\SFR_*}\right]}
+\frac{\text{d}\SFR}{\SFR_*}
+\eeq
+where $\alpha$ is the faint-end slope, $\SFR_*$ is the characteristic
+star-formation rate, and $\phi_*$ is the characteristic number density. The
+average specific intensity in a line $l$ can be related to the comoving
+emissivity by \citep{2011ApJ...741...70L, 2013ApJ...768...15P},
+\beq\label{eq:emiss_to_int}
+\avg{I_l} = \frac{\epsilon_l}{4\pi \nu_{\text{rest},l}}\frac{c}{H(z)}\text{,}
+\eeq
+where $\nu_{\text{rest},l}$ is the rest-frame emission frequency and
+$\epsilon_l$ is the comoving emissivity, each of line $l$. Assuming a linear
+luminosity-SFR relation with a constant of proportionality of $L_0^l$, along
+with the Schechter form for the SFR function (Equation~\ref{eq:schechter}), it
+follows that \citep{2013ApJ...768...15P},
+\beq\label{eq:com_emiss}
+\epsilon_l = \phi_* L_0^{l}
+\frac{\SFR_*}{1\,\Msun\text{yr}^{-1}}\Gamma{(2+\alpha)}\text{.}
+\eeq
+We adopt the value of $L_0^{\CO}$ for each line transition from
+\citet{2010JCAP...11..016V}.
+
 \bibliography{references}

### 2019-04-11 fisher_plots/threefield.py
Remove chisq object from threefield.py

@@ -79,39 +79,6 @@ class threefield(object):
                         fisher[i][j] = self._fmat_offdiag_noisedom_whitenoise_(i, j, Blist, Nlist)
             return Vk*fisher
 
-# class naive_snr(object):
-#     def __init__(self, z, B, N, kmax, )
-
-class chisq(object):
-    def __init__(self, B1, B2, B3, cov_mat):
-        self.B1 = B1
-        self.B2 = B2
-        self.B3 = B3
-
-        self.cov_mat = cov_mat
-
-        # self.sigma1 = np.sqrt(cov_mat[0][0])
-        # self.sigma2 = np.sqrt(cov_mat[1][1])
-        # self.sigma3 = np.sqrt(cov_mat[2][2])
-
-        # self.sigma12 = cov_mat[0][1]
-        # self.sigma23 = cov_mat[1][2]
-        # self.sigma31 = cov_mat[2][0]
-
-        # self.rho12 = self.sigma12/(self.sigma1*self.sigma2)
-        # self.rho23 = self.sigma23/(self.sigma2*self.sigma3)
-        # self.rho31 = self.sigma31/(self.sigma3*self.sigma1)
-
-    def __call__(self, b1, b2, b3, chisq):
-        d1 = b1 - self.B1
-        d2 = b2 - self.B2
-        d3 = b3 - self.B3
-        d = np.array([d1, d2, d3])
-
-        chisq = np.matmul(np.matmul(np.transpose(d), np.linalg.inv(self.cov_mat)), d)
-        
-        return chisq
-
 def _gaussian_(x, mu, sig):
     return np.exp(-np.power(x - mu, 2.) / (2 * np.power(sig, 2.)))/(np.sqrt(2.*np.pi*np.square(sig)))
 

### 2019-04-14 fisher_plots/threefield.py
Update threefield.py

@@ -82,20 +82,29 @@ class threefield(object):
 def _gaussian_(x, mu, sig):
     return np.exp(-np.power(x - mu, 2.) / (2 * np.power(sig, 2.)))/(np.sqrt(2.*np.pi*np.square(sig)))
 
-def corner_plot(z, B1sq, B2sq, B3sq, N1, N2, N3, kmax, Vk, cosmo):
-    B1 = np.sqrt(B1sq)
-    B2 = np.sqrt(B2sq)
-    B3 = np.sqrt(B3sq)
-
-    Blist = np.array([B1, B2, B3])
-    Nlist = np.array([N1, N2, N3])
-    tf = threefield(z, Blist, Nlist, kmax, 1, cosmo, Vk=Vk)
+def corner_plot(z, Blist, Nlist, cosmo, fac=1, tf=None, kmax=None, Vk=None):
+    if tf is not None:
+        pass
+    elif kmax is not None and Vk is not None:
+        tf = threefield(z, Blist, Nlist, kmax, 1, cosmo, Vk=Vk)
+    else:
+        raise Exception('tf is required or kmax and Vk are required')
 
     cov_mat = np.linalg.inv(tf.fmat)
 
-    b1list = np.linspace(B1-0.7, B1+0.7, 1000)
-    b2list = np.linspace(B2-0.7, B2+0.7, 1000)
-    b3list = np.linspace(B3-0.7, B3+0.7, 1000)
+    B1 = Blist[0]
+    B2 = Blist[1]
+    B3 = Blist[2]
+    N1 = Nlist[0]
+    N2 = Nlist[1]
+    N3 = Nlist[2]
+
+    dB1 = B1*fac
+    dB2 = B2*fac
+    dB3 = B3*fac
+    b1list = np.linspace(B1-dB1, B1+dB1, 1000)
+    b2list = np.linspace(B2-dB2, B2+dB2, 1000)
+    b3list = np.linspace(B3-dB3, B3+dB3, 1000)
 
     b12_1, b12_2 = np.meshgrid(b1list, b2list)
     b23_2, b23_3 = np.meshgrid(b2list, b3list)
@@ -123,7 +132,7 @@ def corner_plot(z, B1sq, B2sq, B3sq, N1, N2, N3, kmax, Vk, cosmo):
     contour_list_23 = [delta1chisq+np.min(chisq_23), delta2chisq+np.min(chisq_23)]
[…]

### 2019-04-14 fisher_plots/CO_predictions_threefield.py
Update CO_predictions_threefield.py

@@ -11,7 +11,7 @@ survey = 'CCAT-p'
 lines = ['6-5', '5-4', '4-3']
 
 b = 3
-bandwidth = 40
+bandwidth = 60
 kmax = 1
 
 zobs = 0.88
@@ -40,12 +40,15 @@ Nlist = np.array(Nlist)
 
 Vsurv = CO_data.calc_Vsurv(nuobs[0], nuemit[0], bandwidth, CO_data.survey_area[survey], cosmo)
 
-tf = threefield(zobs, Blist, Nlist, kmax, Vsurv, cosmo)
-
-fig, ax, tf = corner_plot(1, 1, 2, 3, 1, 1, 1, 1, 20, cosmo)
+fig, ax, _ = corner_plot(1, np.array([1, 2, 3]), np.array([1, 1, 1]), cosmo, 0.5, kmax=1, Vk=20)
 fig.tight_layout()
 fig.savefig('corner_Nconstant.pdf')
 
-fig, ax, tf = corner_plot(1, 2, 2, 2, 1, 2, 3, 1, 20, cosmo)
+fig, ax, _ = corner_plot(1, np.array([2, 2, 2]), np.array([1, 2, 3]), cosmo, 0.5, kmax=1, Vk=20)
 fig.tight_layout()
 fig.savefig('corner_Bconstant.pdf')
+
+tf = threefield(zobs, Blist, Nlist, kmax, Vsurv, cosmo)
+fig, ax, _ = corner_plot(zobs, Blist, Nlist, cosmo, 1.75, tf=tf)
+fig.tight_layout()
+fig.savefig('CO.pdf')

### 2019-04-14 fisher_plots/CO_predictions_threefield.py
Small changes to corner plots

@@ -40,11 +40,11 @@ Nlist = np.array(Nlist)
 
 Vsurv = CO_data.calc_Vsurv(nuobs[0], nuemit[0], bandwidth, CO_data.survey_area[survey], cosmo)
 
-fig, ax, _ = corner_plot(1, np.array([1, 2, 3]), np.array([1, 1, 1]), cosmo, 0.5, kmax=1, Vk=20)
+fig, ax, _ = corner_plot(1, np.array([1, 2, 3]), np.array([1, 1, 1]), cosmo, 0.4, kmax=1, Vk=20)
 fig.tight_layout()
 fig.savefig('corner_Nconstant.pdf')
 
-fig, ax, _ = corner_plot(1, np.array([2, 2, 2]), np.array([1, 2, 3]), cosmo, 0.5, kmax=1, Vk=20)
+fig, ax, _ = corner_plot(1, np.array([2, 2, 2]), np.array([1, 2, 3]), cosmo, 0.4, kmax=1, Vk=20)
 fig.tight_layout()
 fig.savefig('corner_Bconstant.pdf')
 

### 2019-04-14 fisher_plots/CO_predictions_threefield.py
Some more updates to corner plots

@@ -40,11 +40,11 @@ Nlist = np.array(Nlist)
 
 Vsurv = CO_data.calc_Vsurv(nuobs[0], nuemit[0], bandwidth, CO_data.survey_area[survey], cosmo)
 
-fig, ax, _ = corner_plot(1, np.array([1, 2, 3]), np.array([1, 1, 1]), cosmo, 0.4, kmax=1, Vk=20)
+fig, ax, _ = corner_plot(1, np.array([1, 2, 3]), np.array([1, 1, 1]), cosmo, 0.4, kmax=1, Vk=20, norm=True, intstr=True)
 fig.tight_layout()
 fig.savefig('corner_Nconstant.pdf')
 
-fig, ax, _ = corner_plot(1, np.array([2, 2, 2]), np.array([1, 2, 3]), cosmo, 0.4, kmax=1, Vk=20)
+fig, ax, _ = corner_plot(1, np.array([2, 2, 2]), np.array([1, 2, 3]), cosmo, 0.4, kmax=1, Vk=20, norm=True, intstr=True)
 fig.tight_layout()
 fig.savefig('corner_Bconstant.pdf')
 

### 2019-04-14 fisher_plots/threefield.py

@@ -82,7 +82,7 @@ class threefield(object):
 def _gaussian_(x, mu, sig):
     return np.exp(-np.power(x - mu, 2.) / (2 * np.power(sig, 2.)))/(np.sqrt(2.*np.pi*np.square(sig)))
 
-def corner_plot(z, Blist, Nlist, cosmo, fac=1, tf=None, kmax=None, Vk=None):
+def corner_plot(z, Blist, Nlist, cosmo, fac=1, tf=None, kmax=None, Vk=None, norm=False, intstr=False):
     if tf is not None:
         pass
     elif kmax is not None and Vk is not None:
@@ -102,9 +102,9 @@ def corner_plot(z, Blist, Nlist, cosmo, fac=1, tf=None, kmax=None, Vk=None):
     dB1 = B1*fac
     dB2 = B2*fac
     dB3 = B3*fac
-    b1list = np.linspace(B1-dB1, B1+dB1, 1000)
-    b2list = np.linspace(B2-dB2, B2+dB2, 1000)
-    b3list = np.linspace(B3-dB3, B3+dB3, 1000)
+    b1list = np.linspace(B1-dB1, B1+dB1, 5000)
+    b2list = np.linspace(B2-dB2, B2+dB2, 5000)
+    b3list = np.linspace(B3-dB3, B3+dB3, 5000)
 
     b12_1, b12_2 = np.meshgrid(b1list, b2list)
     b23_2, b23_3 = np.meshgrid(b2list, b3list)
@@ -132,57 +132,96 @@ def corner_plot(z, Blist, Nlist, cosmo, fac=1, tf=None, kmax=None, Vk=None):
     contour_list_23 = [delta1chisq+np.min(chisq_23), delta2chisq+np.min(chisq_23)]
     contour_list_31 = [delta1chisq+np.min(chisq_31), delta2chisq+np.min(chisq_31)]
 
-    fig = plt.figure(figsize=(5,6))
+    fig = plt.figure(figsize=(5,5.2))
     ax1 = plt.subplot(3, 3, 1)
     ax2 = plt.subplot(3, 3, 5)
     ax3 = plt.subplot(3, 3, 9)
 
-    pb1list = _gaussian_(b1list, B1, np.sqrt(cov_mat[0][0]))
-    pb2list = _gaussian_(b2list, B2, np.sqrt(cov_mat[1][1]))
[…]

### 2019-04-14 paper/ms.tex
Add thoughts section
Update ms.tex
Minor kmax changes

@@
 cross-spectra in this way only on sufficiently large scales, i.e. only when
-$k<\kmax$ for some value of $k_{\text{max}}$. The value of \kmax{} is set by
-two conditions. First, we must have that linear biasing is a good description
-for each field $i$. This way $B_i$ for each line will be independent of $k$.
-Second, for each pair of lines $(i,j)$ we must have that $\abs{r_{i,j}(k)} =
-1$ when $k<\kmax$.
+$k<\kmax$ for some value of \kmax{}. The value of \kmax{} is set by two
+conditions. First, we must have that linear biasing is a good description for
+each field $i$ so that $B_i$ for each line is independent of $k$. Second, for
+each pair of lines $(i,j)$ we must have that $\abs{r_{i,j}(k)} = 1$ when
+$k<\kmax$.
 
@@
 \citet{2016ApJ...825..143L} and is outlined in Appendix~\ref{app:co_int}. We
-assume that $b_i=3$ for each CO line.
+assume that $b_i=3$ for each \CO{} line.
+
+\section{Thoughts}
+Like doing a matched filter??? Trying to understand intuitively why this
+works. If you have a super well measured field, then its like you're God who
+knows that the density field is. Its almost like using that density field as a
+matched filter?
 

### 2019-04-15 fisher_plots/CO_predictions_threefield.py
Continue to update figures, add new one with Bhigher

@@ -40,11 +40,15 @@ Nlist = np.array(Nlist)
 
 Vsurv = CO_data.calc_Vsurv(nuobs[0], nuemit[0], bandwidth, CO_data.survey_area[survey], cosmo)
 
-fig, ax, _ = corner_plot(1, np.array([1, 2, 3]), np.array([1, 1, 1]), cosmo, 0.4, kmax=1, Vk=20, norm=True, intstr=True)
+fig, ax, _ = corner_plot(1, np.array([1, 2, 3]), np.array([100, 100, 100]), cosmo, 0.25, kmax=1, Vk=200000, norm=True, intstr=True)
 fig.tight_layout()
 fig.savefig('corner_Nconstant.pdf')
 
-fig, ax, _ = corner_plot(1, np.array([2, 2, 2]), np.array([1, 2, 3]), cosmo, 0.4, kmax=1, Vk=20, norm=True, intstr=True)
+fig, ax, _ = corner_plot(1, np.array([1, 4, 9]), np.array([100, 100, 100]), cosmo, 0.25, kmax=1, Vk=200000, norm=True, intstr=True)
+fig.tight_layout()
+fig.savefig('corner_Nconstant_Bhigher.pdf')
+
+fig, ax, _ = corner_plot(1, np.array([2, 2, 2]), np.array([100, 200, 300]), cosmo, 0.4, kmax=1, Vk=200000, norm=True, intstr=True)
 fig.tight_layout()
 fig.savefig('corner_Bconstant.pdf')
 

### 2019-04-15 paper/ms.tex
Add Nconstant fig to paper

@@
 
+\begin{figure}[h!]
+\begin{center}
+\includegraphics{fig/corner_Nconstant.pdf}
+\end{center}
+\caption{Caption.}
+\label{fig:tf_Nconst}
+\end{figure}
+
+As an illustration, we construct a corner plot in Figure~\ref{fig:tf_Nconst}
+for the inferred bias values using toy values of $B_1^2 = 1$, $B_2^2 = 2$, and
+$B_3^2 = 3$ along with $N_1, N_2, N_3 = 100$ and $V_k^2 = 2\times10^6$. The
+units here are arbitrary. Since each line has the same value of $N$, the \SN{}
+of each line is driven by the value of $B_i$, with $B_3$ having the highest
+intrinsic \SN{} and $B_1$ the lowest. We make the same assumptions that go
+into Equation~\ref{eq:fmat_tf_exp}, i.e. that we are white-noise dominated in
+each line.B y plotting each axis as a fraction of the true value for each of
+$B_1$, $B_2$, and $B_3$, we see that the marginalized posterior on each bias
+factor is the same (\textit{diagonal panels}). This is equivalent to saying
+that the fractional error on each bias factor is the same for each line.
+
+Moving on to the joint panels in Figure~\ref{fig:tf_Nconst}, we see that there
+is a strong negative covariance between $B_2$ and $B_3$, a mildly negative
+covariance between $B_3$ and $B_1$, and a mildly positive covariance between
+$B_1$ and $B_2$. We can intuitively understand this behavior by considering
+that each cross-spectrum places a prior on the product $B_1B_2$, $B_2B_3$, and
+$B_3B_1$, with the width of that prior given by the \SN{} of that
+cross-spectrum.
+
+In this toy scenario, the product $B_2B_3$ will have the highest \SN{} and
+therefore the tightest prior, and therefore to account for a larger $B_3$ one
+must have a smaller $B_2$ (and vice-versa), hence the strong negative
+correlation. We can make this argument for the relationship between $B_2$ and
+$B_3$ since $B_2B_3$ has the tightest prior, and therefore the products
+$B_1B_2$ and $B_3B_1$ are not relevant, since they have wider priors. The next
+tighest prior is on the product $B_3B_1$. Increasing the value of $B_1$ means
+that we must decrease the value of $B_3$ to keep $B_3B_1$ constant. Since
+$B_2B_3$ has a tighter prior, this means that we must also decrease the value
+of $B_2$. The prior on $B_1B_2$ is irrelevant, since it is wider than the
+other two.\footnote{Although in this case, to keep $B_1B_2$ constant while
+increasing $B_1$ we would need to decrease $B_2$ anyways.}
+
+Finally, we turn to the product $B_1B_2$, which has the widest prior of the
+three products. If we increase $B_1$, then naively we would need to decrease
+$B_2$. However, increasing $B_1$ also means that we must decrease $B_3$ to
+keep $B_3B_1$ constant. Furthermore, decreasing $B_3$ means that we must
+increase $B_2$ to keep $B_2B_3$ constant. Since the priors on $B_2B_3$ and
+$B_3B_1$ are tighter than on $B_1B_2$, these constraints dominate, and as a
+result increasing $B_1$ means that we must increase $B_2$. Therefore, $B_1$
+and $B_2$ are positively correlated.
+
 \subsection{\CO{} Forecasts for CCAT-p and CONCERTO} \label{ssec:forecasts_tf}

### 2019-04-15 paper/ms.tex
Add Bhigher fig to paper

@@
 
+\begin{figure}[h!]
+\begin{center}
+\includegraphics{fig/corner_Nconstant_Bhigher.pdf}
+\end{center}
+\caption{Caption.}
+\label{fig:tf_Nconst_Bhigher}
+\end{figure}
+
 As an illustration, we construct a corner plot in Figure~\ref{fig:tf_Nconst}
@@
 and $B_2$ are positively correlated.
+
+In Figure~\ref{fig:tf_Nconst_Bhigher} we perform the same procedure, except
+now we slightly increase the intrinsic \SN{} of $B_2$ and $B_3$ by setting
+$B_2^2 = 4$ and $B_3^2 = 9$. Notice that we have not changed the intrinsic
+\SN{} of field $1$. Two things are apparent. First, the strength of the
+correlations that we discussed for Figure~\ref{fig:tf_Nconst} are stronger,
+since the different priors have become more disparate in their relative
+tightness. Second, as a consequence of the fractional \SN{} being the same for
+each line, we see that the error on $B_1$ has become much smaller (and
+similarly for $B_2$ and $B_3$). However, this is particularly interesting in
+the case of $B_1$. No modification has been made to it's intrinsic \SN{} (or,
+in other words, no additional measurements have been made of line $1$).
+Nonetheless, the \SN{} on the inferred $B_1$ has become higher.
 

### 2019-04-15 fisher_plots/threefield.py
Remove yticks from corner plots

@@ -171,6 +171,7 @@ def corner_plot(z, Blist, Nlist, cosmo, fac=1, tf=None, kmax=None, Vk=None, norm
     for bl,f,x in zip([b1list, b2list, b3list], [fac1,fac2,fac3],[ax1, ax2, ax3]):
         x.set_xlim([np.min(bl)/f, np.max(bl)/f])
         x.set_yticklabels([])
+        x.set_yticks([])
         x.set_ylim(bottom=0)
 
     if intstr:

### 2019-04-15 paper/fig/update_fig.sh
Change from soft links to copies for paper figs

@@ -1,0 +1,4 @@
+#!/bin/bash
+
+cp ../../fisher_plots/corner_Nconstant.pdf .
+cp ../../fisher_plots/corner_Nconstant_Bhigher.pdf .

### 2019-04-15 paper/ms.tex
Make thoughts section more clear
Add caption to both figs

@@
 \end{center}
-\caption{Caption.}
+\caption{A toy corner plot showing the degeneracies between different lines
+with different intrinsic \SN{} ratios under the white-noise dominated
+assumption. We set $B_1^2 = 1$, $B_2^2 = 2$, and $B_3^2 = 3$ along with $N_1,
+N_2, N_3 = 100$ and $V_k^2 = 2\times10^6$. Since each line has the same value
+of $N$, the \SN{} of each line is driven by the value of $B_i$, with $B_3$
+having the highest intrinsic \SN{} and $B_1$ the lowest. We plot each axis as
+a fraction of the true value for each of $B_1$, $B_2$, and $B_3$, and see that
+the marginalized posterior on each bias factor is the same (\textit{diagonal
+panels}) as we expect from Equation~\ref{eq:frac_error_same}. There is a
+strong negative covariance between $B_2$ and $B_3$, a mildly negative
+covariance between $B_3$ and $B_1$, and a mildly positive covariance between
+$B_1$ and $B_2$. An explanation for this behavior is given in the text.}
 \label{fig:tf_Nconst}
@@
 \end{center}
-\caption{Caption.}
+\caption{We perform the same procedure as in Figure~\ref{fig:tf_Nconst}, except
+now we slightly increase the intrinsic \SN{} of $B_2$ and $B_3$ by setting
+$B_2^2 = 4$ and $B_3^2 = 9$. The values for each $N_i$ and $V_k$ are the same
+as in Figure~\ref{fig:tf_Nconst}. We see that even though nothing about line
+$1$ has changed (i.e. no additional measurements of line $1$ have been made),
+the \SN{} on $B_1$ has improved because the fractional error on each line must
+be the same (Equation~\ref{eq:frac_error_same}). The degeneracies between the
+different lines discussed in Figure~\ref{fig:tf_Nconst} become stronger in
+this case.}
 \label{fig:tf_Nconst_Bhigher}
@@
 into Equation~\ref{eq:fmat_tf_exp}, i.e. that we are white-noise dominated in
-each line.B y plotting each axis as a fraction of the true value for each of
+each line. By plotting each axis as a fraction of the true value for each of
 $B_1$, $B_2$, and $B_3$, we see that the marginalized posterior on each bias
@@
 
-\section{Thoughts}
+\section{Random Thoughts}
 Like doing a matched filter??? Trying to understand intuitively why this

### 2019-04-15 fisher_plots/CO_predictions_threefield.py
More updates to figures

@@ -53,6 +53,13 @@ fig.tight_layout()
 fig.savefig('corner_Bconstant.pdf')
 
 tf = threefield(zobs, Blist, Nlist, kmax, Vsurv, cosmo)
-fig, ax, _ = corner_plot(zobs, Blist, Nlist, cosmo, 1.75, tf=tf)
+labels = [r'$B_{6-5}\,[\,\text{Jy}/\text{str}\,]$', r'$B_{5-4}\,[\,\text{Jy}/\text{str}\,]$', 
+          r'$B_{4-3}\,[\,\text{Jy}/\text{str}\,]$']
+fig, ax, _ = corner_plot(zobs, Blist, Nlist, cosmo, 1.75, tf=tf, labels=labels, printtext=False)
 fig.tight_layout()
 fig.savefig('CO.pdf')
+
+print('for CCAT-p, lines:', lines)
+print('Blist:', Blist)
+print('Nlist:', Nlist)
+

### 2019-04-15 fisher_plots/threefield.py

@@ -82,7 +82,8 @@ class threefield(object):
 def _gaussian_(x, mu, sig):
     return np.exp(-np.power(x - mu, 2.) / (2 * np.power(sig, 2.)))/(np.sqrt(2.*np.pi*np.square(sig)))
 
-def corner_plot(z, Blist, Nlist, cosmo, fac=1, tf=None, kmax=None, Vk=None, norm=False, intstr=False):
+def corner_plot(z, Blist, Nlist, cosmo, fac=1, tf=None, kmax=None, Vk=None, norm=False, labels=None, intstr=False, 
+                printtext=True):
     if tf is not None:
         pass
     elif kmax is not None and Vk is not None:
@@ -168,8 +169,12 @@ def corner_plot(z, Blist, Nlist, cosmo, fac=1, tf=None, kmax=None, Vk=None, norm
     ax23 = plt.subplot(3, 3, 8, sharex=ax2)
     ax31 = plt.subplot(3, 3, 7, sharex=ax1, sharey=ax23)
 
+    for x in [ax12, ax23, ax31]:
+        x.locator_params('x', nbins=5)
+
     for bl,f,x in zip([b1list, b2list, b3list], [fac1,fac2,fac3],[ax1, ax2, ax3]):
         x.set_xlim([np.min(bl)/f, np.max(bl)/f])
+        x.locator_params('x', nbins=5)
         x.set_yticklabels([])
         x.set_yticks([])
         x.set_ylim(bottom=0)
@@ -189,12 +194,13 @@ def corner_plot(z, Blist, Nlist, cosmo, fac=1, tf=None, kmax=None, Vk=None, norm
         N2str = "{:.2E}".format(N2)
         N3str = "{:.2E}".format(N3)
 
-    ax1.text(0.05, 1.2, r'$B_1^2='+B1str+r'$' , transform=ax1.transAxes, in_layout=True)
-    ax1.text(0.05, 1.05, r'$N_1='+N1str+r'$' , transform=ax1.transAxes, in_layout=True)
-    ax2.text(0.05, 1.2, r'$B_2^2='+B2str+r'$' , transform=ax2.transAxes, in_layout=False)
-    ax2.text(0.05, 1.05, r'$N_2='+N2str+r'$' , transform=ax2.transAxes, in_layout=False)
[…]

### 2019-04-15 fisher_plots/CO_predictions_threefield.py
Change name of CO fig

@@ -57,7 +57,7 @@ labels = [r'$B_{6-5}\,[\,\text{Jy}/\text{str}\,]$', r'$B_{5-4}\,[\,\text{Jy}/\te
           r'$B_{4-3}\,[\,\text{Jy}/\text{str}\,]$']
 fig, ax, _ = corner_plot(zobs, Blist, Nlist, cosmo, 1.75, tf=tf, labels=labels, printtext=False)
 fig.tight_layout()
-fig.savefig('CO.pdf')
+fig.savefig('CO_tf.pdf')
 
 print('for CCAT-p, lines:', lines)
 print('Blist:', Blist)

### 2019-04-15 paper/fig/update_fig.sh
Update paper/fig/

@@ -2,3 +2,4 @@
 
 cp ../../fisher_plots/corner_Nconstant.pdf .
 cp ../../fisher_plots/corner_Nconstant_Bhigher.pdf .
+cp ../../fisher_plots/CO_tf.pdf .

### 2019-04-15 fisher_plots/multifield.py
Create multifield.py, bare min from threefield.py

@@ -1,0 +1,56 @@
+import numpy as np
+import itertools
+
+class threefield(object):
+    def __init__(self, z, Blist, Nlist, kmax, Vsurv, cosmo, kmin=1E-3, nint=1000,
+                 noisedominated=True, whitenoise=True, Vk=None):
+        
+        if not noisedominated or not whitenoise:
+            raise NotImplementedError()
+
+        # store some parameters
+        self.kmin, self.kmax = kmin, kmax
+        self.z, self.nint, self.Vk = z, nint, Vk
+        self.Vsurv, self.cosmo = Vsurv, cosmo
+
+        # construct linear matter power spectrum
+        self.klist, self.Pklist = self._gen_lin_ps_(self.z, self.kmin, self.kmax, 
+                                                    self.nint, self.cosmo)
+
+        # check Blist, Nlist, make sure lengths match
+        self.Blist, self.Nlist, self.nparam = self._check_BN_param_(Blist, Nlist)
+
+        self.fmat = self._gen_fmat_(self.Blist, self.Nlist, self.klist, self.Pklist, 
+                                    self.Vsurv, self.nparam, self.nint,
+                                    self.noisedominated, self.whitenoise, self.Vk)
+
+    def _gen_lin_ps_(self, z, kmin, kmax, nint, cosmo):
+        klist = np.logspace(np.log10(kmin), np.log10(kmax), nint)
+        Pklist = cosmo.matterPowerSpectrum(klist/cosmo.h, z)
+        Pklist /= cosmo.h**3
+
+        return klist, Pklist
+
+    def _check_BN_param_(self, Blist, Nlist):
+        # check Blist, Nlist, make sure lengths match
+        Blist = np.asarray(Blist)
+        Nlist = np.asarray(Nlist)
+        assert len(Blist) == len(Nlist), "Bias and noise lists are different length!"
+                                                    
+        nparam = len(Blist)
+        return Blist, Nlist, nparam
+
+if __name__ == '__main__':
+    from colossus.cosmology import cosmology
+
+    params = {'flat': True, 'H0': 70, 'Om0': 0.27, 'Ob0': 0.046, 'sigma8': 0.8, 'ns': 1.0}
+    cosmo = cosmology.setCosmology('myCosmo', params)
+
+    z = 0.88
+    kmax = 1
+
+    Blist = [1, 2, 3]
+    Nlist = [1, 2, 3]
+    Vsurv = 1
+
+    mf = multifield(z, Blist, Nlist, kmax, Vsurv, cosmo)

### 2019-04-15 fisher_plots/multifield.py
Add function to gen varij, covijk

@@ -20,6 +20,9 @@ class threefield(object):
         # check Blist, Nlist, make sure lengths match
         self.Blist, self.Nlist, self.nparam = self._check_BN_param_(Blist, Nlist)
 
+        self.varij, self.covijk = self._gen_var_cov_(self.Blist, self.Nlist, self.Pklist,
+                                                     self.nparam, self.nint)
+
         self.fmat = self._gen_fmat_(self.Blist, self.Nlist, self.klist, self.Pklist, 
                                     self.Vsurv, self.nparam, self.nint,
                                     self.noisedominated, self.whitenoise, self.Vk)
@@ -39,6 +42,40 @@ class threefield(object):
                                                     
         nparam = len(Blist)
         return Blist, Nlist, nparam
+
+    def _gen_varij_covijk_(Blist, Nlist, Pklist, nparam, nint):
+        BPi = np.reshape(Blist, (nparam, 1))
+        PkPi = np.reshape(Pklist, (1, nint))
+        PkPi = np.repeat(PkPi, nparam, axis=0)
+        Pi = np.multiply(np.square(BPi), PkPi)
+
+        Bouter = np.reshape(np.outer(Blist, Blist), (nparam, nparam, 1))
+        Pkrepeat = np.reshape(Pklist, (1, 1, nint))
+        Pkrepeat = np.repeat(Pkrepeat, nparam, axis=0)
+        Pkrepeat = np.repeat(Pkrepeat, nparam, axis=1)
+        Pij = np.multiply(Bouter, Pkrepeat)
+
+        NPitot = np.reshape(Nlist, (nparam, 1))
+        NPitot = np.repeat(NPitot, nint, axis=1)
+        Pitot = np.add(Pi, NPitot)
+
+        t = np.multiply.outer(Pitot, Pitot)
+        PitotPjtot = np.diagonal(t, axis1=1, axis2=3)
+
+        varij = np.add(np.square(Pij), PitotPjtot)
+
+
+        t = np.multiply.outer(Pitot, Pij)
+        PitotPjk = np.diagonal(t, axis1=1, axis2=4)
+
+        t = np.multiply.outer(Pij, Pij)
+        t2 = np.diagonal(t, axis1=0, axis2=3)
+        t3 = np.diagonal(t2, axis1=1, axis2=3)
+        PijPik = np.swapaxes(t3, 0, 2)
+
+        covijk = np.add(PitotPjk, PijPik)
+
[…]

### 2019-04-15 fisher_plots/multifield.py
Add Chung to references.bib

@@ -77,6 +77,9 @@ class threefield(object):
 
         return varij, covijk, np.square(Pij), PitotPjtot, PitotPjk, PijPik
 
+
+    def _gen_fmat_(self, Blist, Nlist, klist, Pklist, Vsurv)
+
 if __name__ == '__main__':
     from colossus.cosmology import cosmology
 

### 2019-04-15 paper/ms.tex
Change to SNR instead of SNR^2
Update preamble
Move figures around
Add section on simple CO forecasts (at one z)

@@
 
+\newcommand{\MHz}{\ensuremath{\text{MHz}}}
 \newcommand{\GHz}{\ensuremath{\text{GHz}}}
@@
 \beq \label{eq:frac_error_same}
-\frac{\sigma_{B_1}^2}{B_1^2} = \frac{\sigma_{B_2}^2}{B_2^2} = 
-\frac{\sigma_{B_3}^2}{B_3^2}\text{.}
+\frac{\sigma_{B_1}}{B_1} = \frac{\sigma_{B_2}}{B_2} = 
+\frac{\sigma_{B_3}}{B_3}\text{.}
 \eeq
@@
 the same only holds in the three field case.
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics{fig/corner_Nconstant.pdf}
+\end{center}
+\caption{A toy corner plot showing the degeneracies between different lines
+with different intrinsic \SN{} ratios under the white-noise dominated
+assumption. We set $B_1^2 = 1$, $B_2^2 = 2$, and $B_3^2 = 3$ along with $N_1,
+N_2, N_3 = 100$ and $V_k^2 = 2\times10^6$. Since each line has the same value
+of $N$, the \SN{} of each line is driven by the value of $B_i$, with $B_3$
+having the highest intrinsic \SN{} and $B_1$ the lowest. We plot each axis as
+a fraction of the true value for each of $B_1$, $B_2$, and $B_3$, and see that
+the marginalized posterior on each bias factor is the same (\textit{diagonal
+panels}) as we expect from Equation~\ref{eq:frac_error_same}. There is a
+strong negative covariance between $B_2$ and $B_3$, a mildly negative
+covariance between $B_3$ and $B_1$, and a mildly positive covariance between
+$B_1$ and $B_2$. An explanation for this behavior is given in the text.}
+\label{fig:tf_Nconst}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics{fig/corner_Nconstant_Bhigher.pdf}
+\end{center}
+\caption{We perform the same procedure as in Figure~\ref{fig:tf_Nconst}, except
+now we slightly increase the intrinsic \SN{} of $B_2$ and $B_3$ by setting
+$B_2^2 = 4$ and $B_3^2 = 9$. The values for each $N_i$ and $V_k$ are the same
+as in Figure~\ref{fig:tf_Nconst}. We see that even though nothing about line
+$1$ has changed (i.e. no additional measurements of line $1$ have been made),
+the \SN{} on $B_1$ has improved because the fractional error on each line must
+be the same (Equation~\ref{eq:frac_error_same}). The degeneracies between the
+different lines discussed in Figure~\ref{fig:tf_Nconst} become stronger in
+this case.}
+\label{fig:tf_Nconst_Bhigher}
+\end{figure}
 
@@
 
-\begin{figure}[h!]
-\begin{center}
-\includegraphics{fig/corner_Nconstant.pdf}
-\end{center}
-\caption{A toy corner plot showing the degeneracies between different lines
-with different intrinsic \SN{} ratios under the white-noise dominated
-assumption. We set $B_1^2 = 1$, $B_2^2 = 2$, and $B_3^2 = 3$ along with $N_1,
-N_2, N_3 = 100$ and $V_k^2 = 2\times10^6$. Since each line has the same value
-of $N$, the \SN{} of each line is driven by the value of $B_i$, with $B_3$
-having the highest intrinsic \SN{} and $B_1$ the lowest. We plot each axis as
-a fraction of the true value for each of $B_1$, $B_2$, and $B_3$, and see that
-the marginalized posterior on each bias factor is the same (\textit{diagonal
-panels}) as we expect from Equation~\ref{eq:frac_error_same}. There is a
-strong negative covariance between $B_2$ and $B_3$, a mildly negative
-covariance between $B_3$ and $B_1$, and a mildly positive covariance between
-$B_1$ and $B_2$. An explanation for this behavior is given in the text.}
-\label{fig:tf_Nconst}
-\end{figure}
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics{fig/corner_Nconstant_Bhigher.pdf}
-\end{center}
-\caption{We perform the same procedure as in Figure~\ref{fig:tf_Nconst}, except
-now we slightly increase the intrinsic \SN{} of $B_2$ and $B_3$ by setting
-$B_2^2 = 4$ and $B_3^2 = 9$. The values for each $N_i$ and $V_k$ are the same
-as in Figure~\ref{fig:tf_Nconst}. We see that even though nothing about line
-$1$ has changed (i.e. no additional measurements of line $1$ have been made),
-the \SN{} on $B_1$ has improved because the fractional error on each line must
-be the same (Equation~\ref{eq:frac_error_same}). The degeneracies between the
-different lines discussed in Figure~\ref{fig:tf_Nconst} become stronger in
-this case.}
-\label{fig:tf_Nconst_Bhigher}
-\end{figure}
-
 As an illustration, we construct a corner plot in Figure~\ref{fig:tf_Nconst}
@@
 
-\subsection{\CO{} Forecasts for CCAT-p and CONCERTO} \label{ssec:forecasts_tf}
+\subsection{Three-field \CO{} Forecasts for CCAT-p} \label{ssec:forecasts_tf}
+\begin{figure}[h!]
+\begin{center}
+\includegraphics{fig/CO_tf.pdf}
+\end{center}
+\caption{Constraints that can be placed on the fluctuations of the \CO(6-5),
+\CO(5-4), and \CO(4-3) lines with CCAT-p at $z_{\text{obs}} = 0.88$. This
+Figure is purely illustrative, as we do not include noise contributions from
+residual foreground contamination or interloper/extraloper lines. According to
+our simple \CO{} model, we have that $B_{\text{6-5}}, B_{\text{5-4}},
+B_{\text{4-3}} = 151, 183, 232\,\text{Jy}/\text{str}$. Using the instrumental
+specifications in \citet{2018arXiv181208135C}, we find that $N_{\text{6-5}},
+N_{\text{5-4}}, N_{\text{4-3}} = 5.1\times10^9, 1.4\times10^9,
+5.4\times10^8\,\left(\text{Jy}/\text{str}\right)^2\,\Mpc^3$. We find the same
+behavior as in Figure~\ref{fig:tf_Nconst}, where the best-measured line is
+strongly negatively degenerate with the second-best measured line, the
+best-measured and worst-measured are slightly negatively degenerate, and the
+second-best measured line and the worst-measured are slightly positively
+degenerate. }
+\label{fig:CO_tf}
+\end{figure}
+
 Armed with some intuition from the simple white noise-dominated case, we now
-turn to forecasting constraints that can be placed on the CO bias factors. Our
-modelling of the \CO{} intensity as a function of redshift follows
+turn to forecasting constraints that can be placed on the \CO{} bias factors.
+Our modelling of the \CO{} intensity as a function of redshift follows
 \citet{2016ApJ...825..143L} and is outlined in Appendix~\ref{app:co_int}. We
 assume that $b_i=3$ for each \CO{} line.
+
+At $z=0.88$, the lines \CO(6-5) ($\nu_{\text{obs}} = 367\,\MHz$), \CO(5-4)
+($\nu_{\text{obs}} = 306\,\MHz$), and \CO(4-3) ($\nu_{\text{obs}} =
+245\,\MHz$) are all in the observing band of CCAT-p. We only include
+instrumental noise for this Subsection, neglecting foreground and
+interloper/extraloper contamination. We simply want to place the result of
+Section~\ref{ssec:tf_noisedom} in the context of an actual experiment.
+
+Using our \CO{} modelling, we find that $B_{\text{6-5}}, B_{\text{5-4}},
+B_{\text{4-3}} = 151, 183, 232\,\text{Jy}/\text{str}$ at $z=0.88$. Using the
+instrumental specifications in \citet{2018arXiv181208135C}, we find that
+$N_{\text{6-5}}, N_{\text{5-4}}, N_{\text{4-3}} = 5.1\times10^9,
+1.4\times10^9, 5.4\times10^8\,\left(\text{Jy}/\text{str}\right)^2\,\Mpc^3$. We
+assume the instrumental noise is white, but note that in this case the
+noise-dominated assumption is mildly broken. The worst case is that of the
+\CO(4-3) line, where on a scale of $k\sim0.01\,\Mpc^{-1}$ we have that
+$P_{\text{4-3}} \sim 3N_{\text{4-3}}$. Again, this Subsection is purely
+illustrative, and we will rectify these assumptions in the next Section.
+
+We assume a bandwidth of $60\,\MHz$ for the line \CO(6-5). This corresponds to
+a redshift band of width $\Delta z = 0.16$. We resize the \CO(5-4) and
+\CO(4-3) bands to have the same extent in redshift space, which means slightly
+scaling the frequency bandwidth --- in this case, the bandwidths are $50$ and
+$40\,\MHz$, respectively. In Figure~\ref{fig:CO_tf} we show the constraints
+that can be placed on each of $B_{\text{6-5}}$, $B_{\text{5-4}}$, and
+$B_{\text{4-3}}$. The line \CO(4-3) is measured to the best intrinsic \SN{},
+followed by \CO(5-4) and then \CO(6-5). We find the same behavior as in
+Section~\ref{ssec:tf_noisedom}, where the best-measured line is strongly
+negatively degenerate with the second-best measured line, the best-measured
+and worst-measured are slightly negatively degenerate, and the second-best
+measured line and the worst-measured are slightly positively degenerate.
+However, we find that CCAT-p should be able to make a measurement of each bias
+factor using the three-field approach.
 

### 2019-04-26 fisher_plots/CO_predictions_mf.py
Move CO predictions to CO_predictions_mf.py

@@ -1,0 +1,38 @@
+import numpy as np 
+
+import sys
+sys.path.append('../')
+
+from multifield import threefield, corner_plot
+import CO_data
+from colossus.cosmology import cosmology
+
+params = {'flat': True, 'H0': 70, 'Om0': 0.27, 'Ob0': 0.046, 'sigma8': 0.8, 'ns': 1.0}
+cosmo = cosmology.setCosmology('myCosmo', params)
+
+def three_fields_corner_plot():
+    survey = 'CCAT-p'
+    lines = ['6-5', '5-4', '4-3']
+    
+    b = 3
+    bandwidth = 60
+    kmax = 1
+    
+    zobs = 0.88
+    nuemit = np.array([CO_data.CO_lines[l] for l in lines])
+    nuobs = nuemit / (1.+zobs)
+
+    Vsurv = CO_data.calc_Vsurv(nuobs[0], nuemit[0], bandwidth, CO_data.survey_area[survey], cosmo)
+    
+    Blist, Nlist = CO_data.gen_Blist_Nlist(3, bandwidth, kmax, zobs, lines, survey, cosmo)
+
+    tf = threefield(zobs, Blist, Nlist, kmax, Vsurv, cosmo)
+    labels = [r'$B_{6-5}\,[\,\text{Jy}/\text{str}\,]$', r'$B_{5-4}\,[\,\text{Jy}/\text{str}\,]$', 
+              r'$B_{4-3}\,[\,\text{Jy}/\text{str}\,]$']
+    fig, ax, _ = corner_plot(zobs, Blist, Nlist, cosmo, 1.75, tf=tf, labels=labels, printtext=False)
+    fig.tight_layout()
+    fig.savefig('CO_tf.pdf')
+
+
+if __name__ == '__main__':
+    three_fields_corner_plot()

### 2019-04-26 plots/fisher_plots/CO_predictions_mf.py
Move fisher_plots into plots folder

@@ -1,7 +1,7 @@
 import numpy as np 
 
 import sys
-sys.path.append('../')
+sys.path.append('../../')
 
 from multifield import threefield, corner_plot
 import CO_data

### 2019-04-26 plots/fisher_plots/CO_predictions_mf.py
Add SN at all z plot

@@ -3,12 +3,28 @@ import numpy as np
 import sys
 sys.path.append('../../')
 
-from multifield import threefield, corner_plot
+from multifield import multifield, threefield, corner_plot
 import CO_data
 from colossus.cosmology import cosmology
 
+import matplotlib.pyplot as plt
+
+import matplotlib as mpl
+from matplotlib import rc
+rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
+rc('text', usetex=True)
+mpl.rcParams['text.latex.preamble'] = [r'\usepackage{amsmath}']
+
+tb_c = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f',
+        '#edc948', '#b07aa1', '#ff9da7', '#9c755f', '#bab0ac']
+
 params = {'flat': True, 'H0': 70, 'Om0': 0.27, 'Ob0': 0.046, 'sigma8': 0.8, 'ns': 1.0}
 cosmo = cosmology.setCosmology('myCosmo', params)
+
+def _Vk_(klist, Pklist, Vsurv):
+    integrand = np.divide(np.square(klist*Pklist), 2.*np.pi**2)
+    Vk = np.trapz(integrand, klist)
+    return np.sqrt(Vsurv*Vk)
 
 def three_fields_corner_plot():
     survey = 'CCAT-p'
@@ -33,6 +49,110 @@ def three_fields_corner_plot():
     fig.tight_layout()
     fig.savefig('CO_tf.pdf')
 
+def plot_all_SN(survey, lines, zbounds=[0, 10], nz=1000):
+
+    freq_range = CO_data.survey_freq_range[survey]
+
+    b = 3
+    bandwidth = 60
+    kmax = 1
+
+    # Vsurv = CO_data.calc_Vsurv(nuobs[0], nuemit[0], bandwidth, CO_data.survey_area[survey], cosmo)
+    
+    # Blist, Nlist = CO_data.gen_Blist_Nlist(3, bandwidth, kmax, zobs, lines, survey, cosmo)
+
+    zextent_list = []
+    for l in lines:
+        nuemit = CO_data.CO_lines[l]
+        zextent = (nuemit - freq_range)/freq_range
+        zextent_list.append(np.flip(zextent))
+    zextent_list = np.array(zextent_list)
+    print(zextent_list)
+
+    zlist = np.linspace(zbounds[0], zbounds[1], nz)
+    lines_obs_list = []
+    tf_bool_list = []
+
+    for z in zlist:
[…]

### 2019-04-26 multifield.py
Allow multifield to take in a user given klist

@@ -16,7 +16,7 @@ tb_c = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f',
 
 class multifield(object):
     def __init__(self, z, Blist, Nlist, kmax, Vsurv, cosmo, kmin=1E-3, nint=1000,
-                 whitenoise=True, Vk=None):
+                 whitenoise=True, Vk=None, klist=None):
         
         if not whitenoise:
             raise NotImplementedError()
@@ -26,9 +26,13 @@ class multifield(object):
         self.z, self.nint, self.Vk = z, nint, Vk
         self.Vsurv, self.cosmo = Vsurv, cosmo
 
+        # ignore nint if a klist is provided
+        if klist is not None:
+            self.nint = len(klist)
+
         # construct linear matter power spectrum
         self.klist, self.Pklist = self._gen_lin_ps_(self.z, self.kmin, self.kmax, 
-                                                    self.nint, self.cosmo)
+                                                    self.nint, self.cosmo, klist)
 
         # check Blist, Nlist, make sure lengths match
         self.Blist, self.Nlist, self.nparam = self._check_BN_param_(Blist, Nlist)
@@ -47,9 +51,11 @@ class multifield(object):
         self.fmat = self._gen_fmat_(self.dPldBi, self.invcov, self.klist,
                                     self.Vsurv, self.npair, self.nparam, self.nint)
 
-    def _gen_lin_ps_(self, z, kmin, kmax, nint, cosmo):
+    def _gen_lin_ps_(self, z, kmin, kmax, nint, cosmo, klist=None):
         # generate linear power spectrum from colossus
-        klist = np.logspace(np.log10(kmin), np.log10(kmax), nint)
+        if klist is None:
+            klist = np.logspace(np.log10(kmin), np.log10(kmax), nint)
+
         Pklist = cosmo.matterPowerSpectrum(klist/cosmo.h, z)
         Pklist /= cosmo.h**3
 

### 2019-04-26 multifield.py
Add klist, Nlist testing to multifield

@@ -373,9 +373,16 @@ if __name__ == '__main__':
     z = 0.88
     kmax = 1
 
+    nint = 100
+    klist = np.logspace(-3, 0, nint)
+
     Blist = [1, 2, 3]
-    Nlist = [1E8, 2E8, 3E8]
     Vsurv = 1E8
 
-    mf = multifield(z, Blist, Nlist, kmax, Vsurv, cosmo)
+    # do tf with constant N
+    Nlist = [1E8, 2E8, 3E8]
     tf = threefield(z, Blist, Nlist, kmax, Vsurv, cosmo)
+
+    # do mf with full N
+    Nlist = np.array([np.full(nint, 1E8), np.full(nint, 2E8), np.full(nint, 3E8)])
+    mf = multifield(z, Blist, Nlist, kmax, Vsurv, cosmo, klist=klist)

### 2019-04-27 paper/ms.tex
Update first fish mat eq

@@
 F_{i,j} = 
-\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
-\sum_{\substack{l,l'\\l > l'}} \sum_{\substack{m,m'\\m > m'}}
-\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
-\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
-\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
+\int \frac{\text{d}^3k}{(2\pi)^3} V_{\text{surv}}
+% \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
+\sum_{l} \sum_{m}
+\frac{\partial \hat{P}_{l}(\bm{k})}{\partial B_i}
+\left(\Cov{\hat{P}_{l}(\bm{k})}{\hat{P}_{m}(\bm{k})}\right)^{-1}
+\frac{\partial \hat{P}_{m}(\bm{k})}{\partial B_j}\text{,}
 \eeq
-where the sum of $l$, $l'$, $m$, and $m'$ is over each of the three lines.
+where the sum over $l$ and $m$ each is over every \emph{pair} of lines.
 Equation~\ref{eq:fisher_tf} can be readily modified to accomodate the case of
 more than three lines (by extending the summations to include these lines) and
-to accomodate the auto-spectra (by allowing $l=l'$ and $m=m'$ in the relevant
-summations). We will consider these cases in Sections~\Gus{x}~and~\Gus{y},
+to accomodate the auto-spectra (by extending the sum over $l$ and $m$ to
+include them). We will consider these cases in Sections~\Gus{x}~and~\Gus{y},
 respectively.

### 2019-04-27 paper/ms.tex
Silence crap about CO line

--- 2019-04-15 paper/ms.tex
@@
 
-\subsection{\CO{} Forecasts for CCAT-p and CONCERTO} \label{ssec:forecasts_tf}
-Armed with some intuition from the simple white noise-dominated case, we now
-turn to forecasting constraints that can be placed on the CO bias factors. Our
-modelling of the \CO{} intensity as a function of redshift follows
-\citet{2016ApJ...825..143L} and is outlined in Appendix~\ref{app:co_int}. We
-assume that $b_i=3$ for each \CO{} line.
+\subsection{Three-field \CO{} Forecasts for CCAT-p} \label{ssec:forecasts_tf}
+% \begin{figure}[h!]
+% \begin{center}
+% \includegraphics{fig/CO_tf.pdf}
+% \end{center}
+% \caption{Constraints that can be placed on the fluctuations of the \CO(6-5),
+% \CO(5-4), and \CO(4-3) lines with CCAT-p at $z_{\text{obs}} = 0.88$. This
+% Figure is purely illustrative, as we do not include noise contributions from
+% residual foreground contamination or interloper/extraloper lines. According to
+% our simple \CO{} model, we have that $B_{\text{6-5}}, B_{\text{5-4}},
+% B_{\text{4-3}} = 151, 183, 232\,\text{Jy}/\text{str}$. Using the instrumental
+% specifications in \citet{2018arXiv181208135C}, we find that $N_{\text{6-5}},
+% N_{\text{5-4}}, N_{\text{4-3}} = 5.1\times10^9, 1.4\times10^9,
+% 5.4\times10^8\,\left(\text{Jy}/\text{str}\right)^2\,\Mpc^3$. We find the same
+% behavior as in Figure~\ref{fig:tf_Nconst}, where the best-measured line is
+% strongly negatively degenerate with the second-best measured line, the
+% best-measured and worst-measured are slightly negatively degenerate, and the
+% second-best measured line and the worst-measured are slightly positively
+% degenerate. }
+% \label{fig:CO_tf}
+% \end{figure}
+
+% Armed with some intuition from the simple white noise-dominated case, we now
+% turn to forecasting constraints that can be placed on the \CO{} bias factors.
+% Our modelling of the \CO{} intensity as a function of redshift follows
+% \citet{2016ApJ...825..143L} and is outlined in Appendix~\ref{app:co_int}. We
+% assume that $b_i=3$ for each \CO{} line.
+
+% At $z=0.88$, the lines \CO(6-5) ($\nu_{\text{obs}} = 367\,\MHz$), \CO(5-4)
+% ($\nu_{\text{obs}} = 306\,\MHz$), and \CO(4-3) ($\nu_{\text{obs}} =
+% 245\,\MHz$) are all in the observing band of CCAT-p. We only include
+% instrumental noise for this Subsection, neglecting foreground and
+% interloper/extraloper contamination. We simply want to place the result of
+% Section~\ref{ssec:tf_noisedom} in the context of an actual experiment.
+
+% Using our \CO{} modelling, we find that $B_{\text{6-5}}, B_{\text{5-4}},
+% B_{\text{4-3}} = 151, 183, 232\,\text{Jy}/\text{str}$ at $z=0.88$. Using the
+% instrumental specifications in \citet{2018arXiv181208135C}, we find that
+% $N_{\text{6-5}}, N_{\text{5-4}}, N_{\text{4-3}} = 5.1\times10^9,
+% 1.4\times10^9, 5.4\times10^8\,\left(\text{Jy}/\text{str}\right)^2\,\Mpc^3$. We
+% assume the instrumental noise is white, but note that in this case the
+% noise-dominated assumption is mildly broken. The worst case is that of the
+% \CO(4-3) line, where on a scale of $k\sim0.01\,\Mpc^{-1}$ we have that
+% $P_{\text{4-3}} \sim 3N_{\text{4-3}}$. Again, this Subsection is purely
+% illustrative, and we will rectify these assumptions in the next Section.
+
+% We assume a bandwidth of $60\,\MHz$ for the line \CO(6-5). This corresponds to
+% a redshift band of width $\Delta z = 0.16$. We resize the \CO(5-4) and
+% \CO(4-3) bands to have the same extent in redshift space, which means slightly
+% scaling the frequency bandwidth --- in this case, the bandwidths are $50$ and
+% $40\,\MHz$, respectively. In Figure~\ref{fig:CO_tf} we show the constraints
+% that can be placed on each of $B_{\text{6-5}}$, $B_{\text{5-4}}$, and
+% $B_{\text{4-3}}$. The line \CO(4-3) is measured to the best intrinsic \SN{},
+% followed by \CO(5-4) and then \CO(6-5). We find the same behavior as in
+% Section~\ref{ssec:tf_noisedom}, where the best-measured line is strongly
+% negatively degenerate with the second-best measured line, the best-measured
+% and worst-measured are slightly negatively degenerate, and the second-best
+% measured line and the worst-measured are slightly positively degenerate.
+% However, we find that CCAT-p should be able to make a measurement of each bias
+% factor using the three-field approach.
 

### 2019-04-27 multifield.py
Add 3d k construction

@@ -51,6 +51,19 @@ class multifield(object):
         self.fmat = self._gen_fmat_(self.dPldBi, self.invcov, self.klist,
                                     self.Vsurv, self.npair, self.nparam, self.nint)
 
+    def _gen_meshgrid_(self, klist):
+
+        kx, ky, kz = np.meshgrid(klist, klist, klist, indexing='ij')
+
+        kx2 = np.square(kx)
+        ky2 = np.square(ky)
+        kz2 = np.square(kz)
+        
+        k = np.sqrt( np.add(np.add(kx2, ky2), kz2) )
+        mu = np.divide(kx, k)
+        
+        return kx, ky, kz, k, mu
+
     def _gen_lin_ps_(self, z, kmin, kmax, nint, cosmo, klist=None):
         # generate linear power spectrum from colossus
         if klist is None:

### 2019-04-27 paper/ms.tex
Add basic stuff about interloping lines

@@
 \newcommand{\Bsum}{\ensuremath{\tilde{B}}}
+
+\newcommand{\kpar}{k_{\parallel}}
+\newcommand{\kperp}{\bm{k}_{\perp}}
+\newcommand{\apar}{\alpha_{\parallel}}
+\newcommand{\aperp}{\alpha_{\perp}}
 
@@
 \eeq
-where $\pstot{i} \equiv \ps{i} + N_i$. Note that $N_i$ contains contributions
+where $\pstot{i} = \ps{i} + N_i$. Note that $N_i$ contains contributions
 from instrument noise, residual foreground contamination, and
@@
 
-\subsection{Three-field \CO{} Forecasts for CCAT-p} \label{ssec:forecasts_tf}
+\subsection{Interloping Lines} \label{ssec:interlopers}
+The multi-field method relies only on the measurements of cross-spectra beween
+various lines. Interloping lines do not contribute to the average
+cross-spectra signal, but does contribute to the noise of the measurement. We
+can account for this by modifying the equation for $N_i$ to be
+\citep{2016ApJ...825..143L, 2016ApJ...832..165C},
+\beq\label{eq:ptot_intlpr}
+N_i = N_{i,\text{instrumental}} + \sum_{j} \frac{1}{\apar(z_j) \aperp(z_j)^2} 
+            P_j\left(\frac{\kpar}{\apar(z_j)}, 
+                     \frac{\kperp}{\aperp(z_j)}\right)\text{,}
+\eeq
+where $N_{i,\text{instrumental}}$ is the instrumental noise of line $i$ at the
+observed frequency, the sum on $j$ is over all interloping lines, $z_j$ is the
+emitted redshift of line $j$, and where,
+\begin{alignat}{2}
+\apar = \frac{H(z_i)}{H(z_j)} \frac{1+z_j}{1+z_i} \quad \quad &&
+\aperp = \frac{D_{A}(z_j)}{D_A(z_i)}\text{,}
+\end{alignat}
+where $z_i$ is the emitted redshift of line $i$ and $D_A(z)$ is the comoving
+angular diameter distance to redshift $z$.
+
+For simplicity, we assume the instrumental noise is white (i.e.
+$N_{i,\text{instrumental}}$ is constant).
+
+% \begin{multicols}{2}
+%   \beq
+%     \apar = \frac{H(z_i)}{H(z_j)} \frac{1+z_j}{1+z_i}
+%   \eeq\break
+%   \beq
+%     \aperp = \frac{D_{A}(z_j)}{D_A(z_i)}
+%   \eeq
+% \end{multicols}
+
 % \begin{figure}[h!]

### 2019-04-27 CO_data.py
Add ability to smooth intensity function

@@ -51,7 +51,14 @@ def epsilon_l(L0, z, smit_table, log=False):
     eps = phi * L0 * SFR * gamma(2.+alpha)
     return eps # Lsolar / Mpc^3
 
-def avg_int(L0, z, smit_table, nurest_l, cosmo, log=False):
+def _smooth_(x, y, x_eval, sigma):
+    delta_x = x_eval[:, None] - x 
+    weights = np.exp(-delta_x*delta_x / (2*sigma*sigma)) / (np.sqrt(2*np.pi) * sigma) 
+    weights /= np.sum(weights, axis=1, keepdims=True) 
+    y_eval = np.dot(weights, y) 
+    return y_eval 
+
+def _avg_int_lookup_(L0, z, smit_table, nurest_l, cosmo, log=False):
     eps = epsilon_l(L0, z, smit_table, log=log)
 
     avg = (eps/(4.*np.pi*nurest_l))
@@ -62,6 +69,22 @@ def avg_int(L0, z, smit_table, nurest_l, cosmo, log=False):
     avg *= r
     
     return avg
+
+def avg_int(L0, z, smit_table, nurest_l, cosmo, smooth=False, sigma=None, log=False):
+    if smooth:
+        assert sigma is not None, "Must specify sigma and zlist to smooth!"
+
+        zsmit_list = smit_table[:,0]
+
+        int_list = np.array([ _avg_int_lookup_(L0, zsmit, smit_table, nurest_l, cosmo, log=log) 
+                                                   for zsmit in zsmit_list ])
+        
+        int_smooth = _smooth_(zsmit_list, int_list, z, sigma)
+
+        return int_smooth
+
+    else:
+        return _avg_int_lookup_(L0, z, smit_table, nurest_l, cosmo)
 
 smit_table = np.array( [[0.0, 0.91, -3.80, -1.51], 
                         [0.2, 0.88, -3.01, -1.45], 

### 2019-04-27 plots/freq_redshift_coverage/plot_freq_redshift_coverage.py
Add intensity vs. z plot

@@ -1,5 +1,5 @@
 import sys
-sys.path.append('../../fisher_plots')
+sys.path.append('../../')
 
 import CO_data
 import numpy as np 

### 2019-04-27 plots/freq_redshift_coverage/plot_intensity_vs_z.py

@@ -1,0 +1,68 @@
+import sys
+sys.path.append('../../')
+
+import CO_data
+import numpy as np 
+import matplotlib.pyplot as plt
+
+from colossus.cosmology import cosmology
+
+from labellines import labelLine, labelLines
+from colour import Color
+
+import matplotlib as mpl
+from matplotlib import rc
+rc('font', **{'family': 'serif', 'serif': [r'\ttdefault']})
+rc('text', usetex=True)
+mpl.rcParams['text.latex.preamble'] = [r'\usepackage{amsmath}']
+
+params = {'flat': True, 'H0': 70, 'Om0': 0.27, 'Ob0': 0.046, 'sigma8': 0.8, 'ns': 1.0}
+cosmo = cosmology.setCosmology('myCosmo', params)
+
+tb_c = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f',
+        '#edc948', '#b07aa1', '#ff9da7', '#9c755f', '#bab0ac']
+
+c1 = Color(tb_c[7])
+c2 = Color(tb_c[0])
+c3 = Color(tb_c[7])
+
+clist1 = list(c3.range_to(c2, 10))
+clist2 = list(c2.range_to(c1, 4))
+clist2 = clist2[1:]
+
+clist = np.append(clist1, clist2)
+clist = [c.get_hex() for c in clist]
+clist.append(tb_c[-1])
+
+lslist = ['dashed', 'dashed', 'dashed', 'dashed', 'dashed', 'dashed', 'dashed', 'dashed', 'dashed',
+          None, None, None, None, None]
+
+xlist = [2.5, 2.5, 2.5, 2.5, 2.5, 2.5, 2.5, 2.5, 2.5, 1.75, 1.25, 1.5, 1.5, 8]
+
+lines = ['13-12', '12-11', '11-10', '10-9', '9-8', '8-7', 
+         '7-6', '6-5', '5-4', '4-3', '3-2', '2-1', '1-0', 'CII']
+
+zlist = np.linspace(0, 10, 100)
+sigma = 1
+stable = CO_data.smit_unlog_table
+
+avg_int_list = {}
+
+for l in lines:
+    nuemit = CO_data.CO_lines[l]
+    L0 = CO_data.CO_L0[l]
+    avg_int_list[l] = CO_data.avg_int(L0, zlist, stable, nuemit, cosmo, smooth=True, sigma=sigma)
+
[…]

### 2019-04-27 multifield.py
Add alpha factors calc to multifield

@@ -377,6 +377,14 @@ def corner_plot(z, Blist, Nlist, cosmo, fac=1, tf=None, kmax=None, Vk=None, norm
 
     return fig, (ax12, ax23, ax31), chisq_12
 
+def alpha_factors(zi, zj, cosmo):
+    alphapar = cosmo.Hz(zi)/cosmo.Hz(zj)
+    alphapar *= (1. + zj)/(1. + zi)
+
+    alphaperp = cosmo.angularDiameterDistance(zj)/cosmo.angularDiameterDistance(zi)
+
+    return alphapar, alphaperp
+
 if __name__ == '__main__':
     from colossus.cosmology import cosmology
 

### 2019-04-27 multifield.py
Move gen_meshgrid to outside multifield

@@ -51,19 +51,6 @@ class multifield(object):
         self.fmat = self._gen_fmat_(self.dPldBi, self.invcov, self.klist,
                                     self.Vsurv, self.npair, self.nparam, self.nint)
 
-    def _gen_meshgrid_(self, klist):
-
-        kx, ky, kz = np.meshgrid(klist, klist, klist, indexing='ij')
-
-        kx2 = np.square(kx)
-        ky2 = np.square(ky)
-        kz2 = np.square(kz)
-        
-        k = np.sqrt( np.add(np.add(kx2, ky2), kz2) )
-        mu = np.divide(kx, k)
-        
-        return kx, ky, kz, k, mu
-
     def _gen_lin_ps_(self, z, kmin, kmax, nint, cosmo, klist=None):
         # generate linear power spectrum from colossus
         if klist is None:
@@ -384,6 +371,24 @@ def alpha_factors(zi, zj, cosmo):
     alphaperp = cosmo.angularDiameterDistance(zj)/cosmo.angularDiameterDistance(zi)
 
     return alphapar, alphaperp
+
+def gen_k_meshgrid(klist, kparkperp=False):
+
+    kx, ky, kz = np.meshgrid(klist, klist, klist, indexing='ij')
+    kx2 = np.square(kx)
+    ky2 = np.square(ky)
+    kz2 = np.square(kz)
+    
+    k = np.sqrt( np.add(np.add(kx2, ky2), kz2) )
+    mu = np.divide(kx, k)
+    
+    if kparkperp:
+        kpar = kx
+        kperp = np.sqrt(np.add(ky2, kz2))
+
+        return kpar, kperp, k, mu
+    else:
+        return kx, ky, kz, k, mu
 
 if __name__ == '__main__':
     from colossus.cosmology import cosmology

### 2019-04-27 multifield.py
Add ability to distort in gen_k_meshgrid

@@ -372,9 +372,17 @@ def alpha_factors(zi, zj, cosmo):
 
     return alphapar, alphaperp
 
-def gen_k_meshgrid(klist, kparkperp=False):
+def gen_k_meshgrid(klist, kparkperp=False, distort=False, apar=None, aperp=None):
 
     kx, ky, kz = np.meshgrid(klist, klist, klist, indexing='ij')
+
+    if distort:
+        assert apar is not None and aperp is not None, "Must specify apar, aperp to distort!"
+        
+        kx = np.divide(kx, apar)
+        ky = np.divide(ky, aperp)
+        kz = np.divide(kz, aperp)
+    
     kx2 = np.square(kx)
     ky2 = np.square(ky)
     kz2 = np.square(kz)

### 2019-04-27 multifield.py
Add fomega function

@@ -382,7 +382,7 @@ def gen_k_meshgrid(klist, kparkperp=False, distort=False, apar=None, aperp=None)
         kx = np.divide(kx, apar)
         ky = np.divide(ky, aperp)
         kz = np.divide(kz, aperp)
-    
+
     kx2 = np.square(kx)
     ky2 = np.square(ky)
     kz2 = np.square(kz)
@@ -397,6 +397,15 @@ def gen_k_meshgrid(klist, kparkperp=False, distort=False, apar=None, aperp=None)
         return kpar, kperp, k, mu
     else:
         return kx, ky, kz, k, mu
+
+def fomega(z, cosmo):
+    D = cosmo.growthFactor(z)
+    dDdz = cosmo.growthFactor(z, derivative=1)
+
+    fomega = np.divide(np.add(1., z), D)
+    fomega = np.multiply(fomega, dDdz)
+
+    return np.negative(fomega)
 
 if __name__ == '__main__':
     from colossus.cosmology import cosmology

### 2019-04-27 multifield.py
Change gen_k_meshgrid to only output k, mu

@@ -372,31 +372,28 @@ def alpha_factors(zi, zj, cosmo):
 
     return alphapar, alphaperp
 
-def gen_k_meshgrid(klist, kparkperp=False, distort=False, apar=None, aperp=None):
+def gen_k_meshgrid(klist, mulist, distort=False, apar=None, aperp=None):
 
-    kx, ky, kz = np.meshgrid(klist, klist, klist, indexing='ij')
+    k, mu = np.meshgrid(klist, mulist, indexing='ij')
 
     if distort:
         assert apar is not None and aperp is not None, "Must specify apar, aperp to distort!"
         
-        kx = np.divide(kx, apar)
-        ky = np.divide(ky, aperp)
-        kz = np.divide(kz, aperp)
+        kpar = np.multiply(k, mu)
+        kpar2 = np.square(kpar)
+        k2 = np.square(k)
+        kperp2 = np.subtract(k2, kpar2)
+        kperp = np.sqrt(kperp2)
 
-    kx2 = np.square(kx)
-    ky2 = np.square(ky)
-    kz2 = np.square(kz)
-    
-    k = np.sqrt( np.add(np.add(kx2, ky2), kz2) )
-    mu = np.divide(kx, k)
-    
-    if kparkperp:
-        kpar = kx
-        kperp = np.sqrt(np.add(ky2, kz2))
+        kpar = np.divide(kpar, apar)
+        kperp = np.divide(kperp, aperp)
 
-        return kpar, kperp, k, mu
-    else:
-        return kx, ky, kz, k, mu
+        k2 = np.add(np.square(kpar), np.square(kperp))
+        k = np.sqrt(k2)
+
+        mu = np.divide(kpar, k)
+    
+    return k, mu
 
 def fomega(z, cosmo):
     D = cosmo.growthFactor(z)

### 2019-04-27 multifield.py
Add intensity power spectrum function

@@ -404,6 +404,46 @@ def fomega(z, cosmo):
 
     return np.negative(fomega)
 
+def intensity_power_spectrum(z, b, I, cosmo, kmin=1E-3, kmax=1, nk=256, nmu=256,
+                             distort=False, ztarget=None, returnk=False):
+    klist = np.logspace(np.log10(kmin), np.log10(kmax), nk)
+    mulist = np.linspace(-1, 1, nmu)
+
+    if distort:
+        assert ztarget is not None, "Must specify ztarget to distort!"
+        apar, aperp = alpha_factors(ztarget, z, cosmo)
+    else:
+        apar, aperp = None, None
+
+    k, mu = gen_k_meshgrid(klist, mulist, distort=distort, apar=apar, aperp=aperp)
+
+    Pden = cosmo.matterPowerSpectrum(np.divide(k, cosmo.h), z)
+    Pden = np.divide(Pden, cosmo.h**3)
+
+    B = b * I
+
+    beta_z = fomega(z, cosmo)/b
+    kaiser = np.add(1., np.multiply(beta_z, np.square(mu)))
+    kaiser = np.square(kaiser)
+
+    fingerofgod = 1 # TODO: implement
+
+    shot = 0 # TODO: implement
+
+    prefactor = np.multiply(B**2, kaiser)
+    prefactor = np.multiply(prefactor, fingerofgod)
+
+    Pintensity = np.multiply(prefactor, Pden)
+    Pintensity = np.add(Pintensity, shot)
+
+    if distort:
+        Pintensity = np.divide(Pintensity, apar * aperp**2)
+
+    if returnk:
+        return k, mu, Pintensity
+    else:
+        return Pintensity
+
 if __name__ == '__main__':
     from colossus.cosmology import cosmology
 

### 2019-04-27 multifield.py
Add ability to angle average intensity_power_spectrum

@@ -405,7 +405,7 @@ def fomega(z, cosmo):
     return np.negative(fomega)
 
 def intensity_power_spectrum(z, b, I, cosmo, kmin=1E-3, kmax=1, nk=256, nmu=256,
-                             distort=False, ztarget=None, returnk=False):
+                             distort=False, ztarget=None, returnk=False, angle_averaged=False):
     klist = np.logspace(np.log10(kmin), np.log10(kmax), nk)
     mulist = np.linspace(-1, 1, nmu)
 
@@ -439,10 +439,25 @@ def intensity_power_spectrum(z, b, I, cosmo, kmin=1E-3, kmax=1, nk=256, nmu=256,
     if distort:
         Pintensity = np.divide(Pintensity, apar * aperp**2)
 
+    if angle_averaged:
+        k, Pintensity = _angle_average_ps_(k, mu, Pintensity)
+
     if returnk:
-        return k, mu, Pintensity
+        if angle_averaged:
+            return k, Pintensity
+        else:
+            return k, mu, Pintensity
     else:
         return Pintensity
+
+def _angle_average_ps_(k, mu, Pkmu):
+    klist = k[:,0]
+
+    Pi = np.trapz(mu, Pkmu, axis=1)
+    Pi = np.divide(Pi, 2.)
+
+    return klist, Pi
+
 
 if __name__ == '__main__':
     from colossus.cosmology import cosmology

### 2019-04-27 plots/freq_redshift_coverage/plot_intensity_vs_z.py
Put intensity_vs_z plot in function

@@ -22,47 +22,55 @@ cosmo = cosmology.setCosmology('myCosmo', params)
 tb_c = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f',
         '#edc948', '#b07aa1', '#ff9da7', '#9c755f', '#bab0ac']
 
-c1 = Color(tb_c[7])
-c2 = Color(tb_c[0])
-c3 = Color(tb_c[7])
 
-clist1 = list(c3.range_to(c2, 10))
-clist2 = list(c2.range_to(c1, 4))
-clist2 = clist2[1:]
+def plot_intensity_vs_z():
 
-clist = np.append(clist1, clist2)
-clist = [c.get_hex() for c in clist]
-clist.append(tb_c[-1])
+    c1 = Color(tb_c[7])
+    c2 = Color(tb_c[0])
+    c3 = Color(tb_c[7])
+    
+    clist1 = list(c3.range_to(c2, 10))
+    clist2 = list(c2.range_to(c1, 4))
+    clist2 = clist2[1:]
+    
+    clist = np.append(clist1, clist2)
+    clist = [c.get_hex() for c in clist]
+    clist.append(tb_c[-1])
+    
+    lslist = ['dashed', 'dashed', 'dashed', 'dashed', 'dashed', 'dashed', 'dashed', 'dashed', 'dashed',
+              None, None, None, None, None]
+    
+    xlist = [2.5, 2.5, 2.5, 2.5, 2.5, 2.5, 2.5, 2.5, 2.5, 1.75, 1.25, 1.5, 1.5, 8]
+    
+    lines = ['13-12', '12-11', '11-10', '10-9', '9-8', '8-7', 
+             '7-6', '6-5', '5-4', '4-3', '3-2', '2-1', '1-0', 'CII']
+    
+    zlist = np.linspace(0, 10, 100)
+    sigma = 1
+    stable = CO_data.smit_unlog_table
+    
+    avg_int_list = {}
+    
+    for l in lines:
+        nuemit = CO_data.CO_lines[l]
+        L0 = CO_data.CO_L0[l]
+        avg_int_list[l] = CO_data.avg_int(L0, zlist, stable, nuemit, cosmo, smooth=True, sigma=sigma)
+    
+    fig, ax = plt.subplots(1, 1, figsize=(7,7))
+    for l,c,ls in zip(lines, clist, lslist):
[…]

### 2019-06-09 plots/reproduce_LT16/plot_CII_ps.py
Fix freq issue, add distorted PS

@@ -31,10 +31,10 @@ def plot_CII_ps(z=7, name='CIIps_z7.pdf'):
     kmax = 10
 
     l = 'CII'
-    # lint = ['3-2', '4-3', '5-4', '6-5']
-    lint = ['2-1', '3-2', '4-3', '5-4', '6-5', '7-6', '8-7', '9-8', '10-9', '11-10', '12-11', '13-12']
+    lint = ['3-2', '4-3', '5-4', '6-5']
+    # lint = ['2-1', '3-2', '4-3', '5-4', '6-5', '7-6', '8-7', '9-8', '10-9', '11-10', '12-11', '13-12']
 
-    nue = CO_data.CO_lines[l]
+    nue = CO_data.CO_lines_LT16[l]
     L0 = CO_data.CO_L0[l]
     Il = CO_data.avg_int(L0, z, CO_data.smit_unlog_table, nue, cosmo, smooth=False)
     bl = 3
@@ -48,9 +48,10 @@ def plot_CII_ps(z=7, name='CIIps_z7.pdf'):
     ax.plot(k, del2, c=tb_c[0], label='CII')
 
     del2int = np.zeros(np.shape(del2))
+    del2int_dist = np.zeros(np.shape(del2))
     ICOtot = 0
     for li in lint:
-        nue_i = CO_data.CO_lines[li]
+        nue_i = CO_data.CO_lines_LT16[li]
         L0 = CO_data.CO_L0[li]
         zint = (nue_i/nue) * (1+z)
         zint -= 1
@@ -64,12 +65,18 @@ def plot_CII_ps(z=7, name='CIIps_z7.pdf'):
             k, Pi = mf.intensity_power_spectrum(zint, bi, Ii, cosmo, kmin=kmin, kmax=kmax, returnk=True, angle_averaged=True,
                                                                      distort=False, ztarget=z)
 
+            k, Pidist = mf.intensity_power_spectrum(zint, bi, Ii, cosmo, kmin=kmin, kmax=kmax, returnk=True, angle_averaged=True,
+                                                                     distort=True, ztarget=z)
+
             del2 = k**3 * Pi / (2.*np.pi**2)
+            del2_dist = k**3 * Pidist / (2.*np.pi**2)
 
             del2int += del2
+            del2int_dist += del2_dist
 
     print('ICO tot:', ICOtot)
     ax.plot(k, del2int, c=tb_c[1], label='CO interlopers')
[…]

### 2019-06-09 paper/ms.tex
Add first draft abstract

@@
 \begin{abstract}
-Abstract.
+% Context
+Intensity mapping of galactic emission lines stands to shed light on both
+galactic astrophysics and cosmology in the coming years. Current efforts span
+a wide range of redshifts, from $z\sim1$ to $z\sim10$, allowing pursuits of
+key science goals out of reach of spectroscopic galaxy surveys and into the
+uncertain astrophysics of the Epoch of Reionization.
+% Aims
+Cross-correlations of two different emission lines can confront many of the
+observational challenges of line intensity mapping, most notably interloper
+contamination. We aim to better our understanding when three or more lines are
+combined through the cross-power spectrum.
+% Methods
+Using the Fisher matrix formalism, we develop a framework for understanding
+the observational constraints possible with intensity mapping of an arbitrary
+number of lines, considering both the cross-spectra alone and the auto- and
+cross-spectra combined.
+% Results
+Results.
+% Conclusions
+We find that multi-line intensity mapping is a promising technique, and future
+intensity mapping efforts should take care to maximize the shared area between
+different surveys.
 \end{abstract}

### 2019-06-11 paper/ms.tex
Update affil

@@
 \newcommand{\penn}{Department of Physics \& Astronomy, University of
-Pennsylvania, 209 South 33rd St., Philadelphia, PA 19104, USA}
+Pennsylvania, 209 South 33rd Street, Philadelphia, PA 19104, USA}
+\newcommand{\harvard}{Center for Astrophysics {\normalfont |} Harvard \& Smithsonian, 60
+Garden Street, Cambridge, MA 02138, USA}
 
@@
 
+\correspondingauthor{Angus Beane}
 \email{abeane@sas.upenn.edu}
@@
 \author{Angus Beane}
+\affil{\harvard}
 \affil{\penn}

### 2019-06-11 CO_data.py
Add smith to CO_data, for hlittle conversions

@@ -106,6 +106,9 @@ def avg_int(L0, z, smit_table, nurest_l, cosmo, smooth=False, sigma=None, log=Fa
     else:
         return _avg_int_lookup_(L0, z, smit_table, nurest_l, cosmo)
 
+smit_h = 0.7
+smit_h3 = smit_h**3
+
 smit_table = np.array( [[0.0, 0.91, -3.80, -1.51], 
                         [0.2, 0.88, -3.01, -1.45], 
                         [0.4, 0.97, -2.97, -1.45], 

### 2019-06-11 multifield.py
Fix hlittle in sigmap2 calc

@@ -415,6 +415,9 @@ def fomega(z, cosmo):
 def sigmap2(z, b, cosmo, kmin=1E-4, kmax=1E4, nk=1000):
     klist = np.logspace(np.log10(kmin), np.log10(kmax), nk)
     Pklist = cosmo.matterPowerSpectrum(klist, z)
+    
+    klist *= cosmo.h
+    Pklist /= cosmo.h**3
     Pint = np.trapz(Pklist, klist)
 
     f = fomega(z, cosmo)

### 2019-06-11 multifield.py
Add back in fingerofgod effect

@@ -453,10 +453,10 @@ def intensity_power_spectrum(z, b, I, cosmo, kmin=1E-3, kmax=1, nk=256, nmu=256,
     # print(kaiser)
 
 
-    # sp2 = sigmap2(z, b, cosmo)
-    # x2 = sp2 * k**2 * mu**2
-    # fingerofgod = 1./(1. + x2)
-    fingerofgod = 1
+    sp2 = sigmap2(z, b, cosmo)
+    x2 = sp2 * (kdist*cosmo.h)**2 * mu**2
+    fingerofgod = 1./(1. + x2)
+    # fingerofgod = 1
 
     # SFR, phi, alpha = CO_data._find_nearest_smit_(z, CO_data.smit_unlog_table)
     # shot = I**2 * (2. + alpha) / (phi * gamma(2.+alpha))

### 2019-06-11 multifield.py
Add back in shot noise, fied hlittle

@@ -458,10 +458,10 @@ def intensity_power_spectrum(z, b, I, cosmo, kmin=1E-3, kmax=1, nk=256, nmu=256,
     fingerofgod = 1./(1. + x2)
     # fingerofgod = 1
 
-    # SFR, phi, alpha = CO_data._find_nearest_smit_(z, CO_data.smit_unlog_table)
-    # shot = I**2 * (2. + alpha) / (phi * gamma(2.+alpha))
-    # print(I, shot)
-    shot = 0
+    SFR, phi, alpha = CO_data._find_nearest_smit_(z, CO_data.smit_unlog_table)
+    shot = I**2 * (2. + alpha) / (phi * gamma(2.+alpha))
+    shot *= CO_data.smit_h3
+    print('shot:', z, I, shot)
 
     prefactor = np.multiply(B**2, kaiser)
     # print(prefactor)

### 2019-06-11 multifield.py
Simplify Pintensity computation

@@ -463,15 +463,8 @@ def intensity_power_spectrum(z, b, I, cosmo, kmin=1E-3, kmax=1, nk=256, nmu=256,
     shot *= CO_data.smit_h3
     print('shot:', z, I, shot)
 
-    prefactor = np.multiply(B**2, kaiser)
-    # print(prefactor)
-    prefactor = np.multiply(prefactor, fingerofgod)
-    # print(prefactor)
-
-    Pintensity = np.multiply(prefactor, Pden)
-    # print(Pintensity[50])
+    Pintensity = np.multiply(np.multiply(np.multiply(B**2, kaiser), fingerofgod), Pden)
     Pintensity = np.add(Pintensity, shot)
-    # print(Pintensity[50])
 
     if distort:
         Pintensity = np.divide(Pintensity, apar * aperp**2)

### 2019-06-11 multifield.py
Clean up comments in IM PS calc

@@ -448,32 +448,23 @@ def intensity_power_spectrum(z, b, I, cosmo, kmin=1E-3, kmax=1, nk=256, nmu=256,
     beta_z = fomega(z, cosmo)/b
     kaiser = np.add(1., np.multiply(beta_z, np.square(mudist)))
     kaiser = np.square(kaiser)
-    # print(np.average(kaiser))
-    # kaiser = 56/45
-    # print(kaiser)
-
 
     sp2 = sigmap2(z, b, cosmo)
     x2 = sp2 * (kdist*cosmo.h)**2 * mu**2
     fingerofgod = 1./(1. + x2)
-    # fingerofgod = 1
 
     SFR, phi, alpha = CO_data._find_nearest_smit_(z, CO_data.smit_unlog_table)
     shot = I**2 * (2. + alpha) / (phi * gamma(2.+alpha))
     shot *= CO_data.smit_h3
-    print('shot:', z, I, shot)
 
     Pintensity = np.multiply(np.multiply(np.multiply(B**2, kaiser), fingerofgod), Pden)
     Pintensity = np.add(Pintensity, shot)
 
     if distort:
         Pintensity = np.divide(Pintensity, apar * aperp**2)
-    # print(Pintensity[50])
 
     if angle_averaged:
         k, Pintensity = _angle_average_ps_(k, mu, Pintensity)
-
-    # print(Pintensity[50])
 
     if returnk:
         if angle_averaged:

### 2019-06-11 multifield.py
Add comments for IM PS calc

@@ -438,6 +438,8 @@ def intensity_power_spectrum(z, b, I, cosmo, kmin=1E-3, kmax=1, nk=256, nmu=256,
     else:
         apar, aperp = None, None
 
+    # generate distorted k, mu - if applicable
+    # otherwise kdist, mudist = k, mu
     k, mu = gen_k_meshgrid(klist, mulist)
     kdist, mudist = gen_k_meshgrid(klist, mulist, distort=distort, apar=apar, aperp=aperp)
 
@@ -445,27 +447,34 @@ def intensity_power_spectrum(z, b, I, cosmo, kmin=1E-3, kmax=1, nk=256, nmu=256,
 
     B = b * I
 
+    # compute prefactor from kaiser effect
     beta_z = fomega(z, cosmo)/b
     kaiser = np.add(1., np.multiply(beta_z, np.square(mudist)))
     kaiser = np.square(kaiser)
 
+    # compute prefactor from fingerofgod effect
     sp2 = sigmap2(z, b, cosmo)
     x2 = sp2 * (kdist*cosmo.h)**2 * mu**2
     fingerofgod = 1./(1. + x2)
 
+    # compute shot noise
     SFR, phi, alpha = CO_data._find_nearest_smit_(z, CO_data.smit_unlog_table)
     shot = I**2 * (2. + alpha) / (phi * gamma(2.+alpha))
     shot *= CO_data.smit_h3
 
+    # put all the pieces together
     Pintensity = np.multiply(np.multiply(np.multiply(B**2, kaiser), fingerofgod), Pden)
     Pintensity = np.add(Pintensity, shot)
 
+    # add in prefactor if distorted
     if distort:
         Pintensity = np.divide(Pintensity, apar * aperp**2)
 
+    # angle average, if necessary
     if angle_averaged:
         k, Pintensity = _angle_average_ps_(k, mu, Pintensity)
 
+    # return
     if returnk:
         if angle_averaged:
             return k, Pintensity

### 2019-06-11 plots/reproduce_LT16/plot_CII_ps.py
Update colors, gen CII ps plot

@@ -45,7 +45,7 @@ def plot_CII_ps(z=7, name='CIIps_z7.pdf'):
 
     fig, ax = plt.subplots(1, 1)
 
-    ax.plot(k, del2, c=tb_c[0], label='CII')
+    ax.plot(k, del2, c=tb_c[-1], label=r'CII')
 
     del2int = np.zeros(np.shape(del2))
     del2int_dist = np.zeros(np.shape(del2))
@@ -75,8 +75,8 @@ def plot_CII_ps(z=7, name='CIIps_z7.pdf'):
             del2int_dist += del2_dist
 
     print('ICO tot:', ICOtot)
-    ax.plot(k, del2int, c=tb_c[1], label='CO interlopers')
-    ax.plot(k, del2int_dist, c=tb_c[2], label='CO interlopers, distorted')
+    ax.plot(k, del2int, c=tb_c[2], label='CO interlopers')
+    ax.plot(k, del2int_dist, c=tb_c[0], label='CO interlopers, distorted')
 
     # now plot values from LT16
     LT16_target = np.genfromtxt('LT16_fig3/delta_mon_quad_target_z7.dat')

### 2019-06-11 multifield.py
Add docstrings for linear matter ps

@@ -54,7 +54,33 @@ class multifield(object):
                                     self.Vsurv, self.npair, self.nparam, self.nint)
 
     def _gen_lin_ps_(self, z, kmin, kmax, nint, cosmo, klist=None):
-        # generate linear power spectrum from colossus
+        """Generates a the linear power spectrum at redshift z.
+
+        Uses the input colossus cosmology to generate the linear matter
+        power spectrum at redshift z. Note that kmin and kmax are ignored if
+        klist is provided, but are still required arguments. If klist is not
+        given, then a klist will be generated with logarithmic spacing from kmin
+        to kmax, with a length of nint.
+    
+        Args:
+            z (float): The redshift at which to compute the power spectrum.
+            kmin (float): The minimum k at which to compute the power spectrum.
+                Ignored if klist is given.
+            kmax (float): The maximum k at which to compute the power spectrum.
+                Ignored if klist is given.
+            nint (int): The number of spacings for the klist. Ignored if klist is
+                given.
+            cosmo: A colossus cosmology object. Used to compute the matter power
+                spectrum.
+            klist (array, optional): A list of k values at which to compute the
+                matter power spectrum. Recommended to be in ascending order. Overrides
+                the kmin, kmax, and nint arguments.
+    
+        Returns:
+            klist (array): The k values [h/Mpc] at which the matter power spectrum is 
+                computed.
+            Pklist (array): The power spectrum values [(Mpc/h)^3].
+        """
         if klist is None:
             klist = np.logspace(np.log10(kmin), np.log10(kmax), nint)
 

### 2019-06-11 CO_data.py
Add cosmology from LT16

@@ -2,6 +2,10 @@ import numpy as np
 import astropy.units as u
 from astropy.constants import c
 from scipy.special import gamma
+from colossus.cosmology import cosmology
+
+LT16_params = {'flat': True, 'H0': 70, 'Om0': 0.27, 'Ob0': 0.046, 'sigma8': 0.8, 'ns': 1.0}
+LT16_cosmo = cosmology.setCosmology('myCosmo', LT16_params)
 
 # basic info about the lines
 

### 2019-06-11 CO_data.py
Add preliminary line class

@@ -260,3 +260,65 @@ def gen_Blist_Nlist(b, bandwidth, kmax, zobs, lines, survey, cosmo):
     Nlist = np.array(Nlist)
 
     return Blist, Nlist
+
+class line(object):
+    def __init__(self, key, cosmo, redshift=None, bias=None):
+        self.key = key
+        self.intensity_assigned = False
+
+        self.freq_emit = CO_lines[key]
+        self.wave_emit = CO_lines_wave[key]
+
+        self.cosmo = cosmo
+
+        if redshift is not None:
+            self.assign_redshift(redshift)
+            self.intensity(redshift, assign=True)
+        else:
+            self.assign_redshift(redshift)
+
+        if bias is not None:
+            self.assign_bias(bias)
+
+    def assign_redshift(self, z):
+        self.redshift = z
+
+    def assign_bias(self, b):
+        self.bias = b
+
+    def freq_obs(self, z):
+        return self.freq_emit / (1. + z)
+
+    def wave_obs(self, z):
+        return self.wave_emit * (1. + z)
+
+    def redshift_emit_interloping(self, ztarget, freq_target):
+        zinterlop = (1.+ztarget)*(self.freq_emit/freq_target) - 1
+        return zinterlop
+
+    def freq_obs_interloping(self, ztarget, freq_target):
+        zinterlop = self.redshift_interloping(ztarget, freq_target)
+        return self.freq_emit / (1. + zinterlop)
+
+    def wave_obs_interloping(self, ztarget, freq_target):
+        zinterlop = self.redshift_interloping(ztarget, freq_target)
+        return self.wave_emit * (1. + zinterlop)
+
+    def calc_intensity(self, z, assign=False):
+        L0 = CO_L0[self.key]
+        intensity = avg_int(L0, z, smit_unlog_table, 
+                            self.freq_emit, self.cosmo, smooth=False)
+
+        if assign:
+            self.intensity = intensity
+            self.intensity_assigned = True
+
+        return intensity
+
+    def B(self, z):
+        assert self.bias is not None, "You must assign the line bias first!"
+        
+        if self.intensity_assigned:
+            return self.intensity * self.bias
+        else:
+            return self.intensity(z)*self.bias

### 2019-06-11 CO_data.py
Add specific instances of line class

@@ -322,3 +322,18 @@ class line(object):
             return self.intensity * self.bias
         else:
             return self.intensity(z)*self.bias
+
+CO1_0 = line('1-0', LT16_cosmo)
+CO2_1 = line('2-1', LT16_cosmo)
+CO3_2 = line('3-2', LT16_cosmo)
+CO4_3 = line('4-3', LT16_cosmo)
+CO5_4 = line('5-4', LT16_cosmo)
+CO6_5 = line('6-5', LT16_cosmo)
+CO7_6 = line('7-6', LT16_cosmo)
+CO8_7 = line('8-7', LT16_cosmo)
+CO9_8 = line('9-8', LT16_cosmo)
+CO10_9 = line('10-9', LT16_cosmo)
+CO11_10 = line('11-10', LT16_cosmo)
+CO12_11 = line('12-11', LT16_cosmo)
+CO13_12 = line('13-12', LT16_cosmo)
+CII = line('CII', LT16_cosmo)

### 2019-06-14 paper/ms.tex
Add k, mu Fisher matrix

@@
 where $z_i$ is the emitted redshift of line $i$ and $D_A(z)$ is the comoving
-angular diameter distance to redshift $z$.
+angular diameter distance to redshift $z$. For simplicity, we assume the
+instrumental noise is white (i.e. $N_{i,\text{instrumental}}$ is constant),
+though it is straightforward in this formalism to incorporate a $k$- or
+$\mu$-dependence in the instrumental noise.
 
-For simplicity, we assume the instrumental noise is white (i.e.
-$N_{i,\text{instrumental}}$ is constant).
+Unlike in the three field case, where the integrand of the Fisher matrix was
+only dependent on $k$, the noise and therefore covariance matrix depends also
+on $\mu$. Galactic foregrounds can imprint an azimuthal dependence as well,
+which we do not consider in this work. Incorporating a polar dependence is straightforward, and we can write the Fisher matrix as:
+\beq\label{eq:fisher_mu}
+F_{i,j} = 
+\int \frac{\text{d}k\,\text{d}\mu}{(2\pi)^2} k^2 V_{\text{surv}}
+% \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
+\sum_{l} \sum_{m}
+\frac{\partial \hat{P}_{l}(k, \mu)}{\partial B_i}
+\left(\Cov{\hat{P}_{l}(k, \mu)}{\hat{P}_{m}(k, \mu)}\right)^{-1}
+\frac{\partial \hat{P}_{m}(k, \mu)}{\partial B_j}\text{,}
+\eeq
 

### 2019-06-14 multifield.py
Fix sigmap2 calc

@@ -442,13 +442,10 @@ def sigmap2(z, b, cosmo, kmin=1E-4, kmax=1E4, nk=1000):
     klist = np.logspace(np.log10(kmin), np.log10(kmax), nk)
     Pklist = cosmo.matterPowerSpectrum(klist, z)
     
-    klist *= cosmo.h
-    Pklist /= cosmo.h**3
     Pint = np.trapz(Pklist, klist)
 
     f = fomega(z, cosmo)
-    beta = f/b
-    sigmav2 = beta**2 * Pint / (3. * 2. * np.pi**2)
+    sigmav2 = f**2 * Pint / (3. * 2. * np.pi**2)
     sigmap2 = sigmav2/2
 
     return sigmap2

### 2019-06-14 multifield.py
Rewriting multifield and CO_data

@@ -1,539 +1,0 @@
-import numpy as np
-import itertools
-
-from scipy.stats import chi2
-import matplotlib.pyplot as plt
-from matplotlib import gridspec
-from scipy.special import gamma
-import CO_data
-
-import matplotlib as mpl
-from matplotlib import rc
-rc('font', **{'serif': ['Computer Modern']})
-rc('text', usetex=True)
-mpl.rcParams['text.latex.preamble'] = [r'\usepackage{amsmath}']
-
-tb_c = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f',
-        '#edc948', '#b07aa1', '#ff9da7', '#9c755f', '#bab0ac']
-
-class multifield(object):
-    def __init__(self, z, Blist, Nlist, kmax, Vsurv, cosmo, kmin=1E-3, nint=1000,
-                 whitenoise=True, Vk=None, klist=None):
-        
-        if not whitenoise:
-            raise NotImplementedError()
-
-        # store some parameters
-        self.kmin, self.kmax = kmin, kmax
-        self.z, self.nint, self.Vk = z, nint, Vk
-        self.Vsurv, self.cosmo = Vsurv, cosmo
-
-        # ignore nint if a klist is provided
-        if klist is not None:
-            self.nint = len(klist)
-
-        # construct linear matter power spectrum
-        self.klist, self.Pklist = self._gen_lin_ps_(self.z, self.kmin, self.kmax, 
-                                                    self.nint, self.cosmo, klist)
-
-        # check Blist, Nlist, make sure lengths match
-        self.Blist, self.Nlist, self.nparam = self._check_BN_param_(Blist, Nlist)
-
-        # generate pairs of indices
-        self.pairlist, self.npair = self._gen_pairlist_(self.nparam)
-
-        # construct derivative vector
-        self.dPldBi = self._gen_dPdB_(self.Blist, self.Pklist, self.pairlist, self.npair, self.nparam, self.nint)
-
-        # construct cov, invcov matrices
-        self.cov, self.invcov = self._gen_cov_(self.Blist, self.Nlist, self.Pklist,
-                                               self.pairlist, self.nparam, self.npair, self.nint)
-
-        # construct fisher matrix
[…]

### 2019-06-14 CO_data.py
Add new lines class

@@ -1,0 +1,43 @@
+import numpy as np
+import warnings
+
+class line(object):
+    def __init__(self, key, freq_emit=None, wave_emit=None):
+        
+        self._speed_of_light_ = 299792.458 # micron * GHz
+        self._assign_freq_and_wave_(freq_emit, wave_emit)
+
+        self.key = key
+
+    def _assign_freq_and_wave_(self, freq_emit, wave_emit):        
+        assert freq_emit is not None or wave_emit is not None, "Must specify emitted frequency\
+                                                                or wavelength"
+        
+        if freq_emit is not None and wave_emit is not None:
+            warnings.warn("Both emitted frequency and wavelength supplied, wavelength is ignored",
+                            RuntimeWarning)
+
+        if freq_emit is not None:
+            self.freq_emit = freq_emit
+            self.wave_emit = self._speed_of_light_/self.freq_emit
+        else:
+            self.wave_emit = wave_emit
+            self.freq_emit = self._speed_of_light_/self.wave_emit
+
+    def freq_obs(self, z):
+        return self.freq_emit / (1. + z)
+
+    def wave_obs(self, z):
+        return self.wave_emit * (1. + z)
+
+    def redshift_emit_interloping(self, ztarget, freq_target):
+        zinterlop = (1. + ztarget) * (self.freq_emit/freq_target) - 1.
+        return zinterlop
+
+    def freq_obs_interloping(self, ztarget, freq_target):
+        zinterlop = self.redshift_emit_interloping(ztarget, freq_target)
+        return self.freq_obs(zinterlop)
+
+    def wave_obs_interloping(self, ztarget, freq_target):
+        zinterlop = self.redshift_emit_interloping(ztarget, freq_target)
+        return self.wave_obs(zinterlop)

### 2019-06-14 CO_data.py
Add start of LT16_COmodel, some testing

@@ -41,3 +41,42 @@ class line(object):
     def wave_obs_interloping(self, ztarget, freq_target):
         zinterlop = self.redshift_emit_interloping(ztarget, freq_target)
         return self.wave_obs(zinterlop)
+    
+class LT16_COmodel(object):
+    def __init__(self):
+        self.CO_L0 = {'1-0': 3.7E3, '2-1': 2.8E4, '3-2': 7E4, '4-3': 9.7E4,
+                      '5-4': 9.6E4, '6-5': 9.5E4, '7-6': 8.9E4, '8-7': 7.7E4,
+                      '9-8': 6.9E4, '10-9': 5.3E4, '11-10': 3.8E4,
+                      '12-11': 2.6E4, '13-12': 1.4E4, 'CII': 6E6}
+        
+        self._assign_smit_table_()
+
+    def _assign_smit_table_(self):
+        smit_h = 0.7
+
+        smit_table = np.array( [[0.0, 0.91, -3.80, -1.51], 
+                                [0.2, 0.88, -3.01, -1.45], 
+                                [0.4, 0.97, -2.97, -1.45], 
+                                [0.6, 1.06, -2.68, -1.45], 
+                                # [0.8, 1.19, -2.77, -1.45], 
+                                [0.8, 1.10, -2.47, -1.56], 
+                                [1.5, 1.41, -2.61, -1.62], 
+                                [2.2, 1.71, -2.73, -1.57], 
+                                [1.5, 2.28, -3.44, -1.60], 
+                                [2.0, 2.27, -3.41, -1.60], 
+                                [2.3, 2.35, -3.49, -1.71], 
+                                [3.8, 1.54, -2.97, -1.60], 
+                                [5.0, 1.36, -3.12, -1.50], 
+                                [5.9, 1.07, -2.97, -1.57], 
+                                [6.8, 1.00, -3.20, -1.96]] )
+        
+        smit_table[:,1] = 10.**smit_table[:,1]
+        smit_table[:,2] = 10.**smit_table[:,2]
+
+        self.smit_table = smit_table
+
+if __name__ == '__main__':
+    l_freq = line('CII', 1901.03)
+    l_wave = line('CII', wave_emit=157.7)
+
+    COmodel = LT16_COmodel()

### 2019-06-14 CO_data.py
Assign CO L0 in separate function

@@ -44,12 +44,13 @@ class line(object):
     
 class LT16_COmodel(object):
     def __init__(self):
+        self._assign_CO_L0_()        
+        self._assign_smit_table_()
+    def _assign_CO_L0_(self):
         self.CO_L0 = {'1-0': 3.7E3, '2-1': 2.8E4, '3-2': 7E4, '4-3': 9.7E4,
                       '5-4': 9.6E4, '6-5': 9.5E4, '7-6': 8.9E4, '8-7': 7.7E4,
                       '9-8': 6.9E4, '10-9': 5.3E4, '11-10': 3.8E4,
                       '12-11': 2.6E4, '13-12': 1.4E4, 'CII': 6E6}
-        
-        self._assign_smit_table_()
 
     def _assign_smit_table_(self):
         smit_h = 0.7

### 2019-06-14 CO_data.py
Add available keys

@@ -44,6 +44,8 @@ class line(object):
     
 class LT16_COmodel(object):
     def __init__(self):
+        self.available_keys = ['1-0', '2-1', '3-2', '4-3', '5-4', '6-5', '7-6', '8-7', '9-8',
+                               '10-9', '11-10', '12-11', '13-12', 'CII']
         self._assign_CO_L0_()        
         self._assign_smit_table_()
     def _assign_CO_L0_(self):

### 2019-06-14 CO_data.py
Assign list of lines in LT16_COmodel

@@ -43,11 +43,16 @@ class line(object):
         return self.wave_obs(zinterlop)
     
 class LT16_COmodel(object):
-    def __init__(self):
+    def __init__(self, use_LT16_freq=False):
         self.available_keys = ['1-0', '2-1', '3-2', '4-3', '5-4', '6-5', '7-6', '8-7', '9-8',
                                '10-9', '11-10', '12-11', '13-12', 'CII']
+        self.use_LT16_freq = use_LT16_freq
+
+        self._assign_lines_()
         self._assign_CO_L0_()        
         self._assign_smit_table_()
+        
+
     def _assign_CO_L0_(self):
         self.CO_L0 = {'1-0': 3.7E3, '2-1': 2.8E4, '3-2': 7E4, '4-3': 9.7E4,
                       '5-4': 9.6E4, '6-5': 9.5E4, '7-6': 8.9E4, '8-7': 7.7E4,
@@ -77,6 +82,24 @@ class LT16_COmodel(object):
         smit_table[:,2] = 10.**smit_table[:,2]
 
         self.smit_table = smit_table
+
+    def _assign_lines_(self):
+        if self.use_LT16_freq:
+            n = 111.52
+            CO_lines_LT16 = {'1-0': n, '2-1': 2*n, '3-2': 3*n, '4-3': 4*n,
+                 '5-4': 5*n, '6-5': 6*n, '7-6': 7*n, '8-7': 8*n,
+                 '9-8': 9*n, '10-9': 10*n, '11-10': 11*n,
+                 '12-11': 12*n, '13-12': 13*n, 'CII': 1901.0}
+
+            self.lines = { key: line(key, freq_emit=f) for key, f in CO_lines_LT16.items() }
+        
+        else:
+            CO_lines_wave = {'1-0': 2610, '2-1': 1300, '3-2': 866, '4-3': 651,
+                             '5-4': 521, '6-5': 434, '7-6': 372, '8-7': 325,
+                             '9-8': 289, '10-9': 260, '11-10': 237,
+                             '12-11': 217, '13-12': 200, 'CII': 157.7}
+            
+            self.lines = { key: line(key, wave_emit=w) for key, w in CO_lines_wave.items() }
 
 if __name__ == '__main__':
     l_freq = line('CII', 1901.03)

### 2019-06-14 CO_data.py
Add cosmology to LT16_COmodel

@@ -1,5 +1,9 @@
 import numpy as np
 import warnings
+from colossus.cosmology import cosmology
+
+LT16_params = {'flat': True, 'H0': 70, 'Om0': 0.27, 'Ob0': 0.046, 'sigma8': 0.8, 'ns': 1.0}
+LT16_cosmo = cosmology.setCosmology('myCosmo', LT16_params)
 
 class line(object):
     def __init__(self, key, freq_emit=None, wave_emit=None):
@@ -43,10 +47,11 @@ class line(object):
         return self.wave_obs(zinterlop)
     
 class LT16_COmodel(object):
-    def __init__(self, use_LT16_freq=False):
+    def __init__(self, use_LT16_freq=False, cosmo=LT16_cosmo):
         self.available_keys = ['1-0', '2-1', '3-2', '4-3', '5-4', '6-5', '7-6', '8-7', '9-8',
                                '10-9', '11-10', '12-11', '13-12', 'CII']
         self.use_LT16_freq = use_LT16_freq
+        self.cosmo = cosmo
 
         self._assign_lines_()
         self._assign_CO_L0_()        

### 2019-06-14 CO_data.py
In LT16_COmodel, compute intensity on redshift grid

@@ -1,5 +1,6 @@
 import numpy as np
 import warnings
+from scipy.special import gamma
 from colossus.cosmology import cosmology
 
 LT16_params = {'flat': True, 'H0': 70, 'Om0': 0.27, 'Ob0': 0.046, 'sigma8': 0.8, 'ns': 1.0}
@@ -48,6 +49,7 @@ class line(object):
     
 class LT16_COmodel(object):
     def __init__(self, use_LT16_freq=False, cosmo=LT16_cosmo):
+        self._speed_of_light_in_kms_ = 299792.458
         self.available_keys = ['1-0', '2-1', '3-2', '4-3', '5-4', '6-5', '7-6', '8-7', '9-8',
                                '10-9', '11-10', '12-11', '13-12', 'CII']
         self.use_LT16_freq = use_LT16_freq
@@ -56,7 +58,8 @@ class LT16_COmodel(object):
         self._assign_lines_()
         self._assign_CO_L0_()        
         self._assign_smit_table_()
-        
+
+        self._compute_intensity_grid_()
 
     def _assign_CO_L0_(self):
         self.CO_L0 = {'1-0': 3.7E3, '2-1': 2.8E4, '3-2': 7E4, '4-3': 9.7E4,
@@ -106,6 +109,24 @@ class LT16_COmodel(object):
             
             self.lines = { key: line(key, wave_emit=w) for key, w in CO_lines_wave.items() }
 
+    def _compute_intensity_grid_(self):
+        print('hi')
+        intensity_grid = {}
+
+        z = self.smit_table[:,0]
+        SFR = self.smit_table[:,1]
+        phi = self.smit_table[:,2]
+        alpha = self.smit_table[:,3]
+
+        for key in self.available_keys:
+            eps = phi * self.CO_L0[key] * SFR * gamma(2.+alpha)
+            avg = (eps/(4.*np.pi*self.lines[key].freq_emit))
+            avg = np.multiply(avg, self._speed_of_light_in_kms_/self.cosmo.Hz(z) )
+            avg *= 0.04020414574289873 # unit handling, will incorporate astropy units later
+            intensity_grid[key] = np.transpose([z, avg])
+        
+        self._intensity_grid_ = intensity_grid
+    
 if __name__ == '__main__':
     l_freq = line('CII', 1901.03)
     l_wave = line('CII', wave_emit=157.7)

### 2019-06-20 multifield.py
Fix FOG effect in distorted case

@@ -477,7 +477,7 @@ def intensity_power_spectrum(z, b, I, cosmo, kmin=1E-3, kmax=1, nk=256, nmu=256,
 
     # compute prefactor from fingerofgod effect
     sp2 = sigmap2(z, b, cosmo)
-    x2 = sp2 * (kdist)**2 * mu**2
+    x2 = sp2 * (kdist)**2 * (mudist)**2
     fingerofgod = 1./(1. + x2)
 
     # compute shot noise

### 2019-06-20 multifield.py
Start multifield.py

@@ -1,0 +1,7 @@
+import numpy as np
+import itertools
+
+from scipy.special import gamma
+import CO_data
+
+

### 2019-06-20 CO_data.py
Add ability to assign a bias to a line

@@ -8,12 +8,18 @@ LT16_params = {'flat': True, 'H0': 70, 'Om0': 0.27, 'Ob0': 0.046, 'sigma8': 0.8,
 LT16_cosmo = cosmology.setCosmology('myCosmo', LT16_params)
 
 class line(object):
-    def __init__(self, key, freq_emit=None, wave_emit=None):
+    def __init__(self, key, freq_emit=None, wave_emit=None, bias=None):
         
         self._speed_of_light_ = 299792.458 # micron * GHz
         self._assign_freq_and_wave_(freq_emit, wave_emit)
 
         self.key = key
+        
+        if bias is not None:
+            self.bias = bias
+            self.bias_assigned = True
+        else:
+            self.bias_assigned = False
 
     def _assign_freq_and_wave_(self, freq_emit, wave_emit):        
         assert freq_emit is not None or wave_emit is not None, "Must specify emitted frequency\

### 2019-06-20 multifield.py
Add multifield, check for assigned bias (for now)

@@ -4,4 +4,11 @@ import itertools
 from scipy.special import gamma
 import CO_data
 
+class multifield(object):
+    def __init__(self, z, line_list):
 
+        self._check_assigned_bias_(line_list)
+    
+    def _check_assigned_bias_(self, line_list):
+        for line in line_list:
+            assert line.bias_assigned, "Bias not assigned for line "+line.key

### 2019-06-20 CO_data.py
Add gaussian smoothing option to LT16_COmodel, and default kind

@@ -53,14 +53,29 @@ class line(object):
     def wave_obs_interloping(self, ztarget, freq_target):
         zinterlop = self.redshift_emit_interloping(ztarget, freq_target)
         return self.wave_obs(zinterlop)
+
+class gaussian_smooth(object):
+    def __init__(self, x, y, sigma):
+        self.x = x
+        self.y = y
+        self.sigma = sigma
     
+    def __call__(self, x_eval):
+        delta_x = x_eval[:, None] - self.x 
+        weights = np.exp(-delta_x*delta_x / (2*self.sigma*self.sigma)) / (np.sqrt(2*np.pi) * self.sigma) 
+        weights /= np.sum(weights, axis=1, keepdims=True) 
+        y_eval = np.dot(weights, self.y) 
+        return y_eval
+
 class LT16_COmodel(object):
-    def __init__(self, use_LT16_freq=False, cosmo=LT16_cosmo):
+    def __init__(self, use_LT16_freq=False, cosmo=LT16_cosmo, kind='smooth', smooth_sigma=1):
         self._speed_of_light_in_kms_ = 299792.458
         self.available_keys = ['1-0', '2-1', '3-2', '4-3', '5-4', '6-5', '7-6', '8-7', '9-8',
                                '10-9', '11-10', '12-11', '13-12', 'CII']
         self.use_LT16_freq = use_LT16_freq
         self.cosmo = cosmo
+        self.kind = kind
+        self.smooth_sigma = smooth_sigma
 
         self._assign_lines_()
         self._assign_CO_L0_()        
@@ -145,6 +160,7 @@ class LT16_COmodel(object):
             for kind in ['linear', 'nearest', 'zero', 'slinear', 'quadratic', 'cubic']:
                 fns[kind] = interp1d(np.array(grid[:,0]), np.array(grid[:,1]), kind=kind, 
                                      bounds_error=False, fill_value="extrapolate")
+            fns['smooth'] = gaussian_smooth(np.array(grid[:,0]), np.array(grid[:,1]), self.smooth_sigma)
             interpolating_fns[key] = fns
 
         self._interpolating_fns_ = interpolating_fns

### 2019-06-20 CO_data.py
Make LT16_COmodel callable

@@ -164,6 +164,12 @@ class LT16_COmodel(object):
             interpolating_fns[key] = fns
 
         self._interpolating_fns_ = interpolating_fns
+    
+    def __call__(self, key, z, kind=None):
+        if kind is None:
+            return self._interpolating_fns_[key][self.kind](z)
+        else:
+            return self._interpolating_fns_[key][kind](z)
 
 if __name__ == '__main__':
     l_freq = line('CII', 1901.03)

### 2019-06-20 multifield.py
Add power spectrum calc from multifield_old

@@ -12,3 +12,130 @@ class multifield(object):
     def _check_assigned_bias_(self, line_list):
         for line in line_list:
             assert line.bias_assigned, "Bias not assigned for line "+line.key
+
+
+def alpha_factors(ztarget, ziloper, cosmo):
+    # if zj >=0 and zi >= 0:
+    if True:
+        alphapar = cosmo.Hz(ztarget)/cosmo.Hz(ziloper)
+        alphapar *= (1. + ziloper)/(1. + ztarget)
+
+        # TODO: check that this is the right conversion in non-flat universes
+        alphaperp = cosmo.angularDiameterDistance(ziloper)/cosmo.angularDiameterDistance(ztarget)
+        alphaperp *= (1. + ziloper)/(1. + ztarget)
+    else:
+        alphaperp, alphapar = np.nan, np.nan
+
+    return alphapar, alphaperp
+
+def gen_k_meshgrid(klist, mulist, distort=False, apar=None, aperp=None):
+
+    k, mu = np.meshgrid(klist, mulist, indexing='ij')
+
+    if distort:
+        assert apar is not None and aperp is not None, "Must specify apar, aperp to distort!"
+
+        # convert from (k, mu) to (kpar, kperp)        
+        kpar = np.multiply(k, mu)
+        kpar2 = np.square(kpar)
+        k2 = np.square(k)
+        kperp2 = np.subtract(k2, kpar2)
+        kperp = np.sqrt(kperp2)
+
+        # distort in (kpar, kperp) space
+        kpar = np.divide(kpar, apar)
+        kperp = np.divide(kperp, aperp)
+
+        # convert back to (k, mu) space
+        k2 = np.add(np.square(kpar), np.square(kperp))
+        k = np.sqrt(k2)
+        mu = np.divide(kpar, k)
+    
+    return k, mu
+
+def fomega(z, cosmo):
+    D = cosmo.growthFactor(z)
+    dDdz = cosmo.growthFactor(z, derivative=1)
+
+    fomega = np.divide(np.add(1., z), D)
+    fomega = np.multiply(fomega, dDdz)
+
+    return np.negative(fomega)
+
+def sigmap2(z, b, cosmo, kmin=1E-4, kmax=1E4, nk=1000):
+    klist = np.logspace(np.log10(kmin), np.log10(kmax), nk)
+    Pklist = cosmo.matterPowerSpectrum(klist, z)
+    
[…]

### 2019-06-20 paper/ms.tex
Add technical background section, average intensity

@@
 \section{Introduction}\label{sec:intro}
+
+\section{Technical Background}\label{sec:tech_back}
+We first lay out the approach to modelling the average intensity of an
+arbitrary emission line, the spatial clustering of that signal, the
+cross-spectrum between two different lines, and the fisher matrix approach for
+estimating the bias factors from an arbitrary number of cross-spectra or
+cross-spectra and auto-spectra.
+
+\subsection{Intrinsic Line Emission}\label{ssec:line_emission}
+The average intensity of an arbitrary line is calculated according
+to the simple model of \citet{2016ApJ...825..143L}, which is based upon
+\citet{2011ApJ...741...70L} and {\bf Pullen 2013}. The details are laid out in
+Appendix~\ref{app:co_int}, but in brief the model assumes a {\bf Schechter
+1976} form for the star formation rate function and a linear relationship
+between a halo's luminosity and its star formation rate with constants of
+proportionality from \citet{2010JCAP...11..016V}.
+
+We note that in this model the redshift evolution of each line is identical up
+to the luminosity-SFR constant of proportionality. In reality, we do not
+expect this to be the case. For example, the different CO lines should have
+varying intrinsic strengths since the typical phase of the ISM in each
+emitting galaxies should change as a function of redshift. This highlights one
+of the limitations of the line intensity model adopted here. Fully
+understanding the underlying galactic population will require more nuanced
+models, though the best path forward is not clear.
 

### 2019-06-20 paper/ms.tex
Add intrinsic spatial fluctuations

@@
 models, though the best path forward is not clear.
+
+To model the intrinsic spatial fluctuations of each line, we follow
+\citet{2016ApJ...825..143L} and \citet{2016ApJ...832..165C}, though we adopt
+the notation of the former. We use the word ``intrinsic'' here not to mean the
+signal in the cosmological rest frame, but rather the observed signal assuming
+the observed coordinates have been transformed to comoving coordinates with
+the correct redshift. This is not the case for interloping lines, for which
+their contribution to the signal is distorted because the assumed redshift and
+the emitted redshift are not the same.
+
+The intrinsic emission from a line $i$ is given by
+\beq\label{eq:int_ps}
+P_{i,i}(k, \mu, z) = \avg{I_i}^2 \avg{b_i}^2 (1 + \beta_i \mu^2)^2 
+              D\left[\mu k \sigma_p(z)\right] P_{\delta, \delta}(k, z)
+              + P_{i, \text{shot}}\text{,}
+\eeq
+where $\mu=k_{\parallel}/k$ is the cosine of the angle between the wavevector
+$\bm{k}$ and the line of sight direction, $\avg{I_i}$ is the average specific
+intensity of line $i$, and $\avg{b_i}$ is the average luminosity-weighted bias
+of the emitting galaxies. The Kaiser effect {\bf Kaiser 1987} is implemented
+through the $(1 + \beta_i \mu^2)^2$ factor, where $\beta_i =
+f_{\Omega}/\avg{b_i}$ with $f_{\Omega} = \text{d}\ln{D}/\text{d}\ln{a}$ is the
+logarithmic derivative of the growth factor, well approximated by $f_{\Omega}
+\approx \Omega^{0.55}$ {\bf Linder 2005}. We assume a Lorentzian form for the
+finger-of-god suppression:
+\beq\label{eq:fog}
+D(x) = \frac{1}{1+x^2}\text{.}
+\eeq
+We approximate the pairwise velocity dispersion by $\sigma_p(z) =
+\sigma_v(z)/\sqrt{2}$ with $\sigma_v^2(z)$ being the variance of the
+line-of-sight component of the velocity field according to linear theory. We
+use the {\bf Eisenstein and Hu 1998} model for the linear theory matter power
+spectrum, $P_{\delta,\delta}(k, z)$. The computation of the shot noise,
+$P_{i,\text{shot}}$ is given in Appendix~\ref{app:co_int}. All basic
+cosmological calculations are performed using the code \texttt{colossus} {\bf
+Diemer 2018}.
 

### 2019-06-24 paper/ms.tex
Add cross-spectrum
Finish of multi-line formalism section

@@
 \newcommand{\SN}{\ensuremath{\text{S}/\text{N}}}
+
+\newcommand{\bi}{\ensuremath{\avg{b_i}}}
+\newcommand{\bj}{\ensuremath{\avg{b_j}}}
+\newcommand{\Ii}{\ensuremath{\avg{I_i}}}
+\newcommand{\Ij}{\ensuremath{\avg{I_j}}}
 
@@
 Diemer 2018}.
+
+For the cross-spectrum between two lines $i$ and $j$, we assume that {\bf need
+to fix this with the shot noise component}
+\beq\label{eq:cross_spec}
+P_{i,j}(k, \mu, z) = r_{i,j}(k, z) \sqrt{P_{i,i}(k, \mu, z) P_{j,j}(k, \mu, z)}
+\eeq
+
+\subsection{Multi-line Formalism}\label{ssec:multi_line}
+Given a set of cross-spectra and their covariance matrix, we can determine the
+optimal constraints that can be placed on both the average bias $\avg{b_i}$
+and average intensity $\avg{I_i}$. For the set of parameters $\theta$
+containing each $\avg{b_i}$ and $\avg{I_i}$, we can write down the Fisher
+matrix as
+\beq\label{eq:fisher}
+F_{i,j} = 
+\int \frac{\text{d}^3k}{(2\pi)^3} V_{\text{surv}}
+% \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
+\sum_{l} \sum_{m}
+\frac{\partial \hat{P}_{l}(\bm{k})}{\partial \theta_i}
+\left(\Cov{\hat{P}_{l}(\bm{k})}{\hat{P}_{m}(\bm{k})}\right)^{-1}
+\frac{\partial \hat{P}_{m}(\bm{k})}{\partial \theta_j}\text{,}
+\eeq
+where the sum over $l$ and $m$ each is over each \emph{pair} of lines.
+
+While in principle one can extract $\bi$ and $\Ii$ independently due to the
+$\mu$-dependence of the Kaiser effect, there are a number of observational
+challenges {\bf Dongwoo 2019}. We will therefore only consider the constraints
+that can be placed on the product of the two, i.e., $B_i \equiv \bi \Ii$. The
+previous Fisher matrix can be converted to the equivalent one for constraints
+on $B_i$, $F'$, by the following relation (e.g. {\bf Coe 2009}):
+\beq\label{eq:fisher_transform}
+F' = M^{\mathsf{T}} F M\text{,}
+\eeq
+where
+\beq\label{eq:trans_matrix}
+M_{ij} = \frac{\partial \theta_i}{\partial B_j}\text{.}
+\eeq
 

### 2019-07-10 paper/ms.tex
Add covariance matrix to multifield section
Remove shot noise

@@
 P_{i,i}(k, \mu, z) = \avg{I_i}^2 \avg{b_i}^2 (1 + \beta_i \mu^2)^2 
-              D\left[\mu k \sigma_p(z)\right] P_{\delta, \delta}(k, z)
-              + P_{i, \text{shot}}\text{,}
+              D\left[\mu k \sigma_p(z)\right] P_{\delta, \delta}(k, z)\text{,}
+              % + P_{i, \text{shot}}\text{,}
 \eeq
@@
 \sigma_v(z)/\sqrt{2}$ with $\sigma_v^2(z)$ being the variance of the
-line-of-sight component of the velocity field according to linear theory. We
-use the {\bf Eisenstein and Hu 1998} model for the linear theory matter power
-spectrum, $P_{\delta,\delta}(k, z)$. The computation of the shot noise,
-$P_{i,\text{shot}}$ is given in Appendix~\ref{app:co_int}. All basic
-cosmological calculations are performed using the code \texttt{colossus} {\bf
-Diemer 2018}.
+line-of-sight component of the velocity field according to linear theory.
+Equation~\eqref{eq:int_ps} neglects the shot noise component of the power
+spectrum, which is an acceptable omission for the large scales considered in
+this work. We use the {\bf Eisenstein and Hu 1998} model for the linear theory
+matter power spectrum, $P_{\delta,\delta}(k, z)$. All basic cosmological
+calculations are performed using the code \texttt{colossus} {\bf Diemer 2018}.
 
-For the cross-spectrum between two lines $i$ and $j$, we assume that {\bf need
-to fix this with the shot noise component}
+For the cross-spectrum between two lines $i$ and $j$, we assume that
 \beq\label{eq:cross_spec}
@@
 \eeq
-where the sum over $l$ and $m$ each is over each \emph{pair} of lines.
+where the sum over $l$ and $m$ each is over each \emph{pair} of lines. In
+order to compute the covariance matrix, we use the result that (cite {\bf
+something? Visbal?})
+\beq\label{eq:var_cov}
+\begin{split}
+\Var{\xps{i}{j}} &= \xps{i}{j}^2 + \pstot{i}\pstot{j} \\
+\Cov{\xps{i}{j}}{\xps{i}{k}} &= \pstot{i}\xps{j}{k} +
+\xps{i}{j}\xps{i}{k}\text{,}
+\end{split}
+\eeq
+where $\pstot{i} = \ps{i} + N_i$. Note that $N_i$ contains contributions from
+instrument noise, residual foreground contamination, and
+interloping/extraloping lines.
 
@@
 \int \frac{\text{d}^3k}{(2\pi)^3} V_{\text{surv}}
-% \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
 \sum_{l} \sum_{m}

### 2019-07-10 paper/ms.tex
Add citations throughout

@@
 intensity of line $i$, and $\avg{b_i}$ is the average luminosity-weighted bias
-of the emitting galaxies. The Kaiser effect {\bf Kaiser 1987} is implemented
+of the emitting galaxies. The Kaiser effect \citep{1987MNRAS.227....1K} is implemented
 through the $(1 + \beta_i \mu^2)^2$ factor, where $\beta_i =
@@
 logarithmic derivative of the growth factor, well approximated by $f_{\Omega}
-\approx \Omega^{0.55}$ {\bf Linder 2005}. We assume a Lorentzian form for the
+\approx \Omega^{0.55}$ \citep{2005PhRvD..72d3529L}. We assume a Lorentzian form for the
 finger-of-god suppression:
@@
 spectrum, which is an acceptable omission for the large scales considered in
-this work. We use the {\bf Eisenstein and Hu 1998} model for the linear theory
+this work. We use the \citet{1998ApJ...496..605E} model for the linear theory
 matter power spectrum, $P_{\delta,\delta}(k, z)$. All basic cosmological
-calculations are performed using the code \texttt{colossus} {\bf Diemer 2018}.
+calculations are performed using the code \texttt{colossus} \citep{2018ApJS..239...35D}.
 
@@
 where the sum over $l$ and $m$ each is over each \emph{pair} of lines. In
-order to compute the covariance matrix, we use the result that (cite {\bf
-something? Visbal?})
+order to compute the covariance matrix, we use the result that \citep[e.g.][]{2010JCAP...11..016V},
 \beq\label{eq:var_cov}
@@
 $\mu$-dependence of the Kaiser effect, there are a number of observational
-challenges {\bf Dongwoo 2019}. We will therefore only consider the constraints
+challenges \citep{2019arXiv190500209C}. We will therefore only consider the constraints
 that can be placed on the product of the two, i.e., $B_i \equiv \bi \Ii$. The
 previous Fisher matrix can be converted to the equivalent one for constraints
-on $B_i$, $F'$, by the following relation (e.g. {\bf Coe 2009}):
+on $B_i$, $F'$, by the following relation \citep[e.g.][]{2009arXiv0906.4123C}:
 \beq\label{eq:fisher_transform}

### 2019-07-15 multifield.py
Put computation of fmat term into a fn

@@ -4,6 +4,49 @@ import itertools
 from scipy.special import gamma
 import CO_data
 
+def fmat_term(z, i, j, ipairs, blist, Ilist, cov, nlines, cosmo):
+    term = 0.0
+    for l, (l1, l2) in enumerate(ipairs):
+        for m, (m1, m2) in enumerate(ipairs):
+            c = cov[l][m]
+            
+            if l1 == i:
+                p1 = intensity_cross_power_spectrum(z, blist[l1], blist[l2], Ilist[l1], Ilist[l2],
+                                                    cosmo, bderivative=True)
+            elif l1 + nlines == i:
+                p1 = intensity_cross_power_spectrum(z, blist[l1], blist[l2], Ilist[l1], Ilist[l2],
+                                                    cosmo, Iderivative=True)
+            elif l2 == i:
+                p1 = intensity_cross_power_spectrum(z, blist[l2], blist[l1], Ilist[l2], Ilist[l1],
+                                                    cosmo, bderivative=True)
+            elif l2 + nlines == i:
+                p1 = intensity_cross_power_spectrum(z, blist[l2], blist[l1], Ilist[l2], Ilist[l1],
+                                                    cosmo, Iderivative=True)
+            else:
+                p1 = 0
+
+            if m1 == j:
+                p2 = intensity_cross_power_spectrum(z, blist[m1], blist[m2], Ilist[m1], Ilist[m2],
+                                                    cosmo, bderivative=True)
+            elif m1 + nlines == j:
+                p2 = intensity_cross_power_spectrum(z, blist[m1], blist[m2], Ilist[m1], Ilist[m2],
+                                                    cosmo, Iderivative=True)
+            elif m2 == j:
+                p2 = intensity_cross_power_spectrum(z, blist[m2], blist[m1], Ilist[m2], Ilist[m1],
+                                                    cosmo, bderivative=True)
+            elif m2 + nlines == j:
+                p2 = intensity_cross_power_spectrum(z, blist[m2], blist[m1], Ilist[m2], Ilist[m1],
+                                                    cosmo, Iderivative=True)
+            else:
+                p2 = 0
+
+            integrand = np.multiply(np.multiply(p1, c), p2)
+            integrand = np.multiply(integrand, np.square(k))
+            print(l, l1, l2, m, m1, m2, integrand[0][0])
+            term = np.add(term, integrand)
+    term = np.trapz(term, mu[0,:], axis=1)
+    term = np.trapz(term, k[:,0], axis=0)
[…]

### 2019-07-15 paper/ms.tex
Small changes to abstract

@@
 Intensity mapping of galactic emission lines stands to shed light on both
-galactic astrophysics and cosmology in the coming years. Current efforts span
-a wide range of redshifts, from $z\sim1$ to $z\sim10$, allowing pursuits of
-key science goals out of reach of spectroscopic galaxy surveys and into the
-uncertain astrophysics of the Epoch of Reionization.
+galactic astrophysics and cosmology from $z\sim1$ to $z\sim10$ in the coming
+years. However, several observational challenges must first be met, including
+the problems of interloper and foreground contamination.
 % Aims
-Cross-correlations of two different emission lines can confront many of the
-observational challenges of line intensity mapping, most notably interloper
-contamination. We aim to better our understanding when three or more lines are
-combined through the cross-power spectrum.
+Cross-correlations of two different emission lines can confront these
+challenges. By combining the cross-correlations between three or more lines,
+one can measure the large-scale bias encoded in the auto-spectrum of each
+line. We aim to understand the general case in more detail.
 % Methods
@@
 the observational constraints possible with intensity mapping of an arbitrary
-number of lines, considering both the cross-spectra alone and the auto- and
-cross-spectra combined.
+number of lines and their associated cross-spectra.
 % Results

### 2019-07-15 paper/ms.tex
Citations, small changes

@@
 to the simple model of \citet{2016ApJ...825..143L}, which is based upon
-\citet{2011ApJ...741...70L} and {\bf Pullen 2013}. The details are laid out in
-Appendix~\ref{app:co_int}, but in brief the model assumes a {\bf Schechter
-1976} form for the star formation rate function and a linear relationship
+\citet{2011ApJ...741...70L} and \citet{2013ApJ...768...15P}. The details are laid out in
+Appendix~\ref{app:co_int}, but in brief the model assumes a \citet{1976ApJ...203..297S} form for the star formation rate function and a linear relationship
 between a halo's luminosity and its star formation rate with constants of
@@
 \beq\label{eq:cross_spec}
-P_{i,j}(k, \mu, z) = r_{i,j}(k, z) \sqrt{P_{i,i}(k, \mu, z) P_{j,j}(k, \mu, z)}
+P_{i,j}(k, \mu, z) = r_{i,j}(k, z) \sqrt{P_{i,i}(k, \mu, z) P_{j,j}(k, \mu, z)}\text{,}
 \eeq
+where $r_{i,j}$ is the cross-correlation coefficient between line $i$ and $j$.
+We will only consider scales where $r_{i,j} = 1$.
 
@@
 \beq\label{eq:fisher_transform}
-F' = M^{\mathsf{T}} F M\text{,}
+F' = M^{\text{T}} F M\text{,}
 \eeq
@@
 \eeq
+
+\subsection{Noise Components}\label{ssec:noise}
+We describe the implementation of each noise component.
+
+\subsubsection{Interloping and Extraloping Lines}\label{sssec:interlopers}
 

### 2019-07-15 multifield.py
Clean up multifield.py

@@ -63,52 +63,6 @@ def fisher_multifield(z, blist, Ilist, Vsurv, cosmo, Nfunclist=None,
         for j in range(nderiv):
             fmat[i][j] = fmat_term(z, i, j, ipairs, blist, Ilist, cov, nlines, cosmo)
 
-    # for i in range(nderiv):
-    #     for j in range(nderiv):
-    #         term = 0.0
-    #         for l, (l1, l2) in enumerate(ipairs):
-    #             for m, (m1, m2) in enumerate(ipairs):
-                    
-    #                 c = cov[l][m]
-
-    #                 if l1 == i:
-    #                     p1 = intensity_cross_power_spectrum(z, blist[l1], blist[l2], Ilist[l1], Ilist[l2],
-    #                                                         cosmo, bderivative=True)
-    #                 elif l1 + nlines == i:
-    #                     p1 = intensity_cross_power_spectrum(z, blist[l1], blist[l2], Ilist[l1], Ilist[l2],
-    #                                                         cosmo, Iderivative=True)
-    #                 elif l2 == i:
-    #                     p1 = intensity_cross_power_spectrum(z, blist[l2], blist[l1], Ilist[l2], Ilist[l1],
-    #                                                         cosmo, bderivative=True)
-    #                 elif l2 + nlines == i:
-    #                     p1 = intensity_cross_power_spectrum(z, blist[l2], blist[l1], Ilist[l2], Ilist[l1],
-    #                                                         cosmo, Iderivative=True)
-    #                 else:
-    #                     p1 = 0.
-                    
-    #                 if m1 == j:
-    #                     p2 = intensity_cross_power_spectrum(z, blist[m1], blist[m2], Ilist[m1], Ilist[m2],
-    #                                                         cosmo, bderivative=True)
-    #                 elif m1 + nlines == j:
-    #                     p2 = intensity_cross_power_spectrum(z, blist[m1], blist[m2], Ilist[m1], Ilist[m2],
-    #                                                         cosmo, Iderivative=True)
-    #                 elif m2 == j:
-    #                     p2 = intensity_cross_power_spectrum(z, blist[m2], blist[m1], Ilist[m2], Ilist[m1],
-    #                                                         cosmo, bderivative=True)
-    #                 elif m2 + nlines == j:
-    #                     p2 = intensity_cross_power_spectrum(z, blist[m2], blist[m1], Ilist[m2], Ilist[m1],
[…]

### 2019-07-15 CO_data_old.py
Add CO_data_old and multifield_old again

@@ -1,0 +1,339 @@
+import numpy as np 
+import astropy.units as u
+from astropy.constants import c
+from scipy.special import gamma
+from colossus.cosmology import cosmology
+
+LT16_params = {'flat': True, 'H0': 70, 'Om0': 0.27, 'Ob0': 0.046, 'sigma8': 0.8, 'ns': 1.0}
+LT16_cosmo = cosmology.setCosmology('myCosmo', LT16_params)
+
+# basic info about the lines
+
+CO_lines_names = ['1-0', '2-1', '3-2', '4-3', '5-4', '6-5', '7-6', '8-7', '9-8',
+                  '10-9', '11-10', '12-11', '13-12', 'CII']
+
+# CO line wavelengths in microns
+CO_lines_wave = {'1-0': 2610, '2-1': 1300, '3-2': 866, '4-3': 651,
+                 '5-4': 521, '6-5': 434, '7-6': 372, '8-7': 325,
+                 '9-8': 289, '10-9': 260, '11-10': 237,
+                 '12-11': 217, '13-12': 200, 'CII': 157.7}
+
+# Convert CO wavelengths to GHz
+speed_of_light = c.to_value(u.micron*u.GHz)
+
+CO_lines = { key: speed_of_light/wave for key, wave in CO_lines_wave.items() }
+
+n = 111.52
+CO_lines_LT16 = {'1-0': n, '2-1': 2*n, '3-2': 3*n, '4-3': 4*n,
+                 '5-4': 5*n, '6-5': 6*n, '7-6': 7*n, '8-7': 8*n,
+                 '9-8': 9*n, '10-9': 10*n, '11-10': 11*n,
+                 '12-11': 12*n, '13-12': 13*n, 'CII': speed_of_light/157.7}
+
+# ---------------------------------------------------------------- #
+#                                                                  #
+#                         line modelling                           #
+#                                                                  #
+# ---------------------------------------------------------------- #
+
+# CO luminosity constant in Lsolar
+CO_L0 = {'1-0': 3.7E3, '2-1': 2.8E4, '3-2': 7E4, '4-3': 9.7E4,
+         '5-4': 9.6E4, '6-5': 9.5E4, '7-6': 8.9E4, '8-7': 7.7E4,
+         '9-8': 6.9E4, '10-9': 5.3E4, '11-10': 3.8E4,
+         '12-11': 2.6E4, '13-12': 1.4E4, 'CII': 6E6}
+
+def _find_nearest_(array, value):
[…]

### 2019-07-15 multifield_old.py

@@ -1,0 +1,539 @@
+import numpy as np
+import itertools
+
+from scipy.stats import chi2
+import matplotlib.pyplot as plt
+from matplotlib import gridspec
+from scipy.special import gamma
+import CO_data
+
+import matplotlib as mpl
+from matplotlib import rc
+rc('font', **{'serif': ['Computer Modern']})
+rc('text', usetex=True)
+mpl.rcParams['text.latex.preamble'] = [r'\usepackage{amsmath}']
+
+tb_c = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f',
+        '#edc948', '#b07aa1', '#ff9da7', '#9c755f', '#bab0ac']
+
+class multifield(object):
+    def __init__(self, z, Blist, Nlist, kmax, Vsurv, cosmo, kmin=1E-3, nint=1000,
+                 whitenoise=True, Vk=None, klist=None):
+        
+        if not whitenoise:
+            raise NotImplementedError()
+
+        # store some parameters
+        self.kmin, self.kmax = kmin, kmax
+        self.z, self.nint, self.Vk = z, nint, Vk
+        self.Vsurv, self.cosmo = Vsurv, cosmo
+
+        # ignore nint if a klist is provided
+        if klist is not None:
+            self.nint = len(klist)
+
+        # construct linear matter power spectrum
+        self.klist, self.Pklist = self._gen_lin_ps_(self.z, self.kmin, self.kmax, 
+                                                    self.nint, self.cosmo, klist)
+
+        # check Blist, Nlist, make sure lengths match
+        self.Blist, self.Nlist, self.nparam = self._check_BN_param_(Blist, Nlist)
+
+        # generate pairs of indices
+        self.pairlist, self.npair = self._gen_pairlist_(self.nparam)
+
+        # construct derivative vector
+        self.dPldBi = self._gen_dPdB_(self.Blist, self.Pklist, self.pairlist, self.npair, self.nparam, self.nint)
+
+        # construct cov, invcov matrices
+        self.cov, self.invcov = self._gen_cov_(self.Blist, self.Nlist, self.Pklist,
+                                               self.pairlist, self.nparam, self.npair, self.nint)
+
+        # construct fisher matrix
[…]

### 2019-07-15 multifield.py
Add back old multifield class

@@ -4,6 +4,155 @@ import itertools
 from scipy.special import gamma
 import CO_data
 
+class multifield(object):
+    def __init__(self, z, Blist, Nlist, kmax, Vsurv, cosmo, kmin=1E-3, nint=1000,
+                 whitenoise=True, Vk=None, klist=None):
+        
+        if not whitenoise:
+            raise NotImplementedError()
+
+        # store some parameters
+        self.kmin, self.kmax = kmin, kmax
+        self.z, self.nint, self.Vk = z, nint, Vk
+        self.Vsurv, self.cosmo = Vsurv, cosmo
+
+        # ignore nint if a klist is provided
+        if klist is not None:
+            self.nint = len(klist)
+
+        # construct linear matter power spectrum
+        self.klist, self.Pklist = self._gen_lin_ps_(self.z, self.kmin, self.kmax, 
+                                                    self.nint, self.cosmo, klist)
+
+        # check Blist, Nlist, make sure lengths match
+        self.Blist, self.Nlist, self.nparam = self._check_BN_param_(Blist, Nlist)
+
+        # generate pairs of indices
+        self.pairlist, self.npair = self._gen_pairlist_(self.nparam)
+
+        # construct derivative vector
+        self.dPldBi = self._gen_dPdB_(self.Blist, self.Pklist, self.pairlist, self.npair, self.nparam, self.nint)
+
+        # construct cov, invcov matrices
+        self.cov, self.invcov = self._gen_cov_(self.Blist, self.Nlist, self.Pklist,
+                                               self.pairlist, self.nparam, self.npair, self.nint)
+
+        # construct fisher matrix
+        self.fmat = self._gen_fmat_(self.dPldBi, self.invcov, self.klist,
+                                    self.Vsurv, self.npair, self.nparam, self.nint)
+
+    def _gen_lin_ps_(self, z, kmin, kmax, nint, cosmo, klist=None):
+        """Generates a the linear power spectrum at redshift z.
+
+        Uses the input colossus cosmology to generate the linear matter
+        power spectrum at redshift z. Note that kmin and kmax are ignored if
+        klist is provided, but are still required arguments. If klist is not
+        given, then a klist will be generated with logarithmic spacing from kmin
+        to kmax, with a length of nint.
+    
[…]

### 2019-07-15 multifield.py
Add ability to get covariance of angle-averaged PS

@@ -443,7 +443,7 @@ def intensity_power_spectrum(z, b, I, cosmo, kmin=1E-3, kmax=1, nk=256, nmu=256,
         return Pintensity
 
 def covariance(z, blist, Ilist, cosmo, Nfunclist=None, kmin=1E-3, kmax=1, nk=256, nmu=256,
-                returnk_and_pairs=False):
+                returnk_and_pairs=False, angle_averaged=False):
 
     assert len(blist) == len(Ilist), "blist, and Ilist must be the same length"
     
@@ -454,28 +454,41 @@ def covariance(z, blist, Ilist, cosmo, Nfunclist=None, kmin=1E-3, kmax=1, nk=256
     npairs = len(ipairs)
 
     # just to get k, mu... TODO: pull this out of PS func later
-    k, mu, _ = intensity_power_spectrum(z, blist[0], Ilist[0], cosmo, kmin=kmin, kmax=kmax,
-                                        nk=nk, nmu=nmu, returnk=True)
+    if angle_averaged:
+        k, _ = intensity_power_spectrum(z, blist[0], Ilist[0], cosmo, kmin=kmin, kmax=kmax,
+                                        nk=nk, nmu=nmu, returnk=True, angle_averaged=True)
+        xPSlist = np.zeros((nparam, nparam, nk))
+        cov = np.zeros((npairs, npairs, nk))
+
+
+    else:   
+        k, mu, _ = intensity_power_spectrum(z, blist[0], Ilist[0], cosmo, kmin=kmin, kmax=kmax,
+                                            nk=nk, nmu=nmu, returnk=True)
+        xPSlist = np.zeros((nparam, nparam, nk, nmu))
+        cov = np.zeros((npairs, npairs, nk, nmu))
+
 
     PSlist = np.array([intensity_power_spectrum(z, b, I, cosmo, kmin=kmin, kmax=kmax, 
-                                             nk=nk, nmu=nmu, returnk=False) for b,I in zip(blist, Ilist)])
+                                             nk=nk, nmu=nmu, returnk=False, angle_averaged=angle_averaged) 
+                                                for b,I in zip(blist, Ilist)])
 
-    xPSlist = np.zeros((nparam, nparam, nk, nmu))
     for i in range(nparam):
         for j in range(nparam):
             xPSlist[i][j] = intensity_cross_power_spectrum(z, blist[i], blist[j], Ilist[i], Ilist[j], 
[…]

### 2019-07-15 multifield.py
Introduce constant N and constant N w/ mu dependence

@@ -518,17 +518,23 @@ def covariance(z, blist, Ilist, cosmo, Nfunclist=None, kmin=1E-3, kmax=1, nk=256
     else:
         return cov
 
-class constant_N(object):
+class constant_N_mu(object):
     def __init__(self, N):
         self.N = N
     def __call__(self, k, mu):
         return np.full(np.shape(k), self.N)
 
+class constant_N(object):
+    def __init__(self, N):
+        self.N = N
+    def __call__(self, k):
+        return np.full(np.shape(k), self.N)
+
 if __name__ == '__main__':
     cosmo = CO_data.LT16_cosmo
 
-    N_const1 = constant_N(10)
-    N_const2 = constant_N(20)
+    N_const1 = constant_N_mu(10)
+    N_const2 = constant_N_mu(20)
     Nlist = [N_const1]
 
     k, mu, ipairs, cov = covariance(2, np.array([1, 2, 3, 4]), np.array([100, 100, 100, 100]), cosmo, 
@@ -538,7 +544,7 @@ if __name__ == '__main__':
     Vsurv = 508
     blist = 100*np.array([1, np.sqrt(2), np.sqrt(3)])
     Ilist = np.array([1, 1, 1])/100
-    Nlist = [constant_N(2E5)]
+    Nlist = [constant_N_mu(2E5)]
     k, mu, ipairs, cov = covariance(0.88, blist, Ilist, cosmo, Nfunclist=Nlist, returnk_and_pairs=True)
     fmat = fisher_multifield(0.88, blist, Ilist, Vsurv, cosmo, Nfunclist=Nlist)
     fmatp = convert_fisher(fmat, blist, Ilist)

### 2019-07-15 paper/ms.tex
Add disclaimer about shot noise
Update to reflect angle-averaged case

@@
 spectrum, which is an acceptable omission for the large scales considered in
-this work. We use the \citet{1998ApJ...496..605E} model for the linear theory
+this work.
+Our neglect to add the shot noise component is out of convenience considering the scales we will encounter, but this is not to imply that the shot noise component is uninteresting in its own right ({\bf cite some?}) even in the cross-spectra ({\bf cite Breysse 2019}).
+We use the \citet{1998ApJ...496..605E} model for the linear theory
 matter power spectrum, $P_{\delta,\delta}(k, z)$. All basic cosmological
@@
 
+Throughout this work we will only consider the angle-averaged power spectrum, that is:
+\beq\label{eq:int_ps}
+\begin{split}
+P_{i,i}(k, z) &= \avg{I_i}^2 \avg{b_i}^2 C_i(k) P_{\delta, \delta}(k, z)\\
+                   &\equiv B_i^2 C_i(k) P_{\delta, \delta}(k, z)\text{,}
+              % + P_{i, \text{shot}}\text{,}
+\end{split}
+\eeq
+where we have defined $C_i(k)$ to be the amplification of the power spectrum
+coming from the average over the angle-dependent terms in
+Equation~\eqref{eq:int_ps}, and $B_i$ to be the product of $\avg{b_i}$ and
+$\avg{I_i}$. Henceforth all power spectra will be assumed to be angle
+averaged.
+
 For the cross-spectrum between two lines $i$ and $j$, we assume that
 \beq\label{eq:cross_spec}
-P_{i,j}(k, \mu, z) = r_{i,j}(k, z) \sqrt{P_{i,i}(k, \mu, z) P_{j,j}(k, \mu, z)}\text{,}
+P_{i,j}(k, z) = r_{i,j}(k, z) \sqrt{P_{i,i}(k, z) P_{j,j}(k, z)}\text{,}
 \eeq
@@
 \subsection{Multi-line Formalism}\label{ssec:multi_line}
-Given a set of cross-spectra and their covariance matrix, we can determine the
-optimal constraints that can be placed on both the average bias $\avg{b_i}$
-and average intensity $\avg{I_i}$. For the set of parameters $\theta$
-containing each $\avg{b_i}$ and $\avg{I_i}$, we can write down the Fisher
-matrix as
+Given a set of cross-spectra and their covariance matrix, we can, in
+principle, determine the optimal constraints that can be placed on both the
+average bias $\avg{b_i}$ and average intensity $\avg{I_i}$. However, such a
+procedure requires measuring the angular dependence of the power spectrum
+({\bf cite}), which may be fairly challenging \citep{2019arXiv190500209C}.
+Therefore, after fixing the value of $b_i$ for each line $i$, we only consider
+the constraint that can be placed on each $B_i$. This is slightly
+inconsistent, since in principle we should first determine the constraint on
+$\bi$ and $\Ii$ and then convert this into a constraint on $B_i$. But our
+approximation is reasonable because {\bf of some reason}.
+
+We can write down the Fisher matrix as
 \beq\label{eq:fisher}
@@
 \sum_{l} \sum_{m}
-\frac{\partial \hat{P}_{l}(\bm{k})}{\partial \theta_i}
+\frac{\partial \hat{P}_{l}(\bm{k})}{\partial B_i}
 \left(\Cov{\hat{P}_{l}(\bm{k})}{\hat{P}_{m}(\bm{k})}\right)^{-1}
-\frac{\partial \hat{P}_{m}(\bm{k})}{\partial \theta_j}\text{,}
+\frac{\partial \hat{P}_{m}(\bm{k})}{\partial B_j}\text{,}
 \eeq
-where the sum over $l$ and $m$ each is over each \emph{pair} of lines. In
+where the sum over $l$ and $m$ each is over each \emph{pair} of lines. Since
+we will be considering only angle-averaged power spectra, we can use the
+angle-averaged form of the Fisher matrix:
+\beq\label{eq:fisher}
+F_{i,j} = 
+\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}}
+% \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
+\sum_{l} \sum_{m}
+\frac{\partial \hat{P}_{l}(k)}{\partial B_i}
+\left(\Cov{\hat{P}_{l}(k)}{\hat{P}_{m}(k)}\right)^{-1}
+\frac{\partial \hat{P}_{m}(k)}{\partial B_j}\text{.}
+\eeq
+
+In
 order to compute the covariance matrix, we use the result that \citep[e.g.][]{2010JCAP...11..016V},
@@
 interloping/extraloping lines.
-
-While in principle one can extract $\bi$ and $\Ii$ independently due to the
-$\mu$-dependence of the Kaiser effect, there are a number of observational
-challenges \citep{2019arXiv190500209C}. We will therefore only consider the constraints
-that can be placed on the product of the two, i.e., $B_i \equiv \bi \Ii$. The
-previous Fisher matrix can be converted to the equivalent one for constraints
-on $B_i$, $F'$, by the following relation \citep[e.g.][]{2009arXiv0906.4123C}:
-\beq\label{eq:fisher_transform}
-F' = M^{\text{T}} F M\text{,}
-\eeq
-where
-\beq\label{eq:trans_matrix}
-M_{ij} = \frac{\partial \theta_i}{\partial B_j}\text{.}
-\eeq
 

### 2019-07-15 paper/ms.tex
Small update
Expand on noise section

@@
 \eeq
-where $\pstot{i} = \ps{i} + N_i$. Note that $N_i$ contains contributions from
-instrument noise, residual foreground contamination, and
-interloping/extraloping lines.
+where $\pstot{i} = \ps{i} + N_i$. The computation of the noise $N_i$ is given in the next subsection.
 
 \subsection{Noise Components}\label{ssec:noise}
-We describe the implementation of each noise component.
+We describe the computation of each noise component. In principle the noise
+should consist of three components:
+\beq\label{eq:noise_comp}
+N_i = N_{i,\text{instrumental}} + N_{i,\text{interlopers}} + N_{i,\text{foreground}}\text{.}
+\eeq
+However, in this work we will ignore the foreground contribution. Our work
+should then be seen as a best-case scenario. {\bf add more words}
+
+\subsubsection{Instrumental Noise}\label{sssec:instrumental}
+{\bf Add.}
 
 \subsubsection{Interloping and Extraloping Lines}\label{sssec:interlopers}
+The noise for interloping and extraloping lines can be written as
+\citep{2016ApJ...825..143L, 2016ApJ...832..165C},
+\beq\label{eq:ptot_intlpr}
+N_{i,\text{interlopers}} = \sum_{j} \frac{1}{\apar(z_j) \aperp(z_j)^2} 
+            P_j\left(\frac{\kpar}{\apar(z_j)}, 
+                     \frac{\kperp}{\aperp(z_j)}\right)\text{,}
+\eeq
+where the sum on $j$ is over all interloping lines, $z_j$ is the
+emitted redshift of line $j$, and where,
+\begin{alignat}{2}
+\apar = \frac{H(z_i)}{H(z_j)} \frac{1+z_j}{1+z_i} \quad \quad &&
+\aperp = \frac{D_{A}(z_j)}{D_A(z_i)}\text{,}
+\end{alignat}
+where $z_i$ is the emitted redshift of line $i$ and $D_A(z)$ is the comoving
+angular diameter distance to redshift $z$.
 
@@
 \beq \label{eq:frac_error_same}
-\frac{\sigma_{B_1}}{B_1} = \frac{\sigma_{B_2}}{B_2} = 
-\frac{\sigma_{B_3}}{B_3}\text{.}
+\frac{B_1}{\sigma_{B_1}} = \frac{B_2}{\sigma_{B_2}} = 
+\frac{B_3}{\sigma_{B_3}} \text{.}
 \eeq

### 2019-07-15 paper/ms.tex
Remove unecessary section

@@
 
-\subsection{Interloping Lines} \label{ssec:interlopers}
-The multi-field method relies only on the measurements of cross-spectra beween
-various lines. Interloping lines do not contribute to the average
-cross-spectra signal, but does contribute to the noise of the measurement. We
-can account for this by modifying the equation for $N_i$ to be
-\citep{2016ApJ...825..143L, 2016ApJ...832..165C},
-\beq\label{eq:ptot_intlpr}
-N_i = N_{i,\text{instrumental}} + \sum_{j} \frac{1}{\apar(z_j) \aperp(z_j)^2} 
-            P_j\left(\frac{\kpar}{\apar(z_j)}, 
-                     \frac{\kperp}{\aperp(z_j)}\right)\text{,}
-\eeq
-where $N_{i,\text{instrumental}}$ is the instrumental noise of line $i$ at the
-observed frequency, the sum on $j$ is over all interloping lines, $z_j$ is the
-emitted redshift of line $j$, and where,
-\begin{alignat}{2}
-\apar = \frac{H(z_i)}{H(z_j)} \frac{1+z_j}{1+z_i} \quad \quad &&
-\aperp = \frac{D_{A}(z_j)}{D_A(z_i)}\text{,}
-\end{alignat}
-where $z_i$ is the emitted redshift of line $i$ and $D_A(z)$ is the comoving
-angular diameter distance to redshift $z$. For simplicity, we assume the
-instrumental noise is white (i.e. $N_{i,\text{instrumental}}$ is constant),
-though it is straightforward in this formalism to incorporate a $k$- or
-$\mu$-dependence in the instrumental noise.
-
-Unlike in the three field case, where the integrand of the Fisher matrix was
-only dependent on $k$, the noise and therefore covariance matrix depends also
-on $\mu$. Galactic foregrounds can imprint an azimuthal dependence as well,
-which we do not consider in this work. Incorporating a polar dependence is straightforward, and we can write the Fisher matrix as:
-\beq\label{eq:fisher_mu}
-F_{i,j} = 
-\int \frac{\text{d}k\,\text{d}\mu}{(2\pi)^2} k^2 V_{\text{surv}}
-% \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
-\sum_{l} \sum_{m}
-\frac{\partial \hat{P}_{l}(k, \mu)}{\partial B_i}
-\left(\Cov{\hat{P}_{l}(k, \mu)}{\hat{P}_{m}(k, \mu)}\right)^{-1}
-\frac{\partial \hat{P}_{m}(k, \mu)}{\partial B_j}\text{,}
-\eeq
-
-% \begin{multicols}{2}
-%   \beq
-%     \apar = \frac{H(z_i)}{H(z_j)} \frac{1+z_j}{1+z_i}
-%   \eeq\break
-%   \beq
-%     \aperp = \frac{D_{A}(z_j)}{D_A(z_i)}
-%   \eeq
-% \end{multicols}
-
-% \begin{figure}[h!]
-% \begin{center}
-% \includegraphics{fig/CO_tf.pdf}
-% \end{center}
-% \caption{Constraints that can be placed on the fluctuations of the \CO(6-5),
-% \CO(5-4), and \CO(4-3) lines with CCAT-p at $z_{\text{obs}} = 0.88$. This
-% Figure is purely illustrative, as we do not include noise contributions from
-% residual foreground contamination or interloper/extraloper lines. According to
-% our simple \CO{} model, we have that $B_{\text{6-5}}, B_{\text{5-4}},
-% B_{\text{4-3}} = 151, 183, 232\,\text{Jy}/\text{str}$. Using the instrumental
-% specifications in \citet{2018arXiv181208135C}, we find that $N_{\text{6-5}},
-% N_{\text{5-4}}, N_{\text{4-3}} = 5.1\times10^9, 1.4\times10^9,
-% 5.4\times10^8\,\left(\text{Jy}/\text{str}\right)^2\,\Mpc^3$. We find the same
-% behavior as in Figure~\ref{fig:tf_Nconst}, where the best-measured line is
-% strongly negatively degenerate with the second-best measured line, the
-% best-measured and worst-measured are slightly negatively degenerate, and the
-% second-best measured line and the worst-measured are slightly positively
-% degenerate. }
-% \label{fig:CO_tf}
-% \end{figure}
-
-% Armed with some intuition from the simple white noise-dominated case, we now
-% turn to forecasting constraints that can be placed on the \CO{} bias factors.
-% Our modelling of the \CO{} intensity as a function of redshift follows
-% \citet{2016ApJ...825..143L} and is outlined in Appendix~\ref{app:co_int}. We
-% assume that $b_i=3$ for each \CO{} line.
-
-% At $z=0.88$, the lines \CO(6-5) ($\nu_{\text{obs}} = 367\,\MHz$), \CO(5-4)
-% ($\nu_{\text{obs}} = 306\,\MHz$), and \CO(4-3) ($\nu_{\text{obs}} =
-% 245\,\MHz$) are all in the observing band of CCAT-p. We only include
-% instrumental noise for this Subsection, neglecting foreground and
-% interloper/extraloper contamination. We simply want to place the result of
-% Section~\ref{ssec:tf_noisedom} in the context of an actual experiment.
-
-% Using our \CO{} modelling, we find that $B_{\text{6-5}}, B_{\text{5-4}},
-% B_{\text{4-3}} = 151, 183, 232\,\text{Jy}/\text{str}$ at $z=0.88$. Using the
-% instrumental specifications in \citet{2018arXiv181208135C}, we find that
-% $N_{\text{6-5}}, N_{\text{5-4}}, N_{\text{4-3}} = 5.1\times10^9,
-% 1.4\times10^9, 5.4\times10^8\,\left(\text{Jy}/\text{str}\right)^2\,\Mpc^3$. We
-% assume the instrumental noise is white, but note that in this case the
-% noise-dominated assumption is mildly broken. The worst case is that of the
-% \CO(4-3) line, where on a scale of $k\sim0.01\,\Mpc^{-1}$ we have that
-% $P_{\text{4-3}} \sim 3N_{\text{4-3}}$. Again, this Subsection is purely
-% illustrative, and we will rectify these assumptions in the next Section.
-
-% We assume a bandwidth of $60\,\MHz$ for the line \CO(6-5). This corresponds to
-% a redshift band of width $\Delta z = 0.16$. We resize the \CO(5-4) and
-% \CO(4-3) bands to have the same extent in redshift space, which means slightly
-% scaling the frequency bandwidth --- in this case, the bandwidths are $50$ and
-% $40\,\MHz$, respectively. In Figure~\ref{fig:CO_tf} we show the constraints
-% that can be placed on each of $B_{\text{6-5}}$, $B_{\text{5-4}}$, and
-% $B_{\text{4-3}}$. The line \CO(4-3) is measured to the best intrinsic \SN{},
-% followed by \CO(5-4) and then \CO(6-5). We find the same behavior as in
-% Section~\ref{ssec:tf_noisedom}, where the best-measured line is strongly
-% negatively degenerate with the second-best measured line, the best-measured
-% and worst-measured are slightly negatively degenerate, and the second-best
-% measured line and the worst-measured are slightly positively degenerate.
-% However, we find that CCAT-p should be able to make a measurement of each bias
-% factor using the three-field approach.
-
 \section{Random Thoughts}

### 2019-07-16 paper/ms.tex
Update title
Add start of intro

@@
 \newcommand{\CO}{\ensuremath{\text{CO}}}
+\newcommand{\HI}{\ensuremath{\text{H~\textsc{i}}}}
 
@@
 
-\title{Multi-line Intensity Mapping}
+\title{Cleaning Foregrounds and Boosting Signals with Multi-line Intensity Mapping}
 
@@
 \section{Introduction}\label{sec:intro}
+Precision studies of the large-scale structure (LSS) of the universe provide
+important cosmological constraints. Traditional galaxy surveys are limited in
+their possible redshift extent to currently $z\lesssim1$ due to the expense
+required in taking spectra of large numbers of high-redshift galaxies.
+Line-intensity mapping has emerged as a promising alternative, instead
+measuring the collective emission in a convenient line in fairly coarse
+pixels. By sacrificing resolution, intensity mapping allows one to measure
+large scales at high redshift.
+
+Intensity mapping of the $\HI$~21~cm line is the most well studied. During
+reionization, it is sourced by the intergalactic medium . Post-reionization,
+it is sourced by neutral hydrogen primarily in the interstellar medium . A
+detection of the 21~cm power spectrum and the baryon acoustic oscillation
+feature have been made at $z\sim0.8$ \citep{2010Natur.466..463C}.
 
@@
 understanding the underlying galactic population will require more nuanced
-models, though the best path forward is not clear.
+models, on which development is underway ({\bf cite}).
 
